### 2020-01-23 paper/appendix.Rmd
preparing for recoded Exp1 JA

---
title: "Appendix"
output: pdf_document
---

## Experiment 1 Activities

### Video A (6-11.9 months) "Pick it up"

Parents are told to encourage their child to pick up and drop individual objects. They are also encouraged to place toys on a small cloth and show the child that they can drag the cloth towards them to reach the toys.

Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car

### Video B (6-11.9 months) "Animal sounds"

Parents are told to call different animals and imitate different sounds the animals make. They are also encouraged to observe which animal the child prefers.

Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls

### Video C (12-17.9 months) "Give me the toy"

Parents are told to ask their child to hand over individual toys. They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.

Props: toy boat, plastic frog, plastic elephant, toy bus

### Video D (12-17.9 months) "Classifying my toys"

Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small horse

### Video E (18-23.9 months) "My toys"

Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object. They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

### Video F (18-23.9 months) "The Orchestra"

Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.

Props: maracas, drum, tambourine, clapper

## Experiment 2 Activities

### Video A (12-17.9 months) "Give me the toy"

Parents are told to ask their child to hand over individual toys. They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.

Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow

### Video B (12-17.9 months) "Classifying my toys"

Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small horse

### Video C (12-17.9 months) "Geometric shapes jigsaw puzzle"

Parents are told to encourage their child to name different shapes on a jigsaw puzzle. Then they are told to undo the puzzle and invite the child to complete the puzzle.

Props: A jigsaw puzzle of geometric shapes

### Video D (18-23.9 months) "My toys"

Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object. They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

### Video E (18-23.9 months) "The Orchestra"

Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.

Props: maracas, drum, tambourine, clapper

### Video F (18-23.9 months) "My Yellow Toys"

Parents are told to show their child yellow toys and to ask, "What color are they?" They are also told to give the child toys of different colors, to ask them to only play with the yellow ones, and to praise the child after they do so.

Props: blue car, yellow car, yellow block, red block, blue block, green block

### 2020-01-23 paper/manuscript.Rmd
preparing for recoded Exp1 JA

---
title             : "Understanding the impacts of video-guided activities on parent-child interaction"
shorttitle        : "Impacts of videos on parent-child interaction"

author: 
  - name          : "George Kachergis"
    affiliation   : "1"
    address       : "Stanford, CA 94305 USA"
    email         : "kachergis@stanford.edu"
  - name          : "Emily Hembacher"
    affiliation   : "2"
  - name          : "Veronica Cristiano"
    affiliation   : "3"
  - name          : "Hanwen Vivian Zhang"
    affiliation   : "4"
  - name          : "Michael C. Frank"
    corresponding : yes
    address       : "Stanford, CA 94305 USA"
    email         : "mcfrank@stanford.edu"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Nextdoor, Inc."
  - id            : "3"
    institution    : "Gallaudet University"
  - id            : "4"
    institution    : "Cornell University"

authornote: |

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4629"

bibliography      : ["library.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
header-includes:
  - \usepackage{float}
documentclass     : "apa6"
csl: apa6.csl
classoption       : "man"
output            : papaja::apa6_pdf
appendix: "appendix.Rmd"
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

```{r setup, include = FALSE}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library("papaja")
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidyboot)
library(knitr)
source("multiplot.R")

select <- dplyr::select # masked by MASS
theme_set(theme_few())

# labels=addline_format(c("Activity Video", "Science Video"))
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}
```

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
e1_parent_ed = table(d$parent_ed)
#d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
d = read.csv("exp1_lexical_diversity_data.csv") # old one
d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns

e1ld <- d %>%
  mutate(condition = factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

e1_gender = table(e1ld$gender)
```

```{r load-exp1-joint-attention-data, echo=F}
load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))

e1ja <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>% # 6 parents NA -- don't want to remove from main analysis!
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         parent_ed = langcog::scale(parent_ed, scale=TRUE),
         gender = as.factor(gender),
         Video = as.factor(Video),
         pja_length = pja_length/1000,
         cja_length = cja_length/1000,
         total_lja = total_lja/1000) # convert duration ms -> seconds
```

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
#d = read.csv("exp2_lexical_diversity_data.csv")
d = read.csv("../exp2_lexical_diversityAdd.csv")

e2data <- d %>%
  mutate(condition = as.factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

e2data$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))

e2_gender = table(d$gender)
e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled
e2_18to24 = nrow(subset(d, Age>=1.5))
```

```{r load-exp2-joint-attention-data, echo=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
d$Age = d$age 
e2ja <- d %>% mutate(bids = bids_tot,
                     age = as.numeric(langcog::scale(age, scale=FALSE)),
                     pja_length = pja_length/1000,
                     cja_length = cja_length/1000,
                     total_lja = total_lja/1000) # convert duration ms -> seconds

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015]. Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment. 
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004], making implementation at scale a daunting proposition. 
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
But what do parents take away from these short messages about what to do with or how to talk with their children?

The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities. 
A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages [for a review, see @Breitenstein2014].
For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51% attendance vs. 85% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior [@Breitenstein2016].
Often, however, the theory of change presupposed by such interventions is relatively vague.
Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.

This theory of change is typically grounded in ideas about guided play and early language stimulation. 
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
Alternatively, by focusing parents on a specific activity, this theory could be flawed, causing parents to over-focus on achieving the superficial goals of the activity. 
This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
Another possibility is that these messages might produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.

Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages? 
In two experiments, we collected data from parent-child dyads in a local children's museum. 
We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification. 
Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2). 
We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.

# Experiment 1

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the _Activity Video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video. 
Parents in the _No Video_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

## Method

### Participants. 
`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). 
62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
Fifteen parents reported that their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).

### Materials.
Stimuli included activity videos from a commercial parenting application. 
The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development. 
In each video, an adult and child perform the activity (e.g., sorting toys according to size) while a narrator explains the activity and its purpose. 
We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months).
Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.[^1]

[^1]: Details of the specific videos used and the toys associated with each video are in the Appendix.

Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

### Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech. 
After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera. 
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA. 
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered _passive_ if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention. 
A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking. 
Full details of our guidelines for coding joint attention are available in SI.

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.

## Results and Discussion

Parents' child-directed speech during the play sessions was transcribed.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]

### Lexical Diversity

For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity. 
Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).

```{r, e1-lexdiv-regressions, echo=F, include=F}
require("rstanarm")
require(bayestestR)
# get estimated coefficient and 95% CI from Bayesian regression
get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
  pd = p_direction(model)
  pd = pd[which(pd$Parameter==cond),]$pd
  ci = round(c(ci95,ci89,pd), digits)
  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) 
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.10
p_direction(modTTR, effects="all") # orchestra 73.9%

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) 
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -6.27
p_direction(modMTLD, effects="all")

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 57.1
p_direction(tokens_mod, effects="all") # orchestra 84.2%

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
summary(types_mod) # nothing 
p_direction(types_mod, effects="all")

e1_lexdiv <- e1ld %>% group_by(condition) %>%
  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
```

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ
modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) # conditionexp, RR, genderM, parent_ed 
get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
p_direction(modTTRE, effects="all") # EL 84.9%, RR 83.3%, parent_ed 91.7%

modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
summary(modMTLDE) #
p_direction(modMTLDE, effects="all") # EL 78.5% AA 89.2% RR 86.6% genderM 87.8% parent_ed 91.5%

tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
summary(tokens_modE) # condition 54.4 
get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # SHOULD REPORT
p_direction(tokens_modE, effects="all") # RR 75.7% parent_ed 95.1%

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
p_direction(types_modE, effects="all") # EL 87.2% AA 77.7% genderM 88.3%, parent_ed 91.7% cond:AA 94.5%
get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA')

# predict # of conversational turns
modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
summary(modCT) 
get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .91
# E1 CT: exp early significant (+ effect)
# E2 CT: age nearly significany (+ effect)
```

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior falls.
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no predicted influence of age.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

```{r e1tokens, echo=F, include=F}
e1ld$Condition = factor(e1ld$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))

e1_mtld <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(MTLD) 
e1_lex <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(TTR) # Type/Token Ratio
e1_tok <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(tokens) 
e1_type <- e1ld %>% group_by(Condition) %>%
  tidyboot_mean(types)
```

We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf. int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf. int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

```{r e1tab, echo=F, include=F}
e1 <- e1ld %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
```

```{r e1ld-figs, include=F}
small_text = theme(
  plot.title = element_text(size = 12, face="bold"),
  axis.title.x = element_text(size = 10),
  axis.text.x = element_text(size = 8),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 8))

e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
  geom_point(data=e1ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
# want carriage return in Condition labels..

e1mtld <- ggplot(e1_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

```

```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\\% confidence intervals, and gray dots indicate values for each participant."}

ttr2 <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(TTR)

e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle("Experiment 2") + small_text

mtld2 <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(MTLD)

e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

e2tok <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(tokens)

e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none") + ggtitle(" ") + small_text

#multiplot(e1ttr, e1mtld, e1tokens, cols=3) # Exp1 LD graph
#multiplot(e2ttr, e2mtld, e2tokens, cols=3) # Exp2 LD graph

multiplot(e1ttr, e1mtld, e1tokens, 
          e2ttr, e2mtld, e2tokens, cols=3, layout=matrix(c(1,2,3, 4,5,6), nrow=2, byrow=T)) 
```

```{r, e1-effect-size, echo=F, include=F}
cohens_d <- function(dat) {
  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
}

ttr_means <- e1ld %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means) # -1.68 - should we report this?
```

### Joint Attention

```{r, e1ja-regressions, echo=F, include=F}

model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
summary(e1bids_mod) 
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # 2.59

e1bids_M <- e1ja %>% group_by(Condition) %>% 
  summarise(mean = mean(bids), sd = sd(bids))

e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
summary(e1tja_mod) # NA

e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
summary(e1tjadur_mod) # NA

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # NA

# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
summary(e1cja_mod) # NA

# Total duration of passive joint attention.
e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
summary(e1pja_time_mod) # NA

# Total duration of coordinated joint attention.
e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
summary(e1cja_time_mod) # NA
```

```{r e1ja-epaq-regressions, include=F, echo=F}
# follow-up regression (if we find a sig effect?)
model_stringE =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"

# Total number of bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, almost gender

# Episodes of coordinated joint attention.
e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
summary(e1cja_modE) # NA

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.09, 95% CI = [-2.22,0.07] % report % posterior <0?
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")

# Total duration of passive joint attention.
e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
summary(e1pja_time_modE) # NA

# Total duration of coordinated joint attention.
e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
summary(e1cja_time_modE) # NA
```

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no notable effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

### Exploratory Analyses

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the number of passive JA episodes showed an effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.

To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot). 
Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that are most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.

```{r fig-JA, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:JA} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1 (top). For Experiment 2 (bottom), mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right)."}
# Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA.

ms_bids1 <- e1ja %>% group_by(Condition) %>%
  tidyboot_mean(bids_tot)

e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle("Experiment 1") + small_text

# total joint attention episodes
ms_tja1 <- e1ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja)

e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none") + ggtitle(" ") + small_text

e2_cja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(cja)

library("scales")
#show_col(solarized_pal()(2)) # blue, red
sol_colors = solarized_pal()(2)

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  labs(fill="Condition") + 
  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") + 
  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
  theme(legend.position="none")
  #theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))

# total JA episodes (not currently graphed)
e2_tja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja) 
e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  ggtitle(" ") + small_text + theme(legend.position="none")

e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  ggthemes::theme_few() + ggtitle(" ") + small_text + 
  theme(legend.position="bottom", legend.text=element_text(size=9), 
        legend.margin=margin(0,0,5,0),
        legend.box.margin=margin(-10,-10,-5,-10))
  #theme(legend.position="none")

# multiplot(e1bids, e1tja, cols=2) # old Exp1
# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
multiplot(e1bids, e1tja, e2bids, e2tja_age, 
          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
```

### Discussion

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable: 
after the Activity Video, parents used more words related to requests (e.g., "Can I have X? / Give me X. Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
However, parents who watched an activity video also made more bids for JA with their child.
While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

# Experiment 2

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]

[^4]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).

## Method

### Participants. 
`r nrow(e2data)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. 
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
Sixteen parents reported their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).

### Materials.

The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children. 
This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development. 
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies. 
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
Details of the videos used in the Activity Video conditions are in the Appendix.

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.60,0.90] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.

## Results and Discussion

Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions[^5] predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

[^5]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).

### Lexical Diversity
```{r, e2-lexdiv-regressions, echo=F, include=F}
# preregistered analyses:
# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens). 
# 1) bids, 2) total JA eps, 3) # tokens 4) TTR 
# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs. control) and age in months as fixed effects and participant and specific video as random effects. 
# DV ~ age * condition + (1 | participant) + (1 | video)
# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
# “secondary analyses"
# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.

# Notes: 
# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
# Predicting lexical diversity based on experimental condition. 
e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
summary(e2TTR_m) # conditionexp beta=-.1 95% CI=[-.2,0.0]
e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp")

# predict word tokens
e2tokens_m <- stan_lmer(log(tokens) ~ age * condition + (1 | video), data=e2data)
summary(e2tokens_m) # NA 
print(e2tokens_m, digits=2)
p_direction(e2tokens_m, effects="all") 
# conditionexp 90.3%, age:conditionexp 83.1%  video:big_small 96.3%, video:orchestra 94.5%
launch_shinystan(e2tokens_m, ppd = FALSE)
summary(e2tokens_m, 
        pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"),
        probs = c(0.025, 0.975),
        digits = 2)
plot(e2tokens_m)
#prior_summary(object = e2tokens_m)
get_stan_glmer_reporting_values(e2tokens_m,"conditionexp")

# require(bayesplot)
# bayesplot_grid(
#   plot(e2tokens_m, plotfun = "intervals", pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"), prob = 0.5, prob_outer = 0.89, point_est = "median") + ggtitle("Marginal Posterior Parameter Estimates"),
#   plot(e2tokens_m, plotfun = "areas", pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"), prob = 0.5, prob_outer = 0.89, point_est = "median") + ggtitle("Marginal Posterior Parameter Estimates"),
#   grid_args = list(ncol = 2)
# )

e2MTLD_m <- stan_lmer(MTLD ~ age * condition + (1 | video), data=e2data)
summary(e2MTLD_m) # NA

e2_lexdiv <- e2data %>% group_by(condition) %>%
  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
# predict word types (NOT A PREREGISTERED REGRESSION)
#types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
#summary(types_mod) # NA
```

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]). 
The preregistered regression predicting the number of tokens used by parents revealed no effects. 
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

```{r e2tab, echo=F}
e2 <- e2data %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
```

```{r e2token-type, include=F}
# NOT INCLUDED
e2typ <- e2data %>% group_by(Condition) %>%
  tidyboot_mean(types)

e2types <- ggplot(e2typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2data, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Types") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

#multiplot(e2tokens, e2types, cols=2)
```

```{r, e2-effect-size, echo=F, include=F}
ttr_means <- e2data %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means)
```

### Joint Attention
```{r, e2ja-regressions, echo=F, include=F}

# Total number of bids
e2bids_m <- stan_lmer(bids ~ age * Condition + (1|video), data=e2ja)
summary(e2bids_m) # condition mean=3.1, 95%CI = [1.1, 5.0]
e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")

e2tja_m <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
summary(e2tja_m) # total episodes of joint attention -- age, age*condition, condition
#                                        mean    sd     2.5%   25%    50%    75%    97.5%
# (Intercept)                             7.3    0.4    6.4    7.0    7.3    7.6    8.2 
# age                                    -5.0    1.7   -8.2   -6.1   -5.0   -3.9   -1.6 
# ConditionVideo                          1.5    0.6    0.3    1.1    1.5    1.9    2.8 
# age:ConditionVideo                      5.6    2.5    0.7    3.9    5.7    7.4   10.5 
e2tjaAge = get_stan_glmer_reporting_values(e2tja_m, "age")
e2tjaCond = get_stan_glmer_reporting_values(e2tja_m, "ConditionActivity Video")
e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionActivity Video")

```

We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made notably more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other effects on parental bids for JA.

The regression predicting the number of episodes of JA revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
Older children also participated in fewer episodes of JA ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]). 
However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in fewer episodes of JA after an activity video.

```{r e2ja-exploratory, echo=F, include=F}
# EXPLORATORY ANALYSES (NOT PREREGISTERED)

# Episodes of coordinated joint attention
e2cja_m <- stan_lmer(cja ~ age * Condition + (1 | video), data = e2ja)
summary(e2cja_m) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
e2cjaCond <- get_stan_glmer_reporting_values(e2cja_m, "ConditionActivity Video")
e2cjaAgeCond <- get_stan_glmer_reporting_values(e2cja_m, "age:ConditionActivity Video")
# age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
#                                        mean    sd     2.5%   25%    50%    75%    97.5%
# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6

# Episodes of passive joint attention.
e2pja_m <- stan_lmer(pja ~ age * Condition + (1 | video), data = e2ja)
summary(e2pja_m) # age beta=-2.7 95% CI=[-5.1,0.0]
e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")

# Total duration of passive joint attention.
e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2pjat_m) # age: est: -17.97 95% CI = [-33.37,-2.41] 
e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")

# Total duration of coordinated joint attention.
e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2cjat_m) # age: est: 35.3 89% CI = [1.57,67.4] 
e2cjat <- get_stan_glmer_reporting_values(e2cjat_m, "age")

e2tjat_m <- stan_glmer(total_lja ~ age * Condition + (1|video), data=e2ja)
summary(e2tjat_m) # anything here?

```

### Exploratory Analyses

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes found no notable effects.

Older children both engaged in more episodes of passive JA with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), and spent more total time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".

```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2."}
# Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition. (no interpretation in PsychSci captions)

#Episodes of coordinated joint attention
e2cjad <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(cja)

e2cja <- ggplot(e2cjad, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ja, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of Coordinated JA") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")

e2cja_age = ggplot(e2ja, aes(x = age, y = cja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
  langcog::scale_colour_solarized() + ggthemes::theme_few()

print(e2cja_age)
#multiplot(e2cja, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
```

# General Discussion

We were interested in how digital parenting advice alters parents' interactions with their children. 
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions. 
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention. 
In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
In some cases--especially in older children--these bids were successful in increasing engagement. 
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity). 
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like"), often asking about animal noises ("What does the X say?").

The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions. 
Why were they successful? 
When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child. 
Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.

Our study has a number of limitations related to design and sample, each of which suggests possible future directions. 
First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned). 
A longer-term study would also address whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
Second, our design assumes that parents have access to the materials needed to complete the suggested activities; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions. 
Providing materials may be critical for the success of activity suggestions. 
Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research. 
A key goal for future research is to assess the generality of these findings across populations.

<!-- Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity. -->

<!-- Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp. 1). However, activity videos resulted in parents using more word tokens, while the number of word types did not differ significantly across conditions. -->
<!-- Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens. -->

In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.

# Acknowledgements

This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

\newpage

# References
```{r create_r-references}
r_refs(file = "library.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

```{r echo = FALSE, results = 'asis'}
render_appendix('appendix.Rmd')
```

```{r echo = FALSE, results = 'asis'}
render_appendix('appendix.Rmd')
```

### 2020-01-23 paper/extra_text.R

@@ -1,8 +1,13 @@
 notes:
   - replace bootstrapped 95pct CIs with Bayesian credibility interval?
-  -
-
-unused text
+  - we should make sure to cite the Weisleder intervention paper (since it’s among the only pieces of causal evidence on early parenting)
+  - ICCs for JA overall are high but very low for sub measures: We should mention that this is a reason why we might may see fewer findings on episodes
+  - Note that figure on JA has non-matching y labels for Experiment 2 (total vs mean)
+  - say in E1 that low reliability led us to follow up and refine coding procedure: 
+      E1 ICCs might be a flag for some folks, so minimally we should think about explaining that these low reliability limits interpretability of those findings
+For consistency, although we didn’t have a preregistration for e1, we used the same analyses that we used in e2.
+Kat: clarify "scientific justification" in videos. Did the videos focus on language, JA?
+  - cite Leung2018 HomeView: https://www.sciencedirect.com/science/article/pii/S0885200618301534
 
 Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
 

### 2020-03-09 parenting_obs_e1/joint_attention_recoded/parenting_obs_JA_recoded.Rmd
renamed files and adjusted to calculated rate of JA episodes (per minute)

---
title: "Parenting Observational Study E1 Coding"
author: "Emily & George"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Looking at the effect of electronically-delivered parenting interventions on parent-child interactions. Parents in the experimental condition viewed a video (designed for a parenting app) demonstrating an activity they could do with their child. Parents in the control condition did not view a video. Both groups of parents were asked to play with their child for 3 minutes with a set of props that matched the video demonstration they had seen. Children were 6-24 months of age. There were 6 videos total (2 per age group). Assignment to videos/sets of toys was counterbalanced within age groups. Parents also completed the Parenting Attitudes Questionnaire. Videos of the play sessions were coded for bids for joint attention, episodes of passive joint attention, and episodes of coordinated joint attention.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(theme_bw())
```

Read in files and consolidate to the same directory.

```{r}
combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

  for (f in files) {
    jf <- paste(data_dir, f, sep="")
    jd <- read.csv(jf)

  # (assumes something happened early in the vid and late in the vid..)
    vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))
    which(jd$phase_length < 3000) # trim episodes <3 seconds long?

    id <- data.frame(SID = str_replace(f, "_recode.csv", ""), # "012017_01_recode"
                   line = jd$JointAttention.ordinal, # numbered list of episodes e.g. 0 1 2 3 4 5 6 7
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

    d.long <- rbind(d.long, id)
    #d.raw <- bind_rows(d.raw, sd)
  }
  return(d.long)
}

d.long <- combine_datavyu_files("data/")

dim(d.long %>% filter((cja==1 | pja==1) & phase_length<3000)) # 150

d.long[which(d.long$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

# summarise per subject
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration

```

Read in trial info and demographics.

```{r}
conditions <- read.csv("conditions.csv")

load("../paq/paq_demo.RData")
load("../paq/obs_demo.RData")

ids <- ids%>%
  mutate(SID = sid)%>%
  select(-sid)

demo <- demo%>%
  mutate(SID = sid)%>%
  select(-sid)%>%
  mutate(age_months = age * 12)

demo$age_group[demo$age_months < 12] <- "6"
demo$age_group[demo$age_months >= 12 & demo$age_months < 18 ] <- "12"
demo$age_group[demo$age_months >= 18] <- "18"

d <- d.raw %>%
  left_join(conditions) %>%
  mutate(bids_tot = bids) %>% 
  left_join(demo)%>%
  left_join(ids)%>%
  select(-sid)
```

#Demographics

```{r}
demos <- conditions%>%
  left_join(demo)

demos$parent_ed[demos$parent_ed == 1] <- 8
demos$parent_ed[demos$parent_ed == 2] <- 12
demos$parent_ed[demos$parent_ed == 3] <- 14
demos$parent_ed[demos$parent_ed == 4] <- 18
demos$parent_ed[demos$parent_ed == 5] <- 20
demos$parent_ed[demos$parent_ed == 6] <- 22

#child gender
table(demos$Condition, demos$gender)
#ethnicity
table(demos$Condition, demos$ethnicity)
#years of education
table(demos$Condition, demos$parent_ed)
```

# Reliability

Import reliability coder's data (20 participants were coded for reliability).
```{r}

d.long_rel <- combine_datavyu_files("rel_data/")

dim(d.long_rel %>% filter((cja==1 | pja==1) & phase_length<3000)) # 39

d.long_rel[which(d.long_rel$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw_rel[,2:9] = d.raw_rel[,2:9] / d.raw_rel$vid_duration

```

# Reliability
```{r}
load("Exp1_joint_attention_data_ORIGINAL.RData") # compare Sama to original Exp1 coding
old <- d %>% select(SID, bids, cja, pja, pja_length, cja_length, total_ja, total_lja, bids_tot)

old %>% summarise(bids = mean(bids), cja=mean(cja), pja=mean(pja), l_pja=mean(pja_length), l_cja=mean(cja_length))

d.raw_rel <- d.raw_rel %>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length) %>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

d.raw %>% summarise(bids = mean(bids), cja=mean(cja), pja=mean(pja), l_pja=mean(pja_length), l_cja=mean(cja_length))

d.raw <- d.raw %>% mutate(l_pja = pja_length, l_cja = cja_length)
# 110416_03 l_cja_rel = -25889, which shouldn't be possible (incomplete final row of file)
# 121516_01 has NA bids_rel, pja_rel, and cja_rel..
# 111716_08 l_cja = -49923, which shouldn't be possible

# 110416_05, 050116_01, and 092216_03: reliability coder saw no passive JA
d_rel <- d.raw_rel %>% left_join(d.raw, by="SID") %>%
  select(SID, bids, bids_rel, pja, pja_rel, cja, cja_rel, l_cja, l_cja_rel, l_pja, l_pja_rel)

d_rel$pja_diff = (d_rel$pja - d_rel$pja_rel) ^ 2
d_rel$l_pja_diff = (d_rel$l_pja - d_rel$l_pja_rel) ^ 2
d_rel %>% arrange(pja_diff, l_pja_diff)

# compare old vs. d.raw

cor(d.raw$bids, old$bids) # .35
cor(d.raw$cja, old$cja) # .53
cor(d.raw$pja, old$pja) # .34
cor(d.raw$pja_length, old$pja_length) # .32
cor(d.raw$cja_length, old$cja_length) # .52
cor(d.raw$total_ja, old$total_ja) # .27
cor(d.raw$total_lja, old$total_lja) # .31

psych::ICC(cbind(d.raw$pja, old$pja), missing = FALSE, alpha = 0.05)

mean(d_rel$pja - d_rel$pja_rel, na.rm=T)
d_rel$pja - d_rel$pja_rel

get_ICC2 <- function(dat)  {
  rel = psych::ICC(dat, missing = FALSE, alpha = 0.05)
  return(rel$results[2,])
}

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")])

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # eps pass JA

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # eps coord JA

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # pass JA length

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # coord JA length

#psych::ICC(d_rel[,c("bids","bids_rel")], missing = FALSE, alpha = 0.05) # orig was ICC2=.8, now is .52
#psych::ICC(d_rel[,c("pja","pja_rel")], missing = FALSE, alpha = 0.05) # orig was ICC2=.20, now is .20 - same :/
#psych::ICC(d_rel[,c("cja","cja_rel")], missing = FALSE, alpha = 0.05) #  orig was ICC2=.66, now is .65
#psych::ICC(d_rel[,c("l_pja","l_pja_rel")], missing = FALSE, alpha = 0.05) # orig was ICC2=.24 now is .15
#psych::ICC(d_rel[,c("l_cja","l_cja_rel")], missing = FALSE, alpha = 0.05) # orig was .62 now is .28
```

Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.

# Compare raters

```{r}
plot(d_rel$pja, d_rel$pja_rel)

plot(d_rel$l_pja, d_rel$l_pja_rel)
```

# Plots

Total number of bids (successful and unsuccessful)
```{r, width=4, height=4}
save(d, file="Exp1_joint_attention_data.RData")
ms_bids <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "bids_tot")

ms_bids$Condition <- factor(ms_bids$Condition,
                            levels = c("con", "exp"),
                            labels = c("control", "video"))

ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.position="none") 
```

Total episodes of joint attention.

```{r}
ms_tja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "total_ja")

ms_tja$Condition <- factor(ms_tja$Condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total episodes of Joint Attention") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Episodes of passive joint attention.
```{r}
ms_pja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Episodes of coordinated joint attention
```{r}
ms_cja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

Total duration of passive joint attention.
```{r}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of coordinated joint attention.
```{r}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

## Demographics

### Child gender

Total bids by gender.
```{r}
# total bids
ms_bids <- d %>%
  group_by(Condition, gender) %>%
  multi_boot_standard(col = "bids_tot")

ggplot(ms_bids, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of passive joint attention by gender
```{r}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, gender) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of coordinated joint attention by gender
```{r}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, gender) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

### Child age

Children were separated into 3 age groups: 6-12 months, 12-18 months, and 18-24 months.

Total bids by age.
```{r}
# total bids
ms_bids <- d %>%
  group_by(Condition, age_group) %>%
  multi_boot_standard(col = "bids_tot")

ms_bids$age_group <- factor(ms_bids$age_group , levels = c("6","12", "18"))

ggplot(ms_bids, aes(x = Condition, y = mean, fill=age_group)) + 
  geom_bar(stat="identity", position= "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of passive joint attention by age
```{r}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, age_group) %>%
  multi_boot_standard(col = "pja_length")

ms_lpja$age_group <- factor(ms_lpja$age_group , levels = c("6","12", "18"))

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Total duration of coordinated joint attention by age
```{r}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, age_group) %>%
  multi_boot_standard(col = "cja_length")

ms_lcja$age_group <- factor(ms_lcja$age_group , levels = c("6","12", "18"))

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

### Parenting attitudes and education

Do PAQ scores predict the number of bids for joint attention by parents?
```{r}
d_plot <- d %>%
  gather("subscale","score", AA:RR)

ggplot(d_plot, aes(x = score, y = bids_tot, col = subscale)) +
  geom_jitter() + 
  xlim(0,6) +
  geom_smooth(method="lm", se=FALSE)  + 
  facet_wrap(~Condition)+
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() 
```

Does parent education predict the number of bids for joint attention by parents?
```{r}
d_plot <- d %>%
  gather("subscale","score", AA:RR)

ggplot(d_plot, aes(x = parent_ed, y = bids_tot)) +
  geom_jitter() + 
  xlim(0,6) +
  geom_smooth(method="lm", se=FALSE)  + 
  facet_wrap(~Condition)+
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() 
```

# Analysis

Is the duration of joint attention correlated with age in months?

```{r}
cormat <- d %>%
  select(age_months, pja_length, cja_length, total_lja)
rcorr(as.matrix(cormat))

```

Mixed effects models.

Prepare data.
```{r}
lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         Video = as.factor(Video))
```

Total number of bids
```{r}
maximal_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Episodes of coordinated joint attention.
```{r}
maximal_mod <- lmer(cja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Episodes of passive joint attention.
```{r}
maximal_mod <- lmer(pja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Total duration of passive joint attention.
```{r}
maximal_mod <- lmer(pja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Total duration of coordinated joint attention.
```{r}
maximal_mod <- lmer(cja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

# Conclusions

There is a main effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.

There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes.

There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids. There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.

While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.

### 2020-03-09 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
renamed files and adjusted to calculated rate of JA episodes (per minute)

---
title: "Parenting Observational Study E2 Coding"
author: "Emily, Vivian, George"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Looking at the effect of electronically-delivered parenting interventions on parent-child interactions. Parents in the experimental condition viewed a video (designed for a parenting app) demonstrating an activity they could do with their child. Parents in the control condition did not view a video. Both groups of parents were asked to play with their child for 3 minutes with a set of props that matched the video demonstration they had seen. Children were 6-24 months of age. There were 6 videos total (2 per age group). Assignment to videos/sets of toys was counterbalanced within age groups. Parents also completed the Parenting Attitudes Questionnaire. Videos of the play sessions were coded for bids for joint attention, episodes of passive joint attention, and episodes of coordinated joint attention.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(ggthemes::theme_few() + theme(legend.title = element_text(size=18), legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16), axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), axis.title.y = element_text(size=18)))
```

Read in files and consolidate to the same directory.

```{r echo=F}
combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

  for (f in files) {
    jf <- paste(data_dir, f, sep="")
    jd <- read.csv(jf)

  # (assumes something happened early in the vid and late in the vid..)
    vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))
    which(jd$phase_length < 3000) # trim episodes <3 seconds long?

    id <- data.frame(SID = str_replace(f, ".csv", ""), # "012017_01_recode"
                   line = jd$JointAttention.ordinal, 
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

    d.long <- rbind(d.long, id)
    #d.raw <- bind_rows(d.raw, sd)
  }
  return(d.long)
}

d.long <- combine_datavyu_files("data/")

d.long[which(d.long$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

# summarise per subject
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
```

Read in trial info 
```{r}
conditions <- read.csv("conditions.csv") %>%
  transmute(SID = sid, condition=condition, video=video, label=label)

d <- left_join(d.raw, conditions, by="SID")

#d$age[d$sid=="111517_3"] = "2"
```

# Reliability

Import reliability coder's data (20 participants were coded for reliability).
```{r}
d.long_rel <- combine_datavyu_files("rel_data/")

d.long_rel[which(d.long_rel$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw_rel[,2:9] = d.raw_rel[,2:9] / d.raw_rel$vid_duration

```

Reliability.
```{r}
d.raw_rel <- d.raw_rel %>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length) %>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

d.raw <- d.raw %>% mutate(l_pja = pja_length, l_cja = cja_length)
# 110416_03 l_cja_rel = -25889, which shouldn't be possible (incomplete final row of file)
# 121516_01 has NA bids_rel, pja_rel, and cja_rel..
# 111716_08 l_cja = -49923, which shouldn't be possible

# 110416_05, 050116_01, and 092216_03: reliability coder saw no passive JA
d_rel <- d.raw_rel %>% left_join(d.raw, by="SID") %>%
  select(SID, bids, bids_rel, pja, pja_rel, cja, cja_rel, l_cja, l_cja_rel, l_pja, l_pja_rel)

get_ICC2 <- function(dat)  {
  rel = psych::ICC(dat, missing = FALSE, alpha = 0.05)
  return(rel$results[2,])
}

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .85

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # .75 eps pass JA

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # .75 eps coord JA

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # .73 pass JA length

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # .75 coord JA length
```

Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.

# Plots

Total number of bids (successful and unsuccessful)
```{r, width=4, height=4}
dem <- read.csv("../anonymized_demographics_parenting_obs_e2.csv", header=T)
dem$age = as.numeric(as.character(dem$age))
d$age = NULL
d <- d %>% left_join(dem, by="SID") %>%
  filter(age <= 2.0) # 1 kid exactly 2...

save(d, file="Exp2_joint_attention_data.RData")

d$condition <- factor(d$condition, levels = c("con", "exp"), labels = c("control", "video"))

ms_bids <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "bids")

ggplot(ms_bids, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total bids for Joint Attention") +
  langcog::scale_colour_solarized() + theme(legend.position="none") 
```

Total episodes of joint attention.

```{r}
ms_tja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "total_ja")

ggplot(ms_tja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total episodes of Joint Attention") +
  langcog::scale_colour_solarized() 
```

Episodes of passive joint attention.
```{r}
ms_pja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized()
```

Episodes of coordinated joint attention
```{r}
ms_cja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()
```

Total duration of passive joint attention.
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of coordinated joint attention.
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() 
```

##Demographics

###Child gender

Total bids by gender.
```{r}
# total bids
ms_bids <- d %>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "bids")

ggplot(ms_bids, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of passive joint attention by gender
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of coordinated joint attention by gender
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() 
```

###Child age

Children were separated into 3 age groups: 6-12 months, 12-18 months, and 18-24 months.

Total bids by age.
```{r}
# total bids
d$age_group = ifelse(d$age<1, "6-12", ifelse(d$age<1.5, "12-18", "18-24"))
d$age_group <- factor(d$age_group , levels = c("6-12","12-18", "18-24"))

ms_bids <- d %>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "bids")

ggplot(ms_bids, aes(x = condition, y = mean, fill=age_group)) + 
  geom_bar(stat="identity", position= "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of passive joint attention by age
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of coordinated joint attention by age
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() 
```

# Analysis

Is the duration of joint attention correlated with age?

```{r}
cormat <- d %>%
  select(age, pja_length, cja_length, total_lja)
rcorr(as.matrix(cormat))
```

Mixed effects models.

Prepare data.
```{r}
lmer_data <- d %>% 
  mutate(Condition = factor(condition), 
         bids = as.numeric(bids),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         Video = as.factor(video))
```

Total number of bids
```{r}
lmer_data$parent_ed = as.numeric(as.character(lmer_data$parent_ed))
maximal_mod <- lmer(bids ~ Condition * age + (1| Video), data = lmer_data)
summary(maximal_mod)
```

Episodes of coordinated joint attention.
```{r}
maximal_mod <- lmer(cja ~ Condition * age + (1| Video), data = lmer_data)
summary(maximal_mod)
```

Episodes of passive joint attention.
```{r}
maximal_mod <- lmer(pja ~ Condition * age + (1| Video), data = lmer_data)
summary(maximal_mod)
```

Total duration of passive joint attention.
```{r}
maximal_mod <- lmer(pja_length ~ Condition * age + (1| Video), data = lmer_data)
summary(maximal_mod)
```

Total duration of coordinated joint attention.
```{r}
maximal_mod <- lmer(cja_length ~ Condition * age + (1| Video), data = lmer_data)
summary(maximal_mod)
```

# Conclusions

### 2020-03-16 paper/manuscript.Rmd
renamed files and adjusted to calculated rate of JA episodes (per minute)
switched to rate of JA per min

@@
 d$Age = d$age 
-e2ja <- d %>% mutate(bids = bids_tot,
+e2ja <- d %>% mutate(bids = bids,
                      age = as.numeric(langcog::scale(age, scale=FALSE)),
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for number of parent bids for JA; ICC = 0.34 with 95% CI = [-0.11,0.67] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for total duration of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for total duration of coordinated JA episodes.
 
@@
 summary(modTTR) 
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.10
-p_direction(modTTR, effects="all") # orchestra 73.9%
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
+p_direction(modTTR, effects="all") # orchestra 78.7%
 
@@
 summary(modMTLD) 
-e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -6.27
+e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -8.48
 p_direction(modMTLD, effects="all")
@@
 summary(tokens_mod)
-e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 57.1
-p_direction(tokens_mod, effects="all") # orchestra 84.2%
+e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.5
+p_direction(tokens_mod, effects="all") # orchestra 89.7%
 
@@
 summary(modCT) 
-get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .91
+get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .92
 # E1 CT: exp early significant (+ effect)
@@
 The coding procedure also matched that of Experiment 1. 
-A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.60,0.90] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.
+To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
+The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48,0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61,0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.
 
@@
 ```
-
-```{r echo = FALSE, results = 'asis'}
-render_appendix('appendix.Rmd')
-```

### 2020-03-16 parenting_obs_e1/joint_attention/parenting_obs_JA.Rmd
switched to rate of JA per min

---
title: "Parenting Observational Study E1"
author: "Emily & George"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Looking at the effect of electronically-delivered parenting interventions on parent-child interactions. Parents in the experimental condition viewed a video (designed for a parenting app) demonstrating an activity they could do with their child. Parents in the control condition did not view a video. Both groups of parents were asked to play with their child for 3 minutes with a set of props that matched the video demonstration they had seen. Children were 6-24 months of age. There were 6 videos total (2 per age group). Assignment to videos/sets of toys was counterbalanced within age groups. Parents also completed the Parenting Attitudes Questionnaire. Videos of the play sessions were coded for bids for joint attention, episodes of passive joint attention, and episodes of coordinated joint attention.

# Data preprocessing

Preliminaries.

```{r include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(ggthemes::theme_few() + theme(legend.title = element_text(size=18), legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16), axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), axis.title.y = element_text(size=18)))
```

Read in files and consolidate to the same directory.

```{r}
# for rate coding (JA/minute), we coded the start / end of play sessions because they were not exactly 3 minutes
play_duration <- read.csv("parenting_obs_play_duration_E1.csv", header=T)
play_duration <- play_duration %>% 
  mutate(play_duration = play_stop_sec - play_start_sec)
sort(play_duration$play_duration) # shortest: 167 seconds
summary(play_duration$play_duration) # median = 201.5, mean=205.9
# use play_duration$verbalcue_start_sec instead of play_start? (when it exists)

combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

  for (f in files) {
    jf <- paste(data_dir, f, sep="")
    jd <- read.csv(jf)

    # (assumes something happened early in the vid and late in the vid..)
    #vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    #if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
    SID = str_replace(f, ".csv", "")
    vid_duration = play_duration[which(play_duration$SID==SID),]$play_duration

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))

    id <- data.frame(SID = SID, # "012017_01_recode"
                   line = jd$JointAttention.ordinal, # numbered list of episodes e.g. 0 1 2 3 4 5 6 7
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

    d.long <- rbind(d.long, id)
    #d.raw <- bind_rows(d.raw, sd)
  }
  return(d.long)
}

d.long <- combine_datavyu_files("data/")

d.long[which(d.long$phase_length<0),] # 3, but only bids so duration doesn't matter

dim(d.long %>% filter((cja==1 | pja==1) & phase_length<3000)) # 150

d.long[which(d.long$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

d.long[which(rowSums(d.long[,c("pja","cja","bid")])==0),] # now several rows are not even classified as bids - should elim

# summarise per subject
# Emily only coded unsuccessful parent bids in Exp 1, assuming that any cJA episode started with a parent bid
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60, # seconds to minutes
         phase_length = phase_length / 1000) %>% # ms to seconds
  summarise(bids=sum(bid) + sum(cja), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute and seconds / min duration of JA)
vid_dur = d.raw$vid_duration
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
d.raw$vid_duration = vid_dur

```

Read in trial info and demographics.

```{r}
conditions <- read.csv("conditions.csv")

load("../paq/paq_demo.RData")
load("../paq/obs_demo.RData")

ids <- ids%>%
  mutate(SID = sid)%>%
  select(-sid)

demo <- demo%>%
  mutate(SID = sid)%>%
  select(-sid)%>%
  mutate(age_months = age * 12)

demo$age_group[demo$age_months < 12] <- "6"
demo$age_group[demo$age_months >= 12 & demo$age_months < 18 ] <- "12"
demo$age_group[demo$age_months >= 18] <- "18"

#note from Emily- I calculated total bids by adding unsuccessful bids + episodes of joint attention that were acheived. In retrospect, this assumes that all episodes of JA were initiated by parent, which is probably false. Next time, code all parent bids rather than only unsuccessful ones.
d <- d.raw %>%
  left_join(conditions)%>%
  mutate(bids_tot = bids + cja + pja)%>%
  left_join(demo)%>%
  left_join(ids)%>%
  select(-sid)
```

# Demographics

```{r}
demos <- conditions%>%
  left_join(demo)

demos$parent_ed[demos$parent_ed == 1] <- 8
demos$parent_ed[demos$parent_ed == 2] <- 12
demos$parent_ed[demos$parent_ed == 3] <- 14
demos$parent_ed[demos$parent_ed == 4] <- 18
demos$parent_ed[demos$parent_ed == 5] <- 20
demos$parent_ed[demos$parent_ed == 6] <- 22

#child gender
table(demos$Condition, demos$gender)
#ethnicity
table(demos$Condition, demos$ethnicity)
#years of education
table(demos$Condition, demos$parent_ed)
```

# Reliability

Import reliability coder's data (20 participants were coded for reliability).
```{r}
d.long_rel <- combine_datavyu_files("rel_data/")

d.long_rel[which(d.long_rel$phase_length<0),] 
# SID=120916_03	 line=7	 -1275	 0	1	 1	 - cja + bid, so should double-check

dim(d.long_rel %>% filter((cja==1 | pja==1) & phase_length<3000)) # 39

d.long_rel[which(d.long_rel$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60, # seconds to minutes
         phase_length = phase_length / 1000) %>% # ms to seconds
  summarise(bids=sum(bid) + sum(cja), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw_rel[,2:9] = d.raw_rel[,2:9] / d.raw_rel$vid_duration

```

## Check Reliability
```{r}
d.raw_rel <- d.raw_rel %>%
  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length) %>%
  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)

d.raw %>% summarise(bids = mean(bids), cja=mean(cja), pja=mean(pja), l_pja=mean(pja_length), l_cja=mean(cja_length))

d.raw <- d.raw %>% mutate(l_pja = pja_length, l_cja = cja_length)

d_rel <- d.raw_rel %>% left_join(d.raw, by="SID") %>%
  select(SID, bids, bids_rel, pja, pja_rel, cja, cja_rel, l_cja, l_cja_rel, l_pja, l_pja_rel)

get_ICC2 <- function(dat)  {
  rel = psych::ICC(dat, missing = FALSE, alpha = 0.05)
  return(rel$results[2,])
}

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .79 [.55, .91]

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # eps pass JA .34 [-.11, .67]

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # eps coord JA .66 [.32, .85]

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # pass JA length .33 [-.11, .67]

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # coord JA length .60 [.24, .82]

save(d, file="Exp1_joint_attention_data.RData")
```

Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.

# Plots

Total parent bids (successful and unsuccessful) per minute.
```{r, echo=F, width=4, height=4}
ms_bids <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "bids_tot")

ms_bids$Condition <- factor(ms_bids$Condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Bids for Joint Attention per Min.") 
```

Total episodes of joint attention.

```{r, echo=F}
ms_tja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "total_ja")

ms_tja$Condition <- factor(ms_tja$Condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of JA per Min.") 
```

Episodes of passive joint attention.
```{r, echo=F}
ms_pja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") +  ylab("Episodes of Passive JA per Min.")  
```

Episodes of coordinated joint attention
```{r, echo=F}
ms_cja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("Episodes of Coordinated JA per Min.")
```

Total duration of passive joint attention.
```{r, echo=F}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Passive JA per Min.")
```

Total duration of coordinated joint attention.
```{r, echo=F}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.")
```

## Demographics

### Child gender

Total bids by gender.
```{r, echo=F}
# total bids
ms_bids <- d %>%
  group_by(Condition, gender) %>%
  multi_boot_standard(col = "bids_tot")

ggplot(ms_bids, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Bids for Joint Attention per Min.") 
```

Total duration of passive joint attention by gender
```{r, echo=F}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, gender) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Passive JA per Min.")
```

Total duration of coordinated joint attention by gender
```{r, echo=F}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, gender) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = Condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.")
```

### Child age

Children were separated into 3 age groups: 6-12 months, 12-18 months, and 18-24 months.

Total bids by age.
```{r, echo=F}
# total bids
ms_bids <- d %>%
  group_by(Condition, age_group) %>%
  multi_boot_standard(col = "bids_tot")

ms_bids$age_group <- factor(ms_bids$age_group , levels = c("6","12", "18"))

ggplot(ms_bids, aes(x = Condition, y = mean, fill=age_group)) + 
  geom_bar(stat="identity", position= "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Bids for JA per Min.")
```

Total duration of passive joint attention by age
```{r, echo=F}
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, age_group) %>%
  multi_boot_standard(col = "pja_length")

ms_lpja$age_group <- factor(ms_lpja$age_group , levels = c("6","12", "18"))

ggplot(ms_lpja, aes(x = Condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Passive JA per Min.")
```

Total duration of coordinated joint attention by age
```{r, echo=F}
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition, age_group) %>%
  multi_boot_standard(col = "cja_length")

ms_lcja$age_group <- factor(ms_lcja$age_group , levels = c("6","12", "18"))

ggplot(ms_lcja, aes(x = Condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.")
```

### Parenting attitudes and education

Do PAQ scores predict the number of bids for joint attention by parents?
```{r, echo=F}
d_plot <- d %>%
  gather("subscale","score", AA:RR)

ggplot(d_plot, aes(x = score, y = bids_tot, col = subscale)) +
  geom_jitter() + xlim(0,6) +
  geom_smooth(method="lm", se=FALSE)  + 
  facet_wrap(~Condition)
```

Does parent education predict the number of bids for joint attention by parents?
```{r, echo=F}
d_plot <- d %>%
  gather("subscale","score", AA:RR)

ggplot(d_plot, aes(x = parent_ed, y = bids_tot)) +
  geom_jitter() + 
  xlim(0,6) +
  geom_smooth(method="lm", se=FALSE)  + 
  facet_wrap(~Condition)
```

# Analysis

Is the duration of joint attention correlated with age in months?

```{r}
cormat <- d %>%
  select(age_months, pja_length, cja_length, total_lja)
rcorr(as.matrix(cormat))
```

## Mixed effects models.

Prepare data.
```{r}
lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         Video = as.factor(Video))
```

Total number of bids
```{r}
maximal_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Episodes of coordinated joint attention.
```{r}
maximal_mod <- lmer(cja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Episodes of passive joint attention.
```{r}
maximal_mod <- lmer(pja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Total duration of passive joint attention.
```{r}
maximal_mod <- lmer(pja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

Total duration of coordinated joint attention.
```{r}
maximal_mod <- lmer(cja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                           (1| Video), data = lmer_data)
summary(maximal_mod)
```

# Conclusions

There is a main effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.

There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes.

There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids. There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.

While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.

### 2020-03-16 parenting_obs_e1/joint_attention_recoded/parenting_obs_JA_recoded.Rmd
switched to rate of JA per min

@@
 
-```{r echo=FALSE}
+```{r include=FALSE}
 rm(list=ls())
@@
 library(Hmisc)
-theme_set(theme_bw())
+theme_set(ggthemes::theme_few() + theme(legend.title = element_text(size=18), legend.text = element_text(size=16), 
+        axis.text.x  = element_text(vjust=0.5, size=16), axis.text.y  = element_text(vjust=0.5, size=16),
+        axis.title.x = element_text(size=18), axis.title.y = element_text(size=18)))
 ```
@@
 
-```{r}
+```{r, echo=F}
+# for rate coding (JA/minute), we coded the start / end of play sessions because they were not exactly 3 minutes
+play_duration <- read.csv("parenting_obs_play_duration_E1.csv", header=T)
+play_duration <- play_duration %>% 
+  mutate(play_duration = play_stop_sec - play_start_sec)
+sort(play_duration$play_duration) # 1 pretty short session: 131 seconds
+summary(play_duration$play_duration) # median = 184.5, mean=185.8
+# use play_duration$verbalcue_start_sec instead of play_start? (when it exists)
+
 combine_datavyu_files <- function(data_dir) {
@@
     # (assumes something happened early in the vid and late in the vid..)
-    vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
-    if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
+    #vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
+    #if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
+    SID = str_replace(f, "_recode.csv", "")
+    vid_duration = play_duration[which(play_duration$SID==SID),]$play_duration
 
@@
     if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))
-    which(jd$phase_length < 3000) # trim episodes <3 seconds long?
 
-    id <- data.frame(SID = str_replace(f, "_recode.csv", ""), # "012017_01_recode"
+    id <- data.frame(SID = SID, # "012017_01_recode"
                    line = jd$JointAttention.ordinal, # numbered list of episodes e.g. 0 1 2 3 4 5 6 7
@@
 
+d.long[which(d.long$phase_length<0),] # 052317_03	7	-93378	0	0	1 (only a bid, so duration doesn't matter)
+
 dim(d.long %>% filter((cja==1 | pja==1) & phase_length<3000)) # 150
@@
 d.raw <- d.long %>% group_by(SID) %>%
-  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
-         phase_length = phase_length / 60000) %>%
+  mutate(vid_duration = vid_duration / 60, # seconds to minutes
+         phase_length = phase_length / 1000) %>% # ms to seconds
   summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
@@
 
-# normalize to rates (e.g., bids/minute)
+# normalize to rates (e.g., bids/minute and seconds / min duration of JA)
+vid_dur = d.raw$vid_duration
 d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
-
+d.raw$vid_duration = vid_dur
 ```
@@
 
+d.long_rel[which(d.long_rel$phase_length<0),] 
+# SID=120916_03	 line=7	 -1275	 0	1	 1	 - cja + bid, so should double-check
+
 dim(d.long_rel %>% filter((cja==1 | pja==1) & phase_length<3000)) # 39
@@
 d.raw_rel <- d.long_rel %>% group_by(SID) %>%
-  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
-         phase_length = phase_length / 60000) %>%
+  mutate(vid_duration = vid_duration / 60, # seconds to minutes
+         phase_length = phase_length / 1000) %>% # ms to seconds
   summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
@@
 ```{r}
-load("Exp1_joint_attention_data_ORIGINAL.RData") # compare Sama to original Exp1 coding
-old <- d %>% select(SID, bids, cja, pja, pja_length, cja_length, total_ja, total_lja, bids_tot)
-
-old %>% summarise(bids = mean(bids), cja=mean(cja), pja=mean(pja), l_pja=mean(pja_length), l_cja=mean(cja_length))
-
 d.raw_rel <- d.raw_rel %>%
@@
 
-d_rel$pja_diff = (d_rel$pja - d_rel$pja_rel) ^ 2
-d_rel$l_pja_diff = (d_rel$l_pja - d_rel$l_pja_rel) ^ 2
-d_rel %>% arrange(pja_diff, l_pja_diff)
-
-# compare old vs. d.raw
-
-cor(d.raw$bids, old$bids) # .35
-cor(d.raw$cja, old$cja) # .53
-cor(d.raw$pja, old$pja) # .34
-cor(d.raw$pja_length, old$pja_length) # .32
-cor(d.raw$cja_length, old$cja_length) # .52
-cor(d.raw$total_ja, old$total_ja) # .27
-cor(d.raw$total_lja, old$total_lja) # .31
-
-psych::ICC(cbind(d.raw$pja, old$pja), missing = FALSE, alpha = 0.05)
-
-mean(d_rel$pja - d_rel$pja_rel, na.rm=T)
-d_rel$pja - d_rel$pja_rel
-
 get_ICC2 <- function(dat)  {
@@
 
-bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")])
+bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .38 [.02, .66]
 
-pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # eps pass JA
+pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # eps pass JA .06 [-.19, .36]
 
-cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # eps coord JA
+cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # eps coord JA .59 [.27, .79]
 
-l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # pass JA length
+l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # pass JA length .15 [-.13, .46]
 
-l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # coord JA length
+l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # coord JA length .37 [-.06, .68]
 
@@
 Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.
-
-# Compare raters
-
-```{r}
-plot(d_rel$pja, d_rel$pja_rel)
-
-plot(d_rel$l_pja, d_rel$l_pja_rel)
-```
 
@@
   xlab("Condition") + 
-  ylab("Total bids for Joint Attention") +
+  ylab("Bids for Joint Attention per Min.") +
   langcog::scale_colour_solarized()  +
@@
   xlab("Condition") + 
-  ylab("Total episodes of Joint Attention") +
+  ylab("Episodes of Joint Attention per Min.") +
   langcog::scale_colour_solarized()  +
@@
   xlab("Condition") + 
-  ylab("Episodes of Passive Joint Attention")  +
+  ylab("Episodes of Passive JA per Min.")  +
   langcog::scale_colour_solarized() + 
@@
   xlab("Condition") + 
-  ylab("Episodes of Coordinated Joint Attention")  +
+  ylab("Episodes of Coordinated JA per Min.")  +
   langcog::scale_colour_solarized()  + 
@@
   xlab("Condition") + 
-  ylab("Total Duration Passive Joint Attention")  +
+  ylab("Seconds of Passive JA per Min.")  +
   langcog::scale_colour_solarized()  +
@@
   xlab("Condition") + 
-  ylab("Total Duration Coordinated Joint Attention")  +
+  ylab("Seconds of Coordinated JA per Min.")  +
   langcog::scale_colour_solarized()  +

### 2020-03-16 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
switched to rate of JA per min

@@
 ```{r echo=F}
+# for rate coding (JA/minute), we coded the start / end of play sessions because they were not exactly 3 minutes
+play_duration <- read.csv("parenting_obs_play_duration_E2.csv", header=T)
+play_duration <- play_duration %>% 
+  mutate(play_duration = play_stop_sec - play_start_sec)
+sort(play_duration$play_duration) # 1 pretty short session: 131 seconds
+summary(play_duration$play_duration) # median = 184.5, mean=185.8
+# use play_duration$verbalcue_start_sec instead of play_start? (when it exists)
+
 combine_datavyu_files <- function(data_dir) {
@@
     # (assumes something happened early in the vid and late in the vid..)
-    vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
-    if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
+    #vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
+    #if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
+    SID = str_replace(f, ".csv", "")
+    vid_duration = play_duration[which(play_duration$sid==SID),]$play_duration
 
@@
     if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))
-    which(jd$phase_length < 3000) # trim episodes <3 seconds long?
 
-    id <- data.frame(SID = str_replace(f, ".csv", ""), # "012017_01_recode"
+    id <- data.frame(SID = SID, 
                    line = jd$JointAttention.ordinal, 
@@
 
+d.long[which(d.long$phase_length<0),] # SID 121317_1  line 17          -68   1   0   1          181
+
 d.long[which(d.long$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)
+# 337 / 1094
 
@@
 d.raw <- d.long %>% group_by(SID) %>%
-  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
-         phase_length = phase_length / 60000) %>%
+  mutate(vid_duration = vid_duration / 60, # seconds to minutes
+         phase_length = phase_length / 1000) %>% # ms to s
   summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
@@
 
-# normalize to rates (e.g., bids/minute)
+# normalize to rates (e.g., bids/minute and seconds / min duration of JA)
+vid_dur = d.raw$vid_duration
 d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
+d.raw$vid_duration = vid_dur
 ```
@@
 
-Import reliability coder's data (20 participants were coded for reliability).
+Import reliability coder's data (25 participants were coded for reliability).
 ```{r}
@@
 d.raw_rel <- d.long_rel %>% group_by(SID) %>%
-  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
-         phase_length = phase_length / 60000) %>%
+  mutate(vid_duration = vid_duration / 60, # seconds to minutes
+         phase_length = phase_length / 1000) %>% # ms to s
   summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
@@
 d.raw_rel[,2:9] = d.raw_rel[,2:9] / d.raw_rel$vid_duration
-
 ```
@@
 
-bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .85
+bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .81 [.62,.91]
 
-pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # .75 eps pass JA
+pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # .74 eps pass JA [.48,.88]
 
-cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # .75 eps coord JA
+cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # .80 eps coord JA [.61,.91]
 
-l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # .73 pass JA length
+l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # .72 pass JA length [.44,.86]
 
-l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # .75 coord JA length
+l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # .88 coord JA length [.75,.94]
 ```
 
-Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.
+Inter-rater reliability is very high for length of coordinated JA (`r round(l_cja_rel$ICC, 2)`), high for bids (`r round(bids_rel$ICC, 2)`) and episodes of coordinated JA (`r round(cja_rel$ICC, 2)`), and not bad for episodes (`r round(pja_rel$ICC, 2)`) and duration of passive JA (`r round(l_pja_rel$ICC, 2)`).
 
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + ylab("Total bids for Joint Attention") +
+  xlab("Condition") + ylab("Bids for Joint Attention per Min.") +
   langcog::scale_colour_solarized() + theme(legend.position="none") 
@@
 
-```{r}
+```{r, echo=F}
 ms_tja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total episodes of Joint Attention") +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Episodes of JA per Min.") 
 ```
@@
 Episodes of passive joint attention.
-```{r}
+```{r, echo=F}
 ms_pja <- d %>%
@@
   xlab("Condition") + 
-  ylab("Episodes of Passive Joint Attention")  +
-  langcog::scale_colour_solarized()
+  ylab("Episodes of Passive JA per Min.") 
 ```
@@
 Episodes of coordinated joint attention
-```{r}
+```{r, echo=F}
 ms_cja <- d %>%
@@
   xlab("Condition") + 
-  ylab("Episodes of Coordinated Joint Attention")  +
-  langcog::scale_colour_solarized()
+  ylab("Episodes of Coordinated JA per Min.") 
 ```
 
-Total duration of passive joint attention.
-```{r}
+Rate of passive joint attention.
+```{r, echo=F}
 ms_lpja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total Duration Passive Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Seconds of Passive JA per Min.") 
 ```
 
-Total duration of coordinated joint attention.
-```{r}
+Rate of coordinated joint attention.
+```{r, echo=F}
 ms_lcja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total Duration Coordinated Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.")
 ```
 
-##Demographics
+## Demographics
 
-###Child gender
+### Child gender
 
 Total bids by gender.
-```{r}
+
+```{r, echo=F}
 # total bids
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total bids for Joint Attention")  +
-  langcog::scale_colour_solarized() 
+             position = position_dodge(width = .9)) +
+  xlab("Condition") + ylab("Bids for Joint Attention per Min.") # look up missing gender: "102518_6" "110418_3"
 ```
 
-Total duration of passive joint attention by gender
-```{r}
+Rate of passive joint attention by gender
+```{r, echo=F}
 ms_lpja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total Duration Passive Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Seconds of Passive JA per Min.") 
 ```
 
-Total duration of coordinated joint attention by gender
-```{r}
+Rate of coordinated joint attention by gender
+
+```{r, echo=F}
 ms_lcja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total Duration Coordinated Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.") 
 ```
 
-###Child age
+### Child age
 
@@
 Total bids by age.
-```{r}
+
+```{r, echo=F}
 # total bids
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total bids for Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Bids for Joint Attention per Min.") 
 ```
 
-Total duration of passive joint attention by age
-```{r}
+Rate of passive joint attention by age
+
+```{r, echo=F}
 ms_lpja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total Duration Passive Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Seconds of Passive JA per Min.") 
 ```
 
-Total duration of coordinated joint attention by age
-```{r}
+Rate of coordinated joint attention by age
+
+```{r, echo=F}
 ms_lcja <- d %>%
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total Duration Coordinated Joint Attention")  +
-  langcog::scale_colour_solarized() 
+  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.") 
 ```
@@
 
-```{r}
+```{r, echo=F}
 cormat <- d %>%
@@
 # Conclusions
+
+As in Exp.
+1, there is a significant effect of video condition on parental bids for JA: parents made more bids after watching an activity video.
+There was also a significant effect of video condition on the number of episodes of coordinated JA, as well as an interaction of condition and age.
+
+There was a significant effect of age on the rate of episodes and duration of passive JA, and on the duration of coordinated JA.

### 2020-03-19 paper/appendix.tex
final pass with rate

--- 2020-01-23 paper/appendix.Rmd
@@
----
-title: "Appendix"
-output: pdf_document
----
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
 
-## Experiment 1 Activities
+\begin{appendix}
+\section{}
+\hypertarget{experiment-1-activities}{%
+\subsection{Experiment 1 Activities}\label{experiment-1-activities}}
 
-### Video A (6-11.9 months) "Pick it up"
+\hypertarget{video-a-6-11.9-months-pick-it-up}{%
+\subsubsection{Video A (6-11.9 months) ``Pick it
+up''}\label{video-a-6-11.9-months-pick-it-up}}
 
-Parents are told to encourage their child to pick up and drop individual objects.
-They are also encouraged to place toys on a small cloth and show the child that they can drag the cloth towards them to reach the toys.
+Parents are told to encourage their child to pick up and drop individual
+objects. They are also encouraged to place toys on a small cloth and
+show the child that they can drag the cloth towards them to reach the
+toys.
 
@@
 
-### Video B (6-11.9 months) "Animal sounds"
+\hypertarget{video-b-6-11.9-months-animal-sounds}{%
+\subsubsection{Video B (6-11.9 months) ``Animal
+sounds''}\label{video-b-6-11.9-months-animal-sounds}}
 
-Parents are told to call different animals and imitate different sounds the animals make. They are also encouraged to observe which animal the child prefers.
+Parents are told to call different animals and imitate different sounds
+the animals make. They are also encouraged to observe which animal the
+child prefers.
 
@@
 
-### Video C (12-17.9 months) "Give me the toy"
+\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video C (12-17.9 months) ``Give me the
+toy''}\label{video-c-12-17.9-months-give-me-the-toy}}
 
-Parents are told to ask their child to hand over individual toys.
-They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child follows the verbal instructions.
 
@@
 
-### Video D (12-17.9 months) "Classifying my toys"
+\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video D (12-17.9 months) ``Classifying my
+toys''}\label{video-d-12-17.9-months-classifying-my-toys}}
 
-Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
 
-Props: two yellow and green rings, big car, small car, big horse, small horse
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
 
-### Video E (18-23.9 months) "My toys"
+\hypertarget{video-e-18-23.9-months-my-toys}{%
+\subsubsection{Video E (18-23.9 months) ``My
+toys''}\label{video-e-18-23.9-months-my-toys}}
 
-Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
-They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
 
@@
 
-### Video F (18-23.9 months) "The Orchestra"
+\hypertarget{video-f-18-23.9-months-the-orchestra}{%
+\subsubsection{Video F (18-23.9 months) ``The
+orchestra''}\label{video-f-18-23.9-months-the-orchestra}}
 
-Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
 
@@
 
-## Experiment 2 Activities
+\hypertarget{experiment-2-activities}{%
+\subsection{Experiment 2 Activities}\label{experiment-2-activities}}
 
-### Video A (12-17.9 months) "Give me the toy"
+\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video A (12-17.9 months) ``Give me the
+toy''}\label{video-a-12-17.9-months-give-me-the-toy}}
 
-Parents are told to ask their child to hand over individual toys.
-They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child follows the verbal instructions.
 
@@
 
-### Video B (12-17.9 months) "Classifying my toys"
+\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video B (12-17.9 months) ``Classifying my
+toys''}\label{video-b-12-17.9-months-classifying-my-toys}}
 
-Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
 
-Props: two yellow and green rings, big car, small car, big horse, small horse
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
 
-### Video C (12-17.9 months) "Geometric shapes jigsaw puzzle"
+\hypertarget{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}{%
+\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigsaw
+puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}}
 
-Parents are told to encourage their child to name different shapes on a jigsaw puzzle. Then they are told to undo the puzzle and invite the child to complete the puzzle.
+Parents are told to encourage their child to name different shapes on a
+jigsaw puzzle. Then they are told to undo the puzzle and invite the
+child to complete the puzzle.
 
@@
 
-### Video D (18-23.9 months) "My toys"
+\hypertarget{video-d-18-23.9-months-my-toys}{%
+\subsubsection{Video D (18-23.9 months) ``My
+toys''}\label{video-d-18-23.9-months-my-toys}}
 
-Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
-They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
 
@@
 
-### Video E (18-23.9 months) "The Orchestra"
+\hypertarget{video-e-18-23.9-months-the-orchestra}{%
+\subsubsection{Video E (18-23.9 months) ``The
+orchestra''}\label{video-e-18-23.9-months-the-orchestra}}
 
-Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
 
@@
 
-### Video F (18-23.9 months) "My Yellow Toys"
+\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
+\subsubsection{Video F (18-23.9 months) ``My yellow
+toys''}\label{video-f-18-23.9-months-my-yellow-toys}}
 
-Parents are told to show their child yellow toys and to ask, "What color are they?" They are also told to give the child toys of different colors, to ask them to only play with the yellow ones, and to praise the child after they do so.
+Parents are told to show their child yellow toys and to ask, ``What
+color are they?'' They are also told to give the child toys of different
+colors, to ask them to only play with the yellow ones, and to praise the
+child after they do so.
 
-Props: blue car, yellow car, yellow block, red block, blue block, green block
+Props: blue car, yellow car, yellow block, red block, blue block, green
+block
+\end{appendix}

### 2020-03-19 paper/manuscript.Rmd
final pass with rate

@@
 #d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
-d = read.csv("exp1_lexical_diversity_data.csv") # old one
+#d = read.csv("exp1_lexical_diversity_data.csv") # old one
 d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns
@@
 e1_gender = table(e1ld$gender)
+
+# rate calculations (tokens / min, words / min)
+e1_dur = read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"))
+e1_dur <- e1_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
+  select(SID, vid_dur)
+e1ld <- e1ld %>% left_join(e1_dur, by=c("sid"="SID"))
+
+# convert types and tokens to rate: types/min and tokens/min
+e1ld <- e1ld %>% 
+  mutate(types = (types / vid_dur), 
+         tokens = (tokens / vid_dur),
+         Conversational_Turns = (Conversational_Turns / vid_dur))
 ```
@@
 ```{r load-exp1-joint-attention-data, echo=F}
-load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
+load(paste0(e1path,"joint_attention/Exp1_joint_attention_data.RData"))
 d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))
@@
 load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+e2Age <- d %>% mutate(Age = age) %>%
+  select(sid, Age)
 e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
@@
 d = read.csv("../exp2_lexical_diversityAdd.csv")
+d <- d %>% left_join(e2Age, by="sid")
 
@@
          gender = as.factor(gender),
-         video = as.factor(video))
+         video = as.factor(video)) %>%
+  select(-X.1, -X)
 
@@
 e2_gender = table(d$gender)
-e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled
+e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled ToDo
 e2_18to24 = nrow(subset(d, Age>=1.5))
+
+e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
+e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
+  select(sid, vid_dur)
+e2data <- e2data %>% left_join(e2_dur, by="sid")
+
+# convert types and tokens to rate: types/min and tokens/min
+e2data <- e2data %>% 
+  mutate(types = (types / vid_dur), 
+         tokens = (tokens / vid_dur),
+         Conversational_Turns = (Conversational_Turns / vid_dur))
 ```
@@
 Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
-The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
+The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
 In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for number of parent bids for JA; ICC = 0.34 with 95% CI = [-0.11,0.67] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for total duration of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11,0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32,0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for rate (seconds per minute) of coordinated JA episodes.
 
@@
 
-For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
+For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
 Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
@@
 summary(tokens_mod)
-e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.5
+e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 19.45
 p_direction(tokens_mod, effects="all") # orchestra 89.7%
@@
 summary(types_mod) # nothing 
-p_direction(types_mod, effects="all")
+p_direction(types_mod, effects="all") # condition 83%, age 92.5%..
 
 e1_lexdiv <- e1ld %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
+  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) # types=mean(types) # con=16.7, exp=18.1
 ```
@@
 get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
-p_direction(modTTRE, effects="all") # EL 84.9%, RR 83.3%, parent_ed 91.7%
+p_direction(modTTRE, effects="all") # EL 75, RR 86%, parent_ed 83.5
 
@@
 summary(modMTLDE) #
-p_direction(modMTLDE, effects="all") # EL 78.5% AA 89.2% RR 86.6% genderM 87.8% parent_ed 91.5%
+p_direction(modMTLDE, effects="all") # RR 81.5% genderM 88.9%
 
@@
 summary(tokens_modE) # condition 54.4 
-get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # SHOULD REPORT
-p_direction(tokens_modE, effects="all") # RR 75.7% parent_ed 95.1%
+get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # 
+p_direction(tokens_modE, effects="all") # RR 71% parent_ed 90%
 
@@
 summary(types_modE) 
-p_direction(types_modE, effects="all") # EL 87.2% AA 77.7% genderM 88.3%, parent_ed 91.7% cond:AA 94.5%
+p_direction(types_modE, effects="all") # EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
 get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
@@
 
-# predict # of conversational turns
+# predict # of conversational turns - COULD REPORT THIS
 modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
 summary(modCT) 
-get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .92
+get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .96 mean=2.52 [-.20,5.28]
+p_direction(modCT, effects="all")
 # E1 CT: exp early significant (+ effect)
-# E2 CT: age nearly significany (+ effect)
+# E2 CT: age nearly significant (+ effect)
 ```
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
 int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
@@
   geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
+  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
@@
   geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
+  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
@@
 summary(e1bids_mod) 
-e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # 2.59
+e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # .72
+p_direction(e1bids_mod, effects="all")
 
@@
 summary(e1tja_mod) # NA
+p_direction(e1tja_mod, effects="all")
 
@@
 summary(e1tjadur_mod) # NA
+p_direction(e1tjadur_mod, effects="all") # condition 91%
 
@@
 summary(e1pja_mod) # NA
+p_direction(e1pja_mod, effects="all") # condition 84.5%
 
@@
 summary(e1cja_mod) # NA
+p_direction(e1cja_mod, effects="all") # condition 80%
 
@@
 summary(e1pja_time_mod) # NA
+p_direction(e1pja_time_mod, effects="all") # condition 85.7%
 
@@
 summary(e1cja_time_mod) # NA
+p_direction(e1cja_time_mod, effects="all") # cond*age 85%
 ```
+
+We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
+Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
+There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
+Figure \@ref(fig:JA) (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.
+
+### Exploratory Analyses
 
@@
 
-# Total number of bids
+# Rate of parental bids
 e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
-summary(e1bids_modE) # cond, almost gender
+summary(e1bids_modE) # cond, gender 
+e1bidsE = get_stan_glmer_reporting_values(e1bids_modE, "genderM") # .73 [.11,1.36] REPORT 
+p_direction(e1bids_modE, effects="all")
 
@@
 summary(e1cja_modE) # NA
+p_direction(e1cja_modE, effects="all") # RR 86% parent_ed 89%
 
@@
 summary(e1pja_modE) # condition*RR beta=1.8, RR close
-get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.09, 95% CI = [-2.22,0.07] % report % posterior <0?
-e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")
+e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 95% CI = [-.65,-.02]  REPORT
+#e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed") # -.23 [-.47,.02] pd=.97 REPORT?
+e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR") # .60 [.14,1.05]
+p_direction(e1pja_modE, effects="all")
 
@@
 summary(e1pja_time_modE) # NA
+p_direction(e1pja_time_mod, effects="all") # condition 85.7%
 
@@
 summary(e1cja_time_modE) # NA
+p_direction(e1cja_time_mod, effects="all") # condition 85.1%
 ```
-
-We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-There were more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
-Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no notable effects on the number of or total duration of coordinated or passive JA episodes.
-Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
-
-### Exploratory Analyses
 
@@
 These models included random intercepts per video. 
-Of these exploratory regressions, only the regression predicting the number of passive JA episodes showed an effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaRR['95pLB']`,`r e1pjaRR['95pUB']`]).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]).
 
@@
   geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
+  xlab("Condition") + ylab("Parental Bids for JA per Minute") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
@@
   geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
+  xlab("Condition") + ylab("Episodes of JA per Minute") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
@@
   geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Bids for Joint Attention") + 
+  xlab("Condition") + ylab("Parental Bids for JA per Minute") + 
   scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
@@
   geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
+  xlab("Condition") + ylab("Episodes of JA per Minute") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
@@
   geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
-  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
+  xlab("Age (years)") + ylab("Episodes of JA per Minute") +
   ggthemes::theme_few() + ggtitle(" ") + small_text + 
@@
 summary(e2TTR_m) # conditionexp beta=-.1 95% CI=[-.2,0.0]
-e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp")
+e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
+p_direction(e2TTR_m, effects="all") # age 85.6% age:cond 78%
 
@@
 p_direction(e2tokens_m, effects="all") 
-# conditionexp 90.3%, age:conditionexp 83.1%  video:big_small 96.3%, video:orchestra 94.5%
-launch_shinystan(e2tokens_m, ppd = FALSE)
-summary(e2tokens_m, 
-        pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"),
-        probs = c(0.025, 0.975),
-        digits = 2)
-plot(e2tokens_m)
+#launch_shinystan(e2tokens_m, ppd = FALSE)
+#summary(e2tokens_m, 
+#        pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"),
+#        probs = c(0.025, 0.975),
+#        digits = 2)
+#plot(e2tokens_m)
 #prior_summary(object = e2tokens_m)
@@
 summary(e2MTLD_m) # NA
+p_direction(e2MTLD_m, effects="all") # cond 77.9% age:cond 84.2%
 
@@
   geom_point(data=e2data, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Types") +
+  xlab("Condition") + ylab("Word Types per Minute") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
@@
 e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")
+p_direction(e2bids_m, effects="all") # age 82%
 
@@
 e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionActivity Video")
-
+p_direction(e2tja_m, effects="all") # age, cond, age:cond
 ```
 
-We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made notably more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
+We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
@@
 
-The regression predicting the number of episodes of JA revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
+The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-Older children also participated in fewer episodes of JA ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]). 
-However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in fewer episodes of JA after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]). 
+However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 e2cja_m <- stan_lmer(cja ~ age * Condition + (1 | video), data = e2ja)
-summary(e2cja_m) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
+summary(e2cja_m) #
 e2cjaCond <- get_stan_glmer_reporting_values(e2cja_m, "ConditionActivity Video")
 e2cjaAgeCond <- get_stan_glmer_reporting_values(e2cja_m, "age:ConditionActivity Video")
-# age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
-# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
-# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
-# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6
+p_direction(e2cja_m, effects="all") # cond, age:cond
 
@@
 e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")
+p_direction(e2pja_m, effects="all") # age
 
@@
 e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")
+p_direction(e2pjat_m, effects="all") # age
 
@@
 e2cjat <- get_stan_glmer_reporting_values(e2cjat_m, "age")
+p_direction(e2cjat_m, effects="all") # age, cond 84.4%, age:cond 86.2%
 
 e2tjat_m <- stan_glmer(total_lja ~ age * Condition + (1|video), data=e2ja)
-summary(e2tjat_m) # anything here?
-
+summary(e2tjat_m) # anything here? close!
+p_direction(e2tjat_m, effects="all") # age 85.3%, cond 89%, age:cond 90.4%
 ```
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
-The regression predicting the total duration of coordinated JA episodes found no notable effects.
+The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in more episodes of passive JA with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), and spent more total time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
-In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
+In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
 In some cases--especially in older children--these bids were successful in increasing engagement. 

### 2020-03-19 paper/manuscript.tex
final pass with rate

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
            pdfauthor={George Kachergis, Emily Hembacher, Veronica Cristiano, Hanwen Vivian Zhang, \& Michael C. Frank},
            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided play},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\shorttitle{Impacts of videos on parent-child interaction}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} Gallaudet University\\\textsuperscript{4} Cornell University}
\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4629}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers
\usepackage{float}

\title{Understanding the impacts of video-guided activities on parent-child interaction}
\author{George Kachergis\textsuperscript{1}, Emily Hembacher\textsuperscript{2}, Veronica Cristiano\textsuperscript{3}, Hanwen Vivian Zhang\textsuperscript{4}, \& Michael C. Frank\textsuperscript{1}}
\date{}

\authornote{

Correspondence concerning this article should be addressed to Michael C. Frank, Stanford, CA 94305 USA. E-mail: \href{mailto:mcfrank@stanford.edu}{\nolinkurl{mcfrank@stanford.edu}}}

\abstract{
Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
The rise of phone- and tablet-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions.
We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention.
Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.

}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008). Thus, because of the potential for large downstream effects (Heckman, 2006), there is tremendous interest in interventions that change children's language environment.
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions.
Many effective parenting interventions require large resource investments and require many hours of in-person contact (Gertler et al., 2014; Schweinhart et al., 2004), making implementation at scale a daunting proposition.
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices.
But what do parents take away from these short messages about what to do with or how to talk with their children?

The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities.
A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see Breitenstein, Gross, \& Christophersen, 2014).
For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51\% attendance vs.~85\% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior (Breitenstein, Fogg, Ocampo, Acosta, \& Gross, 2016).
Often, however, the theory of change presupposed by such interventions is relatively vague.
Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.

This theory of change is typically grounded in ideas about guided play and early language stimulation.
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play?
Alternatively, by focusing parents on a specific activity, this theory could be flawed, causing parents to over-focus on achieving the superficial goals of the activity.
This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
Another possibility is that these messages might produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.

Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages?
In two experiments, we collected data from parent-child dyads in a local children's museum.
We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification.
Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2).
We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

\hypertarget{method}{%
\subsection{Method}\label{method}}

\hypertarget{participants.}{%
\subsubsection{Participants.}\label{participants.}}

53 infants (F = 38, M = 15) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

\hypertarget{materials.}{%
\subsubsection{Materials.}\label{materials.}}

Stimuli included activity videos from a commercial parenting application.
The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
In each video, an adult and child perform the activity (e.g., sorting toys according to size) while a narrator explains the activity and its purpose.
We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months).
Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.\footnote{Details of the specific videos used and the toys associated with each video are in the Appendix.}

Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2018).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

\hypertarget{procedure.}{%
\subsubsection{Procedure.}\label{procedure.}}

After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed.
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.\footnote{Based on piloting, we estimated these activities would would only require three minutes to complete.}
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes.
They were not given any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech.
After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.

\hypertarget{joint-attention-coding-procedure.}{%
\subsubsection{Joint Attention Coding Procedure.}\label{joint-attention-coding-procedure.}}

The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014).
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA.
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA.
If more than 3 seconds elapsed between bids, they were coded as separate attempts.
An episode of joint attention was considered \emph{passive} if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent.
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention.
A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
Full details of our guidelines for coding joint attention are available in SI.

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55,0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11,0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32,0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11,0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24,0.82{]} for rate (seconds per minute) of coordinated JA episodes.

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

Parents' child-directed speech during the play sessions was transcribed.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

\hypertarget{lexical-diversity}{%
\subsubsection{Lexical Diversity}\label{lexical-diversity}}

For each transcript, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy \& Jarvis (2010): 0.720).

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior falls.
There was lower TTR in the Activity Video condition (mean: 0.33) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.05{]}).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 18.55) than in the No Video condition (mean: 27.09, \(\beta=\)-8.48, 95\% CI={[}-15.48,-1.45{]}), with no predicted influence of age.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 19.45, 95\% CI={[}8.93,30.24{]}), with parents using more words in the Activity Video condition (mean: 60, bootstrapped 95\% confidence interval (conf. int.): {[}193,259{]}) than in the No Video condition (mean: 41, 95\% conf. int.: {[}139,194{]}).

\begin{figure}[H]

{\centering \includegraphics{figs/fig-lexdiv-1}

}

\caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\% confidence intervals, and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
\end{figure}

\hypertarget{joint-attention}{%
\subsubsection{Joint Attention}\label{joint-attention}}

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.15,1.27{]}).
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

\hypertarget{exploratory-analyses}{%
\subsubsection{Exploratory Analyses}\label{exploratory-analyses}}

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.65,-0.02{]}).
However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.11,1.04{]}).

To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
Words that are strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that are most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

\begin{figure}[H]

{\centering \includegraphics{figs/fig-JA-1}

}

\caption{\label{fig:JA} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1 (top). For Experiment 2 (bottom), mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right).}\label{fig:fig-JA}
\end{figure}

\hypertarget{discussion}{%
\subsubsection{Discussion}\label{discussion}}

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable:
after the Activity Video, parents used more words related to requests (e.g., \enquote{Can I have X? / Give me X. Thank you!}), whereas after no intervention parents' language related more to invitations (e.g., \enquote{Are you ready?} / \enquote{Let's see.}).
However, parents who watched an activity video also made more bids for JA with their child.
While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.\footnote{Preregistration: \url{https://osf.io/2bpdf/}.}

\hypertarget{method-1}{%
\subsection{Method}\label{method-1}}

\hypertarget{participants.-1}{%
\subsubsection{Participants.}\label{participants.-1}}

84 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).

\hypertarget{materials.-1}{%
\subsubsection{Materials.}\label{materials.-1}}

The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies.
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
Details of the videos used in the Activity Video conditions are in the Appendix.

\hypertarget{procedure.-1}{%
\subsubsection{Procedure.}\label{procedure.-1}}

The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1.
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48,0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61,0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44,0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75,0.94{]} for total duration of coordinated JA episodes.

\hypertarget{results-and-discussion-1}{%
\subsection{Results and Discussion}\label{results-and-discussion-1}}

Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

\hypertarget{lexical-diversity-1}{%
\subsubsection{Lexical Diversity}\label{lexical-diversity-1}}

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15,-0.04{]}).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

\begin{table}

\caption{\label{tab:e2tab}\label{e2tab} Lexical diversity measures in Experiment 2.}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
\hline
Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
\hline
Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 25.14 & 9.2 & 55.30 & 23.69\\
\hline
Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 20.31 & 8.7 & 59.42 & 30.51\\
\hline
\end{tabular}
\end{table}

\hypertarget{joint-attention-1}{%
\subsubsection{Joint Attention}\label{joint-attention-1}}

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf. int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 95\% CI = {[}0.39,1.64{]}) than after the Science Video (mean: 3.18, 95\% conf. int.: {[}2.81, 3.54{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 95\% CI = {[}0.08,0.93{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf. int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.13, 2.61{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 95\% CI = {[}-2.64,-0.37{]}).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 95\% CI = {[}-0.02,3.23{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

\hypertarget{exploratory-analyses-1}{%
\subsubsection{Exploratory Analyses}\label{exploratory-analyses-1}}

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 95\% CI = {[}0.06,0.84{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
There was an interaction of age and condition (\(\beta=1.60\), 95\% CI = {[}0.15,3.18{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.

Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 95\% CI = {[}-1.64,0.02{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 95\% CI = {[}-0.01,0{]}).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that are strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that are most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.

\begin{figure}[H]

{\centering \includegraphics{figs/e2ja-coord-1}

}

\caption{The number of episodes of coordinated JA by condition and age in Experiment 2.}\label{fig:e2ja-coord}
\end{figure}

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

We were interested in how digital parenting advice alters parents' interactions with their children.
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions.
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
In some cases--especially in older children--these bids were successful in increasing engagement.
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}), often asking about animal noises (\enquote{What does the X say?}).

The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions.
Why were they successful?
When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child.
Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.

Our study has a number of limitations related to design and sample, each of which suggests possible future directions.
First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
A longer-term study would also address whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
Second, our design assumes that parents have access to the materials needed to complete the suggested activities; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
Providing materials may be critical for the success of activity suggestions.
Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research.
A key goal for future research is to assess the generality of these findings across populations.

In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Baldwin1991}{}%
Baldwin, D. (1991). Infants' contribution to the achievement of joint reference. \emph{Child Development}, \emph{62}, 875--890.

\leavevmode\hypertarget{ref-Bigelow2004}{}%
Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint attention in the development of infants' play with objects. \emph{Developmental Science}, \emph{7}, 518--526.

\leavevmode\hypertarget{ref-Breitenstein2016}{}%
Breitenstein, S. M., Fogg, L., Ocampo, E. V., Acosta, D. I., \& Gross, D. (2016). Parent use and efficacy of a self-administered, tablet-based parent training intervention: A randomized controlled trial. \emph{JMIR mHealth and uHealth}, \emph{4}(2), e36. \url{http://doi.org/10.2196/mhealth.5202}

\leavevmode\hypertarget{ref-Breitenstein2014}{}%
Breitenstein, S. M., Gross, D., \& Christophersen, R. (2014). Digital delivery methods of parenting training interventions: A systematic review. \emph{Worldviews on Evidence-Based Nursing}, \emph{11}, 168--176.

\leavevmode\hypertarget{ref-Cartmill2013}{}%
Cartmill, E. A., Armstrong, B. F., Gleitman, L. R., Goldin-Meadow, S., Medina, T. N., \& Trueswell, J. C. (2013). Quality of early parent input predicts child vocabulary 3 years later. \emph{Proceedings of the National Academy of Sciences}, \emph{110}(28), 11278--11283. \url{http://doi.org/10.1073/pnas.1309518110}

\leavevmode\hypertarget{ref-Jamaica2014}{}%
Gertler, P., Heckman, J., Pinto, R., Zanolini, A., Vermeersch, C., Walker, S., \ldots{} Grantham-McGregor, S. (2014). Labor market returns to an early childhood stimulation intervention in jamaica. \emph{Science}, \emph{344}(6187), 998--1001. \url{http://doi.org/10.1126/science.1251178}

\leavevmode\hypertarget{ref-rstanarm}{}%
Goodrich, B., Gabry, J., Ali, I., \& Brilleman, S. (2018). Rstanarm: Bayesian applied regression modeling via Stan. Retrieved from \url{http://mc-stan.org/}

\leavevmode\hypertarget{ref-Hart1995}{}%
Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the everyday experience of young american children}. Baltimore, MD: Brookes.

\leavevmode\hypertarget{ref-Heckman2006}{}%
Heckman, J. J. (2006). Skill formation and the economics of investing in disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902. \url{http://doi.org/10.1126/science.1128898}

\leavevmode\hypertarget{ref-Hembacher2018}{}%
Hembacher, E., \& Frank, M. C. (2018). The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development. \emph{PsyArXiv}. \url{http://doi.org/10.31234/osf.io/hxk3d}

\leavevmode\hypertarget{ref-HirshPasek2015}{}%
Hirsh-Pasek, K., Adamson, L. B., Bakeman, R., Owen, M. T., Golinkoff, R. M., Pace, A., \ldots{} Suma, K. (2015). The contribution of early communication quality to low-income children's language success. \emph{Psychological Science}, \emph{26}(7), 1071--1083. \url{http://doi.org/10.1177/0956797615581493}

\leavevmode\hypertarget{ref-spacy2}{}%
Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language understanding with bloom embeddings, convolutional neural networks and incremental parsing. \emph{To Appear}.

\leavevmode\hypertarget{ref-Malvern2004}{}%
Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). \emph{Lexical diversity and language development}. Palgrave Macmillan.

\leavevmode\hypertarget{ref-Marchman2008}{}%
Marchman, V. A., \& Fernald, A. (2008). Speed of word recognition and vocabulary knowledge in infancy predict cognitive and language outcomes in later childhood. \emph{Developmental Science}, \emph{11}, F9--F16.

\leavevmode\hypertarget{ref-McCarthy2010}{}%
McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A validation study of sophisticated approaches to lexical diversity assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.

\leavevmode\hypertarget{ref-PerryPreschool2004}{}%
Schweinhart, L. J., Montie, J., Xiang, Z., Barnett, W. S., Belfield, C. R., \& Nores, M. (2004). \emph{Lifetime effects: The highscope perry preschool study through age 40}. Ypsilanti, MI: HighScope Press.

\leavevmode\hypertarget{ref-datavyu}{}%
Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}. Retrieved from \url{http://datavyu.org}

\leavevmode\hypertarget{ref-Weisberg2013}{}%
Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain, and Education}, \emph{7}, 104--112.

\leavevmode\hypertarget{ref-Wood1976}{}%
Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in problem solving. \emph{Journal of Child Psychology and Psychiatry}, \emph{17}, 89--100.

\leavevmode\hypertarget{ref-Baldwin1991}{}%
Baldwin, D. (1991). Infants' contribution to the achievement of joint reference. \emph{Child Development}, \emph{62}, 875--890.

\leavevmode\hypertarget{ref-Bigelow2004}{}%
Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint attention in the development of infants' play with objects. \emph{Developmental Science}, \emph{7}, 518--526.

\leavevmode\hypertarget{ref-Breitenstein2016}{}%
Breitenstein, S. M., Fogg, L., Ocampo, E. V., Acosta, D. I., \& Gross, D. (2016). Parent use and efficacy of a self-administered, tablet-based parent training intervention: A randomized controlled trial. \emph{JMIR mHealth and uHealth}, \emph{4}(2), e36. \url{http://doi.org/10.2196/mhealth.5202}

\leavevmode\hypertarget{ref-Breitenstein2014}{}%
Breitenstein, S. M., Gross, D., \& Christophersen, R. (2014). Digital delivery methods of parenting training interventions: A systematic review. \emph{Worldviews on Evidence-Based Nursing}, \emph{11}, 168--176.

\leavevmode\hypertarget{ref-Cartmill2013}{}%
Cartmill, E. A., Armstrong, B. F., Gleitman, L. R., Goldin-Meadow, S., Medina, T. N., \& Trueswell, J. C. (2013). Quality of early parent input predicts child vocabulary 3 years later. \emph{Proceedings of the National Academy of Sciences}, \emph{110}(28), 11278--11283. \url{http://doi.org/10.1073/pnas.1309518110}

\leavevmode\hypertarget{ref-Jamaica2014}{}%
Gertler, P., Heckman, J., Pinto, R., Zanolini, A., Vermeersch, C., Walker, S., \ldots{} Grantham-McGregor, S. (2014). Labor market returns to an early childhood stimulation intervention in jamaica. \emph{Science}, \emph{344}(6187), 998--1001. \url{http://doi.org/10.1126/science.1251178}

\leavevmode\hypertarget{ref-rstanarm}{}%
Goodrich, B., Gabry, J., Ali, I., \& Brilleman, S. (2018). Rstanarm: Bayesian applied regression modeling via Stan. Retrieved from \url{http://mc-stan.org/}

\leavevmode\hypertarget{ref-Hart1995}{}%
Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the everyday experience of young american children}. Baltimore, MD: Brookes.

\leavevmode\hypertarget{ref-Heckman2006}{}%
Heckman, J. J. (2006). Skill formation and the economics of investing in disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902. \url{http://doi.org/10.1126/science.1128898}

\leavevmode\hypertarget{ref-Hembacher2018}{}%
Hembacher, E., \& Frank, M. C. (2018). The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development. \emph{PsyArXiv}. \url{http://doi.org/10.31234/osf.io/hxk3d}

\leavevmode\hypertarget{ref-HirshPasek2015}{}%
Hirsh-Pasek, K., Adamson, L. B., Bakeman, R., Owen, M. T., Golinkoff, R. M., Pace, A., \ldots{} Suma, K. (2015). The contribution of early communication quality to low-income children's language success. \emph{Psychological Science}, \emph{26}(7), 1071--1083. \url{http://doi.org/10.1177/0956797615581493}

\leavevmode\hypertarget{ref-spacy2}{}%
Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language understanding with bloom embeddings, convolutional neural networks and incremental parsing. \emph{To Appear}.

\leavevmode\hypertarget{ref-Malvern2004}{}%
Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). \emph{Lexical diversity and language development}. Palgrave Macmillan.

\leavevmode\hypertarget{ref-Marchman2008}{}%
Marchman, V. A., \& Fernald, A. (2008). Speed of word recognition and vocabulary knowledge in infancy predict cognitive and language outcomes in later childhood. \emph{Developmental Science}, \emph{11}, F9--F16.

\leavevmode\hypertarget{ref-McCarthy2010}{}%
McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A validation study of sophisticated approaches to lexical diversity assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.

\leavevmode\hypertarget{ref-PerryPreschool2004}{}%
Schweinhart, L. J., Montie, J., Xiang, Z., Barnett, W. S., Belfield, C. R., \& Nores, M. (2004). \emph{Lifetime effects: The highscope perry preschool study through age 40}. Ypsilanti, MI: HighScope Press.

\leavevmode\hypertarget{ref-datavyu}{}%
Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}. Retrieved from \url{http://datavyu.org}

\leavevmode\hypertarget{ref-Weisberg2013}{}%
Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain, and Education}, \emph{7}, 104--112.

\leavevmode\hypertarget{ref-Wood1976}{}%
Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in problem solving. \emph{Journal of Child Psychology and Psychiatry}, \emph{17}, 89--100.

\endgroup

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\hypertarget{experiment-1-activities}{%
\subsection{Experiment 1 Activities}\label{experiment-1-activities}}

\hypertarget{video-a-6-11.9-months-pick-it-up}{%
\subsubsection{Video A (6-11.9 months) ``Pick it
up''}\label{video-a-6-11.9-months-pick-it-up}}

Parents are told to encourage their child to pick up and drop individual
objects. They are also encouraged to place toys on a small cloth and
show the child that they can drag the cloth towards them to reach the
toys.

Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car

\hypertarget{video-b-6-11.9-months-animal-sounds}{%
\subsubsection{Video B (6-11.9 months) ``Animal
sounds''}\label{video-b-6-11.9-months-animal-sounds}}

Parents are told to call different animals and imitate different sounds
the animals make. They are also encouraged to observe which animal the
child prefers.

Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls

\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video C (12-17.9 months) ``Give me the
toy''}\label{video-c-12-17.9-months-give-me-the-toy}}

Parents are told to ask their child to hand over individual toys. They
are also encouraged to praise the child after they give them the toys,
and repeat the process until the child follows the verbal instructions.

Props: toy boat, plastic frog, plastic elephant, toy bus

\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video D (12-17.9 months) ``Classifying my
toys''}\label{video-d-12-17.9-months-classifying-my-toys}}

Parents are told to place toys of different sizes (big or small) in two
hoops. They are also encouraged to ask their child to distinguish
between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small
horse

\hypertarget{video-e-18-23.9-months-my-toys}{%
\subsubsection{Video E (18-23.9 months) ``My
toys''}\label{video-e-18-23.9-months-my-toys}}

Parents are told to show the child toys of the same shape but different
sizes, to place one of the objects in a basket and to ask the child to
take out the object. They are also encouraged to ask their child if the
object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

\hypertarget{video-f-18-23.9-months-the-orchestra}{%
\subsubsection{Video F (18-23.9 months) ``The
orchestra''}\label{video-f-18-23.9-months-the-orchestra}}

Parents are told to give their child a musical instrument to play. They
are also encouraged to play a song and see if the child follows the
rhythm.

Props: maracas, drum, tambourine, clapper

\hypertarget{experiment-2-activities}{%
\subsection{Experiment 2 Activities}\label{experiment-2-activities}}

\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video A (12-17.9 months) ``Give me the
toy''}\label{video-a-12-17.9-months-give-me-the-toy}}

Parents are told to ask their child to hand over individual toys. They
are also encouraged to praise the child after they give them the toys,
and repeat the process until the child follows the verbal instructions.

Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow

\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video B (12-17.9 months) ``Classifying my
toys''}\label{video-b-12-17.9-months-classifying-my-toys}}

Parents are told to place toys of different sizes (big or small) in two
hoops. They are also encouraged to ask their child to distinguish
between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small
horse

\hypertarget{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}{%
\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigsaw
puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}}

Parents are told to encourage their child to name different shapes on a
jigsaw puzzle. Then they are told to undo the puzzle and invite the
child to complete the puzzle.

Props: A jigsaw puzzle of geometric shapes

\hypertarget{video-d-18-23.9-months-my-toys}{%
\subsubsection{Video D (18-23.9 months) ``My
toys''}\label{video-d-18-23.9-months-my-toys}}

Parents are told to show the child toys of the same shape but different
sizes, to place one of the objects in a basket and to ask the child to
take out the object. They are also encouraged to ask their child if the
object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

\hypertarget{video-e-18-23.9-months-the-orchestra}{%
\subsubsection{Video E (18-23.9 months) ``The
orchestra''}\label{video-e-18-23.9-months-the-orchestra}}

Parents are told to give their child a musical instrument to play. They
are also encouraged to play a song and see if the child follows the
rhythm.

Props: maracas, drum, tambourine, clapper

\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
\subsubsection{Video F (18-23.9 months) ``My yellow
toys''}\label{video-f-18-23.9-months-my-yellow-toys}}

Parents are told to show their child yellow toys and to ask, ``What
color are they?'' They are also told to give the child toys of different
colors, to ask them to only play with the yellow ones, and to praise the
child after they do so.

Props: blue car, yellow car, yellow block, red block, blue block, green
block
\end{appendix}

\end{document}

### 2020-03-26 paper/appendix.Rmd
renamed files and adjusted to calculated rate of JA episodes (per minute)
Mike and Emily edits, fixed NAs

@@
 ---
-title: "Appendix"
+title: "Appendix: Activity Videos"
 output: pdf_document
@@
 Parents are told to ask their child to hand over individual toys.
-They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
+They are also encouraged to praise the child after they give them the toys, and repeat the process until the child follows the verbal instructions.
 
@@
 
-### Video F (18-23.9 months) "The Orchestra"
+### Video F (18-23.9 months) "The orchestra"
 
@@
 
-### Video E (18-23.9 months) "The Orchestra"
+### Video E (18-23.9 months) "The orchestra"
 
@@
 
-### Video F (18-23.9 months) "My Yellow Toys"
+### Video F (18-23.9 months) "My yellow toys"
 

### 2020-03-26 paper/manuscript.Rmd
Mike and Emily edits, fixed NAs

@@
 e1path = "../parenting_obs_e1/"
-load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+
+d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns, but only has 53 subjects !!
+
 e1_parent_ed = table(d$parent_ed)
-#d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
-#d = read.csv("exp1_lexical_diversity_data.csv") # old one
-d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns
 
@@
          Conversational_Turns = (Conversational_Turns / vid_dur))
+
+e1_6to12 = table(subset(e1ld, age<1)$condition) # con 9, exp 10
+e1_12to18 = table(subset(e1ld, age<1.5 & age>=1)$condition) # con 11 exp 9
+e1_18to24 = table(subset(e1ld, age>=1.5)$condition) # con 10, exp 11
 ```
@@
 e2_gender = table(d$gender)
-e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled ToDo
-e2_18to24 = nrow(subset(d, Age>=1.5))
+e2_12to18 = table(subset(d, Age<1.5)$Condition) # Activity Vid 20, Science Vid 21
+e2_18to24 = table(subset(d, Age>=1.5)$Condition) # Activity Vid 22, Science Vid 21
 
@@
 But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
-Alternatively, by focusing parents on a specific activity, this theory could be flawed, causing parents to over-focus on achieving the superficial goals of the activity. 
+Alternatively, by focusing parents on a specific activity, this approach could be flawed, causing parents to over-focus on achieving the superficial goals of the activity. 
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
@@
 ### Participants. 
-`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
+`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
@@
 The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
-Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
+Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
 The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55,0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11,0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32,0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11,0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24,0.82] for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.
 
@@
 
-Parents' child-directed speech during the play sessions was transcribed.
+Parents' child-directed speech during the play sessions was transcribed; child utterances were not considered.
 Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
@@
 
-[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
+[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf)
 
@@
 
-For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
-Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
+For each transcript of child-directed speech, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
+Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
 Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).
@@
 summary(modTTR) 
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14
 p_direction(modTTR, effects="all") # orchestra 78.7%
@@
 For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior falls.
-There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no predicted influence of age.
+There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`, `r e1TTR['95pUB']`]).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`, `r e1MTLD['95pUB']`]), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`, `r e1tokens['95pUB']`]), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
 int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
+Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`, `r e1bids['95pUB']`]).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 These models included random intercepts per video. 
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaRR['95pLB']`,`r e1pjaRR['95pUB']`]).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaRR['95pLB']`, `r e1pjaRR['95pUB']`]).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`, `r e1pjaE['95pUB']`]).
 
-To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
-Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that are most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
+To better understand the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
 
@@
 While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
-In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
+In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, expand the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
 
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.[^4]
 
-[^4]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).
+[^4]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf).
 
@@
 ### Participants. 
-`r nrow(e2data)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+`r nrow(e2data)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
+(`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
+`r e2_12to18["Science Video"]` 12-17.9 month-olds in the Science Video condition; 
+`r e2_18to24["Activity Video"]` 18-24 month-olds in the Activity Video condition;
+`r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
-The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48,0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61,0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for total duration of coordinated JA episodes.
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
+This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`, `r e2TTR['95pUB']`]).
 The preregistered regression predicting the number of tokens used by parents revealed no effects. 
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`, `r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
+The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`, `r e2tjaCond["95pUB"]`]), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]). 
-However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`, `r e2tjaAge["95pUB"]`]). 
+However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`, `r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`, `r e2cjaCond["95pUB"]`]), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`, `r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`, `r e2pja["95pUB"]`]), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`, `r e2pjat["95pUB"]`]).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
-The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".
+The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".
 
@@
 We were interested in how digital parenting advice alters parents' interactions with their children. 
-We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions. 
+We specifically set out to test whether activity suggestions led to higher-quality play, a presupposition of many early parenting interventions. 
 Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
 In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
-In some cases--especially in older children--these bids were successful in increasing engagement. 
+In some cases---especially in older children---these bids were successful in increasing engagement. 
 We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).

### 2020-03-26 paper/manuscript.tex
Mike and Emily edits, fixed NAs

@@
 But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play?
-Alternatively, by focusing parents on a specific activity, this theory could be flawed, causing parents to over-focus on achieving the superficial goals of the activity.
+Alternatively, by focusing parents on a specific activity, this approach could be flawed, causing parents to over-focus on achieving the superficial goals of the activity.
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
@@
 
-53 infants (F = 38, M = 15) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
+60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
@@
 The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
-Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2018).
+Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
 The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55,0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11,0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32,0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11,0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24,0.82{]} for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.
 
@@
 
-Parents' child-directed speech during the play sessions was transcribed.
-Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or exploratory analyses noted.
+Parents' child-directed speech during the play sessions was transcribed; child utterances were not considered.
+Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
@@
 
-For each transcript, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
-Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
+For each transcript of child-directed speech, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
+Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
 Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy \& Jarvis (2010): 0.720).
@@
 For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior falls.
-There was lower TTR in the Activity Video condition (mean: 0.33) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.05{]}).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 18.55) than in the No Video condition (mean: 27.09, \(\beta=\)-8.48, 95\% CI={[}-15.48,-1.45{]}), with no predicted influence of age.
+There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 95\% CI={[}-0.29, 0.01{]}).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 95\% CI={[}-26.25, 12.20{]}), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 19.45, 95\% CI={[}8.93,30.24{]}), with parents using more words in the Activity Video condition (mean: 60, bootstrapped 95\% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 34.34, 95\% CI={[}0.26, 67.83{]}), with parents using more tokens in the Activity Video condition (mean: 61, bootstrapped 95\% confidence interval (conf.
 int.): {[}193,259{]}) than in the No Video condition (mean: 41, 95\% conf.
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.15,1.27{]}).
+Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.15, 1.27{]}).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 These models included random intercepts per video.
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.65,-0.02{]}).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.11,1.04{]}).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.65, -0.02{]}).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.11, 1.04{]}).
 
-To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
-Words that are strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that are most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.
+To better understand the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.
 
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.\footnote{Preregistration: \url{https://osf.io/2bpdf/}.}
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}
 
@@
 
-84 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+84 infants (F = 36, M = 46) aged 12-24 months
+(20 12-17.9 month-olds in the Activity Video condition;
+21 12-17.9 month-olds in the Science Video condition;
+22 18-24 month-olds in the Activity Video condition;
+21 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).
 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
-The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48,0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61,0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44,0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75,0.94{]} for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15,-0.04{]}).
+This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15, -0.04{]}).
 The preregistered regression predicting the number of tokens used by parents revealed no effects.
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf.
-int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 95\% CI = {[}0.39,1.64{]}) than after the Science Video (mean: 3.18, 95\% conf.
+int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 95\% CI = {[}0.39, 1.64{]}) than after the Science Video (mean: 3.18, 95\% conf.
 int.: {[}2.81, 3.54{]}).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 95\% CI = {[}0.08,0.93{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
+The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 95\% CI = {[}0.08, 0.93{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
 int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf.
 int.: {[}2.13, 2.61{]}).
-Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 95\% CI = {[}-2.64,-0.37{]}).
-However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 95\% CI = {[}-0.02,3.23{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 95\% CI = {[}-2.64, -0.37{]}).
+However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 95\% CI = {[}-0.02, 3.23{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 95\% CI = {[}0.06,0.84{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
-There was an interaction of age and condition (\(\beta=1.60\), 95\% CI = {[}0.15,3.18{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 95\% CI = {[}0.06, 0.84{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
+There was an interaction of age and condition (\(\beta=1.60\), 95\% CI = {[}0.15, 3.18{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 95\% CI = {[}-1.64,0.02{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 95\% CI = {[}-0.01,0{]}).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 95\% CI = {[}-1.64, 0.02{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 95\% CI = {[}-0.01, 0{]}).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
-The words that are strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that are most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
+The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
 
@@
 We were interested in how digital parenting advice alters parents' interactions with their children.
-We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions.
+We specifically set out to test whether activity suggestions led to higher-quality play, a presupposition of many early parenting interventions.
 Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
 In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
-In some cases--especially in older children--these bids were successful in increasing engagement.
+In some cases---especially in older children---these bids were successful in increasing engagement.
 We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
@@
 
-\leavevmode\hypertarget{ref-Hembacher2018}{}%
+\leavevmode\hypertarget{ref-Hembacher2020}{}%
 Hembacher, E., \& Frank, M.
 C.
-(2018).
+(2020).
 The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development.
-\emph{PsyArXiv}.
+\emph{Collabra: Psychology}, \emph{6}(1).
 \url{http://doi.org/10.31234/osf.io/hxk3d}

### 2020-03-27 paper/manuscript.Rmd
use verbal start cue for play duration, switched to 89% credible intervals, did Mike and Emily's edits

@@
   - name          : "Emily Hembacher"
+    affiliation   : "1"
+  - name          : "Veronica Cristiano"
     affiliation   : "2"
-  - name          : "Veronica Cristiano"
+  - name          : "Hanwen Vivian Zhang"
     affiliation   : "3"
-  - name          : "Hanwen Vivian Zhang"
-    affiliation   : "4"
   - name          : "Michael C. Frank"
@@
   - id            : "2"
-    institution   : "Nextdoor, Inc."
+    institution    : "Gallaudet University"
   - id            : "3"
-    institution    : "Gallaudet University"
-  - id            : "4"
     institution    : "Cornell University"
@@
 # rate calculations (tokens / min, words / min)
-e1_dur = read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"))
-e1_dur <- e1_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
-  select(SID, vid_dur)
-e1ld <- e1ld %>% left_join(e1_dur, by=c("sid"="SID"))
+e1_play_duration <- read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"), header=T)
+e1_play_duration$start_sec = with(e1_play_duration, ifelse(is.na(verbalcue_start_sec), 
+                                                           play_start_sec, verbalcue_start_sec))
+e1_play_duration <- e1_play_duration %>% 
+  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to mins
+  select(SID, play_duration)
+e1ld <- e1ld %>% left_join(e1_play_duration, by=c("sid"="SID"))
 
@@
 e1ld <- e1ld %>% 
-  mutate(types = (types / vid_dur), 
-         tokens = (tokens / vid_dur),
-         Conversational_Turns = (Conversational_Turns / vid_dur))
+  mutate(types = (types / play_duration), 
+         tokens = (tokens / play_duration),
+         Conversational_Turns = (Conversational_Turns / play_duration))
 
@@
 
-e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
-e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
-  select(sid, vid_dur)
-e2data <- e2data %>% left_join(e2_dur, by="sid")
+#e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
+#e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
+#  select(sid, vid_dur)
+#e2data <- e2data %>% left_join(e2_dur, by="sid")
+
+e2_play_duration <- read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"), header=T)
+e2_play_duration$start_sec = with(e2_play_duration, ifelse(is.na(verbalcue_start_sec), 
+                                                           play_start_sec, verbalcue_start_sec))
+e2_play_duration <- e2_play_duration %>% 
+  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to min
+  select(sid, play_duration)
+e2data <- e2data %>% left_join(e2_play_duration, by="sid")
 
@@
 e2data <- e2data %>% 
-  mutate(types = (types / vid_dur), 
-         tokens = (tokens / vid_dur),
-         Conversational_Turns = (Conversational_Turns / vid_dur))
+  mutate(types = (types / play_duration), 
+         tokens = (tokens / play_duration),
+         Conversational_Turns = (Conversational_Turns / play_duration))
 ```
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 89% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 89% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 89% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 89% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.
 
@@
 require("rstanarm")
-require(bayestestR)
-# get estimated coefficient and 95% CI from Bayesian regression
-get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
+require("bayestestR")
+# get estimated coefficient and 89% CI from Bayesian regression
+get_stan_glmer_reporting_values <- function(model, cond, digits=3) {
   ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
@@
 modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
-summary(modTTR) 
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14
+summary(modTTR) # n_eff ~2100 (is n_eff / n = Effective Sample Size (ESS)?)
+
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14  !!!
 p_direction(modTTR, effects="all") # orchestra 78.7%
+
+#ci_hdi <- ci(modTTR, method = "HDI") # [-0.25, -0.01]
+#ci_eti <- ci(modTTR, method = "ETI") # [-0.26, -0.01]
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
-For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior falls.
-There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`, `r e1TTR['95pUB']`]).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`, `r e1MTLD['95pUB']`]), with no predicted influence of age.
+For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range.
+There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 89% CI=[`r e1TTR['89pLB']`, `r e1TTR['89pUB']`]).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 89% CI=[`r e1MTLD['89pLB']`, `r e1MTLD['89pUB']`]), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+
+[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018].
+Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.
 
@@
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`, `r e1tokens['95pUB']`]), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
-int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
-int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 89% CI=[`r e1tokens['89pLB']`, `r e1tokens['89pUB']`]), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
+int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
+int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`, `r e1bids['95pUB']`]).
+Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 89% CI=[`r e1bids['89pLB']`, `r e1bids['89pUB']`]).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 summary(e1pja_modE) # condition*RR beta=1.8, RR close
-e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 95% CI = [-.65,-.02]  REPORT
+e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 89% CI = [-.65,-.02]  REPORT
 #e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed") # -.23 [-.47,.02] pd=.97 REPORT?
@@
 These models included random intercepts per video. 
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaRR['95pLB']`, `r e1pjaRR['95pUB']`]).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`, `r e1pjaE['95pUB']`]).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 89% CI=[`r e1pjaRR['89pLB']`, `r e1pjaRR['89pUB']`]).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 89% CI=[`r e1pjaE['89pLB']`, `r e1pjaE['89pUB']`]).
 
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.[^4]
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.[^5]
 
-[^4]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf).
+[^5]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf).
 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
-The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 89% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 89% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 89% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 89% CI = [0.75, 0.94] for total duration of coordinated JA episodes.
 
@@
 e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
-summary(e2TTR_m) # conditionexp beta=-.1 95% CI=[-.2,0.0]
+summary(e2TTR_m) # conditionexp beta=-.1 89% CI=[-.2,0.0]
 e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`, `r e2TTR['95pUB']`]).
+This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 89% CI=[`r e2TTR['89pLB']`, `r e2TTR['89pUB']`]).
 The preregistered regression predicting the number of tokens used by parents revealed no effects. 
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`, `r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 89% CI = [`r e2bids["89pLB"]`, `r e2bids["89pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`, `r e2tjaCond["95pUB"]`]), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
+The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 89% CI = [`r e2tjaCond["89pLB"]`, `r e2tjaCond["89pUB"]`]), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`, `r e2tjaAge["95pUB"]`]). 
-However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`, `r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, 89% CI = [`r e2tjaAge["89pLB"]`, `r e2tjaAge["89pUB"]`]). 
+However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 89% CI = [`r e2tjaAgeCond["89pLB"]`, `r e2tjaAgeCond["89pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 e2pja_m <- stan_lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(e2pja_m) # age beta=-2.7 95% CI=[-5.1,0.0]
+summary(e2pja_m) # age beta=-2.7 89% CI=[-5.1,0.0]
 e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")
@@
 e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(e2pjat_m) # age: est: -17.97 95% CI = [-33.37,-2.41] 
+summary(e2pjat_m) # age: est: -17.97 89% CI = [-33.37,-2.41] 
 e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`, `r e2cjaCond["95pUB"]`]), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`, `r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 89% CI = [`r e2cjaCond["89pLB"]`, `r e2cjaCond["89pUB"]`]), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 89% CI = [`r e2cjaAgeCond["89pLB"]`, `r e2cjaAgeCond["89pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`, `r e2pja["95pUB"]`]), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`, `r e2pjat["95pUB"]`]).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, 89% CI = [`r e2pja["89pLB"]`, `r e2pja["89pUB"]`]), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 89% CI = [`r e2pjat["89pLB"]`, `r e2pjat["89pUB"]`]).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 ```
+
+```{r echo = FALSE, results = 'asis'}
+render_appendix('appendix.Rmd')
+```

### 2020-03-27 paper/manuscript.tex
use verbal start cue for play duration, switched to 89% credible intervals, did Mike and Emily's edits

@@
 \vspace{0.5cm}
-\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} Gallaudet University\\\textsuperscript{4} Cornell University}
+\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
 \keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4629}
@@
 \title{Understanding the impacts of video-guided activities on parent-child interaction}
-\author{George Kachergis\textsuperscript{1}, Emily Hembacher\textsuperscript{2}, Veronica Cristiano\textsuperscript{3}, Hanwen Vivian Zhang\textsuperscript{4}, \& Michael C. Frank\textsuperscript{1}}
+\author{George Kachergis\textsuperscript{1}, Emily Hembacher\textsuperscript{1}, Veronica Cristiano\textsuperscript{2}, Hanwen Vivian Zhang\textsuperscript{3}, \& Michael C. Frank\textsuperscript{1}}
 \date{}
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
-For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior falls.
-There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 95\% CI={[}-0.29, 0.01{]}).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 95\% CI={[}-26.25, 12.20{]}), with no predicted influence of age.
+For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; McElreath, 2018).
+Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range.
+There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 95\% CI={[}-0.26, -0.01{]}).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 95\% CI={[}-22.46, 8.45{]}), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 34.34, 95\% CI={[}0.26, 67.83{]}), with parents using more tokens in the Activity Video condition (mean: 61, bootstrapped 95\% confidence interval (conf.
-int.): {[}193,259{]}) than in the No Video condition (mean: 41, 95\% conf.
-int.: {[}139,194{]}).
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 32.41, 95\% CI={[}-2.06, 65.94{]}), with parents using more tokens in the Activity Video condition (mean: 69, bootstrapped 95\% confidence interval (conf.
+int.): {[}193, 259{]}) than in the No Video condition (mean: 52, 95\% conf.
+int.: {[}139, 194{]}).
 
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.15, 1.27{]}).
+Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.27, 1.16{]}).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 These models included random intercepts per video.
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.65, -0.02{]}).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.11, 1.04{]}).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.60, -0.08{]}).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.22, 0.95{]}).
 
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
+Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).}
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15, -0.04{]}).
+This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.14, -0.05{]}).
 The preregistered regression predicting the number of tokens used by parents revealed no effects.
@@
 
+\leavevmode\hypertarget{ref-Kruschke2014}{}%
+Kruschke, J. (2014). \emph{Doing bayesian data analysis: A tutorial with r, jags, and stan}. Academic Press.
+
 \leavevmode\hypertarget{ref-Malvern2004}{}%
@@
 McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A validation study of sophisticated approaches to lexical diversity assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.
+
+\leavevmode\hypertarget{ref-McElreath2018}{}%
+McElreath, R. (2018). \emph{Statistical rethinking: A bayesian course with examples in r and stan}. Chapman; Hall/CRC.
 

### 2020-03-27 parenting_obs_e1/joint_attention/parenting_obs_JA.Rmd
use verbal start cue for play duration, switched to 89% credible intervals, did Mike and Emily's edits

@@
 play_duration <- read.csv("parenting_obs_play_duration_E1.csv", header=T)
+play_duration$start_sec = with(play_duration, ifelse(is.na(verbalcue_start_sec), # use verbal cue if it exists; otherwise play start
+                                                           play_start_sec, verbalcue_start_sec))
 play_duration <- play_duration %>% 
-  mutate(play_duration = play_stop_sec - play_start_sec)
+  mutate(play_duration = play_stop_sec - start_sec)
 sort(play_duration$play_duration) # shortest: 167 seconds

### 2020-03-27 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
use verbal start cue for play duration, switched to 89% credible intervals, did Mike and Emily's edits

@@
 play_duration <- read.csv("parenting_obs_play_duration_E2.csv", header=T)
+play_duration$start_sec = with(play_duration, ifelse(is.na(verbalcue_start_sec), # if no verbal cue use play start
+                                                           play_start_sec, verbalcue_start_sec))
 play_duration <- play_duration %>% 
-  mutate(play_duration = play_stop_sec - play_start_sec)
+  mutate(play_duration = play_stop_sec - start_sec)
 sort(play_duration$play_duration) # 1 pretty short session: 131 seconds

### 2020-03-28 paper/manuscript.Rmd
repo cleanup

@@
 And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
-Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004], making implementation at scale a daunting proposition.
+Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004; @Leung2018], making implementation at scale a daunting proposition.
 For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
@@
 Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2). 
-We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.
+We then gave the toys from the video to all dyads and videotaped their interactions, coding for caregivers' language quantity and quality as well as joint attention.
 
@@
 
+print_CI <- function(mod) {
+  string = paste0("89% CI=[",mod['89pLB'],", ",mod['89pUB'],"]", ", *pd*= ",mod['pd'])
+  return(string)
+}
+
 modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
@@
 p_direction(modTTR, effects="all") # orchestra 78.7%
+#print_CI(e1TTR)
 
@@
 summary(types_mod) # nothing 
-p_direction(types_mod, effects="all") # condition 83%, age 92.5%..
+p_direction(types_mod, effects="all") # condition 80%, age 78, cond*age 84%..
 
@@
 get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
-p_direction(modTTRE, effects="all") # EL 75, RR 86%, parent_ed 83.5
+p_direction(modTTRE, effects="all") # RR 91.00%  parent_ed 92.17%
 
@@
 summary(modMTLDE) #
-p_direction(modMTLDE, effects="all") # RR 81.5% genderM 88.9%
+p_direction(modMTLDE, effects="all") # AA 85.60% RR 85.02% age 55.80% genderM 85.12%
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
-For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range.
-There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 89% CI=[`r e1TTR['89pLB']`, `r e1TTR['89pUB']`]).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 89% CI=[`r e1MTLD['89pLB']`, `r e1MTLD['89pUB']`]), with no predicted influence of age.
+For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range.
+There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`).
+<!-- A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no predicted influence of age.
+-->
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 89% CI=[`r e1tokens['89pLB']`, `r e1tokens['89pUB']`]), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
 int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.

### 2020-03-28 paper/manuscript.tex
repo cleanup

@@
 And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions.
-Many effective parenting interventions require large resource investments and require many hours of in-person contact (Gertler et al., 2014; Schweinhart et al., 2004), making implementation at scale a daunting proposition.
+Many effective parenting interventions require large resource investments and require many hours of in-person contact (Gertler et al., 2014; Leung, Hernandez, \& Suskind, 2018; Schweinhart et al., 2004), making implementation at scale a daunting proposition.
 For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices.
@@
 Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2).
-We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.
+We then gave the toys from the video to all dyads and videotaped their interactions, coding for caregivers' language quantity and quality as well as joint attention.
 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 89\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 89\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 89\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 89\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
-For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; McElreath, 2018).
+For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski, Ben-Shachar, Chen, \& Lüdecke (2019)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; McElreath, 2018).
 Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range.
-There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 95\% CI={[}-0.26, -0.01{]}).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 95\% CI={[}-22.46, 8.45{]}), with no predicted influence of age.
+There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 89\% CI={[}-0.26, -0.01{]}) TEST 89\% CI={[}-0.263, -0.014{]}, \emph{pd}= 0.965.
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 89\% CI={[}-22.46, 8.45{]}), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 32.41, 95\% CI={[}-2.06, 65.94{]}), with parents using more tokens in the Activity Video condition (mean: 69, bootstrapped 95\% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 32.41, 89\% CI={[}-2.06, 65.94{]}), with parents using more tokens in the Activity Video condition (mean: 69, bootstrapped 95\% confidence interval (conf.
 int.): {[}193, 259{]}) than in the No Video condition (mean: 52, 95\% conf.
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.27, 1.16{]}).
+Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 89\% CI={[}0.27, 1.16{]}).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 These models included random intercepts per video.
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.60, -0.08{]}).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.22, 0.95{]}).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 89\% CI={[}-0.60, -0.08{]}).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 89\% CI={[}0.22, 0.96{]}).
 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
-The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 89\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 89\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 89\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 89\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.14, -0.05{]}).
+This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI={[}-0.14, -0.05{]}).
 The preregistered regression predicting the number of tokens used by parents revealed no effects.
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf.
-int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 95\% CI = {[}0.39, 1.64{]}) than after the Science Video (mean: 3.18, 95\% conf.
+int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 89\% CI = {[}0.51, 1.53{]}) than after the Science Video (mean: 3.18, 95\% conf.
 int.: {[}2.81, 3.54{]}).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 95\% CI = {[}0.08, 0.93{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
+The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 89\% CI = {[}0.16, 0.84{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
 int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf.
 int.: {[}2.13, 2.61{]}).
-Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 95\% CI = {[}-2.64, -0.37{]}).
-However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 95\% CI = {[}-0.02, 3.23{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 89\% CI = {[}-2.46, -0.63{]}).
+However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 89\% CI = {[}0.33, 2.99{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 95\% CI = {[}0.06, 0.84{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
-There was an interaction of age and condition (\(\beta=1.60\), 95\% CI = {[}0.15, 3.18{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.14, 0.77{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
+There was an interaction of age and condition (\(\beta=1.60\), 89\% CI = {[}0.40, 2.87{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 95\% CI = {[}-1.64, 0.02{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 95\% CI = {[}-0.01, 0{]}).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 89\% CI = {[}-1.51, -0.17{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 89\% CI = {[}-0.01, 0.00{]}).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 
+\leavevmode\hypertarget{ref-Leung2018}{}%
+Leung, C.
+Y., Hernandez, M.
+W., \& Suskind, D.
+L.
+(2018).
+Enriching home language environment among families from low-ses backgrounds: A randomized controlled trial of a home visiting curriculum.
+\emph{Early Childhood Research Quarterly}.
+\url{http://doi.org/https://doi.org/10.1016/j.ecresq.2018.12.005}
+
+\leavevmode\hypertarget{ref-Makowski2019}{}%
+Makowski, D., Ben-Shachar, M.
+S., Chen, S.
+H.
+A., \& Lüdecke, D.
+(2019).
+Indices of effect existence and significance in the bayesian framework.
+\emph{Frontiers in Psychology}, \emph{10}, 2767.
+\url{http://doi.org/10.3389/fpsyg.2019.02767}
+
 \leavevmode\hypertarget{ref-Malvern2004}{}%
@@
 Kruschke, J. (2014). \emph{Doing bayesian data analysis: A tutorial with r, jags, and stan}. Academic Press.
+
+\leavevmode\hypertarget{ref-Leung2018}{}%
+Leung, C.
+Y., Hernandez, M.
+W., \& Suskind, D.
+L.
+(2018).
+Enriching home language environment among families from low-ses backgrounds: A randomized controlled trial of a home visiting curriculum.
+\emph{Early Childhood Research Quarterly}.
+\url{http://doi.org/https://doi.org/10.1016/j.ecresq.2018.12.005}
+
+\leavevmode\hypertarget{ref-Makowski2019}{}%
+Makowski, D., Ben-Shachar, M.
+S., Chen, S.
+H.
+A., \& Lüdecke, D.
+(2019).
+Indices of effect existence and significance in the bayesian framework.
+\emph{Frontiers in Psychology}, \emph{10}, 2767.
+\url{http://doi.org/10.3389/fpsyg.2019.02767}
 

### 2020-03-28 language_analyses/get_all_parent_speech.py

@@ -1,0 +1,108 @@
+import os
+import string
+import pandas as pd
+from lexical_diversity import mtld, hdd
+import nltk
+from nltk.stem import WordNetLemmatizer
+from nltk import tokenize
+from statistics import mean
+lemmatizer = WordNetLemmatizer()
+
+# a function to clean texts in brackets
+def clean(string):
+    ret = ''
+    skip1c = 0
+    for i in string:
+        if i == '[':
+            skip1c += 1
+        elif i == ']' and skip1c > 0:
+            skip1c -= 1
+        elif skip1c == 0:
+            ret += i
+    return ret
+
+
+# formatted mother utterances (each utterance should be in the same one paragraph) by hand
+# "Female speaker" "*Other Child" "*OTH" "*BOTH" "*ADF,ADM" are what used to refer to other speakers than parent or child
+# should replace all "CHI 2:" with "CHI:"
+# get conditions.csv from google sheet instead of by hand
+
+# creat a dataframe for calculation results
+col_names = ['sid', 'MTLD', 'HDD', 'types', 'tokens', 'TTR', 'len_sentence']
+results = pd.DataFrame(columns = col_names)
+
+files = os.listdir("exp1_trans_out/")
+try:
+    files.remove('.DS_Store')
+except:
+    pass
+all_dat = {}
+# print (files)
+for fname in files:
+    folder = "exp1_trans_out/"
+    name =  fname
+    path = "".join((folder,name))
+    fr = open(path, 'r')
+    print (fr)
+    lines = []
+    for line in fr:
+        spm = line.split('*MOT:')
+        spm_1 = line.split('MOT:')
+        spd = line.split('*FAT:')
+        spd_1 = line.split('FAT:')
+        if len(spm)>1:
+            lines.append(spm[1]) # found mother speech, grab it
+        elif len(spd)>1:
+            lines.append(spd[1]) # found father speech, grab it
+        elif len(spd_1)>1:
+                lines.append(spd_1[1])
+        elif len(spm_1)>1:
+            lines.append(spm_1[1])
+    lines_str = " ".join(lines)
+    lines_str = lines_str.replace ('\n', '')
+    lines_str = lines_str.replace ('\t', '')
+    text_ready = clean(lines_str)
+#   print (repr(text_ready))
+    all_dat[fname] = text_ready
+
+# call MTLD and HDD functions and calculate
+    id = fname[6:14]
+    print (len(str.split(text_ready)))
[…]

### 2020-03-28 parenting_obs_e1/get_all_parent_speech.py

@@ -1,110 +1,0 @@
-import os
-import string
-import pandas as pd
-from lexical_diversity import mtld, hdd
-import nltk
-from nltk.stem import WordNetLemmatizer
-from nltk import tokenize
-from statistics import mean
-lemmatizer = WordNetLemmatizer()
-
-# a function to clean texts in brackets
-def clean(string):
-    ret = ''
-    skip1c = 0
-    for i in string:
-        if i == '[':
-            skip1c += 1
-        elif i == ']' and skip1c > 0:
-            skip1c -= 1
-        elif skip1c == 0:
-            ret += i
-    return ret
-
-
-# formatted mother utterances (each utterance should be in the same one paragraph) by hand
-# "Female speaker" "*Other Child" "*OTH" "*BOTH" "*ADF,ADM" are what used to refer to other speakers than parent or child
-# should replace all "CHI 2:" with "CHI:"
-# get conditions.csv from google sheet instead of by hand
-
-# creat a dataframe for calculation results
-col_names = ['sid', 'MTLD', 'HDD', 'types', 'tokens', 'TTR', 'len_sentence']
-results = pd.DataFrame(columns = col_names)
-
-files = os.listdir("trans_out/")
-try:
-    files.remove('.DS_Store')
-except:
-    pass
-all_dat = {}
-# print (files)
-for fname in files:
-    folder = "trans_out/"
-    name =  fname
-    path = "".join((folder,name))
-    fr = open(path, 'r')
-    print (fr)
-    lines = []
-    for line in fr:
-        spm = line.split('*MOT:')
-        spm_1 = line.split('MOT:')
-        spd = line.split('*FAT:')
-        spd_1 = line.split('FAT:')
-        if len(spm)>1:
-            lines.append(spm[1]) # found mother speech, grab it
-        elif len(spd)>1:
-            lines.append(spd[1]) # found father speech, grab it
-        elif len(spd_1)>1:
-                lines.append(spd_1[1])
-        elif len(spm_1)>1:
-            lines.append(spm_1[1])
-    lines_str = " ".join(lines)
-    lines_str = lines_str.replace ('\n', '')
-    lines_str = lines_str.replace ('\t', '')
-    text_ready = clean(lines_str)
-#   print (repr(text_ready))
-    all_dat[fname] = text_ready
-
-# call MTLD and HDD functions and calculate
-    id = fname
-    print (len(str.split(text_ready)))
-    if (len(str.split(text_ready)))>50:
[…]

### 2020-03-28 parenting_obs_e2/get_all_parent_speech.py

@@ -1,110 +1,0 @@
-import os
-import string
-import pandas as pd
-from lexical_diversity import mtld, hdd
-import nltk
-from nltk.stem import WordNetLemmatizer
-from nltk import tokenize
-from statistics import mean
-lemmatizer = WordNetLemmatizer()
-
-# a function to clean texts in brackets
-def clean(string):
-    ret = ''
-    skip1c = 0
-    for i in string:
-        if i == '[':
-            skip1c += 1
-        elif i == ']' and skip1c > 0:
-            skip1c -= 1
-        elif skip1c == 0:
-            ret += i
-    return ret
-
-
-# formatted mother utterances (each utterance should be in the same one paragraph) by hand
-# "Female speaker" "*Other Child" "*OTH" "*BOTH" "*ADF,ADM" are what used to refer to other speakers than parent or child
-# should replace all "CHI 2:" with "CHI:"
-# get conditions.csv from google sheet instead of by hand
-
-# creat a dataframe for calculation results
-col_names = ['sid', 'MTLD', 'HDD', 'types', 'tokens', 'TTR', 'len_sentence']
-results = pd.DataFrame(columns = col_names)
-
-files = os.listdir("trans_out_txt/")
-try:
-    files.remove('.DS_Store')
-except:
-    pass
-all_dat = {}
-# print (files)
-for fname in files:
-    folder = "trans_out_txt/"
-    name =  fname
-    path = "".join((folder,name))
-    fr = open(path, 'r')
-    print (fr)
-    lines = []
-    for line in fr:
-        spm = line.split('*MOT:')
-        spm_1 = line.split('MOT:')
-        spd = line.split('*FAT:')
-        spd_1 = line.split('FAT:')
-        if len(spm)>1:
-            lines.append(spm[1]) # found mother speech, grab it
-        elif len(spd)>1:
-            lines.append(spd[1]) # found father speech, grab it
-        elif len(spd_1)>1:
-                lines.append(spd_1[1])
-        elif len(spm_1)>1:
-            lines.append(spm_1[1])
-    lines_str = " ".join(lines)
-    lines_str = lines_str.replace ('\n', '')
-    lines_str = lines_str.replace ('\t', '')
-    text_ready = clean(lines_str)
-#   print (repr(text_ready))
-    all_dat[fname] = text_ready
-
-# call MTLD and HDD functions and calculate
-    id = fname[6:14]
-    print (len(str.split(text_ready)))
[…]

### 2020-03-28 parenting_obs_e2/lexical_diversity.py

@@ -1,102 +1,0 @@
-#Copyright 2017 John Frens
-#
-#Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:
-#
-#The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.
-#
-#THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-
-import string
-
-# Global trandform for removing punctuation from words
-remove_punctuation = str.maketrans('', '', string.punctuation)
-
-# MTLD internal implementation
-def mtld_calc(word_array, ttr_threshold):
-    current_ttr = 1.0
-    token_count = 0
-    type_count = 0
-    types = set()
-    factors = 0.0
-    
-    for token in word_array:
-        token = token.translate(remove_punctuation).lower() # trim punctuation, make lowercase
-        token_count += 1
-        if token not in types:
-            type_count +=1
-            types.add(token)
-        current_ttr = type_count / token_count
-        if current_ttr <= ttr_threshold:
-            factors += 1
-            token_count = 0
-            type_count = 0
-            types = set()
-            current_ttr = 1.0
-    
-    excess = 1.0 - current_ttr
-    excess_val = 1.0 - ttr_threshold
-    factors += excess / excess_val
-    if factors != 0:
-        return len(word_array) / factors
-    return -1
-
-# MTLD implementation
-def mtld(word_array, ttr_threshold=0.72):
-    if isinstance(word_array, str):
-        raise ValueError("Input should be a list of strings, rather than a string. Try using string.split()")
-    if len(word_array) < 50:
[…]

### 2020-03-30 paper/appendix-Bayesian-analyses.Rmd
cleaning up and adding appendix

---
title: 'Appendix: Bayesian Analysis Overview'
output: pdf_document
---

```{r setup, include = FALSE}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library("papaja")
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidyboot)
library(knitr)
library(brms)
library(rstanarm)
library(bayestestR)
library(bayesplot)

source("multiplot.R")
select <- dplyr::select # masked by MASS
theme_set(theme_few())

# labels=addline_format(c("Activity Video", "Science Video"))
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

get_stan_glmer_reporting_values <- function(model, cond, digits=3) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
  pd = p_direction(model)
  pd = pd[which(pd$Parameter==cond),]$pd
  ci = round(c(ci95,ci89,pd), digits)
  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}
```

```{r analysis-preferences, echo=F}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"

d = read.csv("../language_analyses/exp1_lexical_diversity.csv")

e1_parent_ed = table(d$parent_ed)

e1ld <- d %>%
  mutate(condition = factor(condition), 
         gender = as.factor(gender),
         video = as.factor(video))

e1_gender = table(e1ld$gender)

# rate calculations (tokens / min, words / min)
e1_play_duration <- read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"), header=T)
e1_play_duration$start_sec = with(e1_play_duration, ifelse(is.na(verbalcue_start_sec), 
                                                           play_start_sec, verbalcue_start_sec))
e1_play_duration <- e1_play_duration %>% 
  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to mins
  select(SID, play_duration)
e1ld <- e1ld %>% left_join(e1_play_duration, by=c("sid"="SID"))

# convert types and tokens to rate: types/min and tokens/min
e1ld <- e1ld %>% 
  mutate(types = (types / play_duration), 
         tokens = (tokens / play_duration),
         TTR = (TTR / play_duration),
         MTLD = (MTLD / play_duration))

e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
```

Here we look at one of the regressions from Experiment 1 in detail in order to explain and illustrate the rationale of the Bayesian analysis, in particular the *probability of direction* (*pd*) and the 89% CI (credible interval). For this example we take the exploratory regression from Experiment 1 predicting parents' rate of word types with fixed effects of condition (*No Video* or *Activity Video*), each subscale of the EPAQ (EL: Early Learning, AA: Affection and Attachment, and RR: Rules & Respect), parent education (parent_ed), the child's age (centered) and gender. The model also included interactions for condition and each subscale of the EPAQ, as well as a random intecept for each video.
The model syntax was: types \~ condition\*EL + condition\*AA + condition\*RR  + age + gender + parent_ed + (1|video).
Table 1 reports the mean of each coefficient's posterior distribution, along with the lower and upper bounds for the 89% credible interval, and the probability of direction (*pd*).

```{r, run-regression, echo=F, include=F}
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) 
diagnostic_posterior(types_modE)

e1ed = get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
pd = p_direction(types_modE, effects="fixed") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
```

```{r, p-direction, echo=F, fig.cap="Mean, *pd*, and 89% CIs of the coefficient posterior distributions."}

cols = c("Mean","89% CI Lower","89% CI Upper")
pd[,cols] = NA
for(i in 2:nrow(pd)) {
  tmp = get_stan_glmer_reporting_values(types_modE, pd[i,]$Parameter) 
  pd[i,cols] = c(tmp[pd[i,]$Parameter], tmp["89pLB"], tmp["89pUB"])
}
kable(pd[2:nrow(pd),c("Parameter","pd", cols)], digits=2, row.names=F)
```

What do these values mean? 
Let's take a closer look at the posterior distribution of the parent education (parent_ed) coefficient. 
Shown below in Figure 1, the 87% of this distribution that is greater than 0 is shaded orange, which corresponds to the probability of direction *pd* = 0.87, which has the straightforward interpretation of being the probability that an effect has the same sign as the median value of the posterior. Thus, *pd* has a range of 0.5 (if the distribution is equally-distributed around 0: a likely true null effect) to 1.0 (if the posterior is entirely positive or negative).
Since *pd* < 0.95 in this case (corresponding to a $p$<.05 threshold in the null hypothesis significance-testing framework), we do not consider parent education to have a notable effect on the rate of types used during play, but the posterior distribution is interpretable.
Also shown are the mean estimated coefficient value (red line) and 89% credible intervals (blue lines), within which 89% of the posterior distribution falls.

```{r, parent-ed-effect, echo=F, fig.cap="Figure 1. Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
dat = types_modE %>% posterior_samples("parent_ed") %>%
  estimate_density(extend=TRUE)

dat %>% 
  ggplot(aes(x=x, y=y)) +
  geom_area(fill="grey") +
  geom_ribbon(data=subset(dat, x>0),aes(ymax=y),ymin=0,
              fill="orange",colour=NA,alpha=0.6) + 
  theme_classic() + ylab("Posterior Density") + xlab("Candidate Values of Parent Education Coefficient") +
  geom_vline(xintercept=e1ed["89pLB"], color="royalblue", size=1) +
  geom_vline(xintercept=e1ed["89pUB"], color="royalblue", size=1) +
  geom_vline(xintercept=0, size=1, lty="dashed") + 
  geom_vline(xintercept=e1ed["parent_ed"], size=1, color="red")
```

Figure 2 shows the posteriors for all of the coefficients in this regression. 
Only the interaction between condition and the Affection and Attachment subscale of the EPAQ was notable (by *pd* in Table 1), but as indicated by their *pd* values, much of the mass some other parameters' posteriors are skewed negative (e.g., conditionexp: the Activity Video condition; EL: the Early Learning subscale of the EPAQ), while others are more evenly-distributed (e.g., RR, $pd$ = 0.51).

```{r, plot-posteriors, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}
posterior <- as.matrix(types_modE)

#plot_title <- ggtitle("Posterior distributions", "with means and 89% credible intervals")
mcmc_areas(posterior,
           pars = c("conditionexp", 
                    "EL", "AA", "RR", 
                    "age", "genderM", "parent_ed", 
                    "conditionexp:EL",
                    "conditionexp:AA",
                    "conditionexp:RR"),
           prob = 0.89,
           prob_outer = 0.95,
           point_est = "mean") + #+ plot_title
  theme(plot.margin=unit(c(-30,2,2,2),"mm"))
```

### 2020-03-30 paper/manuscript.Rmd
cleaning up and adding appendix

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4629"
+wordcount         : "4938"
 
@@
 e1path = "../parenting_obs_e1/"
-#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
 
-d = read.csv("../exp1_lexical_diversityAdd.csv") # with Conversational_Turns, but only has 53 subjects !!
+d = read.csv("../language_analyses/exp1_lexical_diversity.csv")
 
@@
          tokens = (tokens / play_duration),
-         Conversational_Turns = (Conversational_Turns / play_duration))
+         TTR = (TTR / play_duration),
+         MTLD = (MTLD / play_duration))
 
@@
 e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
-#d = read.csv("exp2_lexical_diversity_data.csv")
-d = read.csv("../exp2_lexical_diversityAdd.csv")
+d = read.csv("../language_analyses/exp2_lexical_diversity.csv")
 d <- d %>% left_join(e2Age, by="sid")
 
-e2data <- d %>%
+e2ld <- d %>%
   mutate(condition = as.factor(condition), 
@@
 
-e2data$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
+e2ld$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
 
@@
 #  select(sid, vid_dur)
-#e2data <- e2data %>% left_join(e2_dur, by="sid")
+#e2ld <- e2ld %>% left_join(e2_dur, by="sid")
 
@@
   select(sid, play_duration)
-e2data <- e2data %>% left_join(e2_play_duration, by="sid")
+e2ld <- e2ld %>% left_join(e2_play_duration, by="sid")
 
 # convert types and tokens to rate: types/min and tokens/min
-e2data <- e2data %>% 
+e2ld <- e2ld %>% 
   mutate(types = (types / play_duration), 
          tokens = (tokens / play_duration),
-         Conversational_Turns = (Conversational_Turns / play_duration))
+         TTR = (TTR / play_duration),
+         MTLD = (MTLD / play_duration))
 ```
@@
 
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015].
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015; see @Schwab2016 for a review].
 Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment.
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 89% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 89% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 89% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 89% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.
 
@@
 
-Parents' child-directed speech during the play sessions was transcribed; child utterances were not considered.
+Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e1ld$play_duration), 2)` min) was transcribed; child utterances were not considered.
 Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
@@
 
-For each transcript of child-directed speech, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
+For each transcript of child-directed speech, the caregivers' unique word *types* and *tokens* (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
 Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
@@
 summary(modTTR) # n_eff ~2100 (is n_eff / n = Effective Sample Size (ESS)?)
-
+diagnostic_posterior(modTTR) # 2500-4100
 e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14  !!!
@@
 # predict word types
-types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
+types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld,
+                        adapt_delta = .97)
 summary(types_mod) # nothing 
@@
 summary(types_modE) 
-p_direction(types_modE, effects="all") # EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
+p_direction(types_modE, effects="all") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
 get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
-get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA')
+e1types_condAA = get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA') # ADD THIS TO TEXT
 
-# predict # of conversational turns - COULD REPORT THIS
-modCT <- stan_glmer(Conversational_Turns ~ condition * age + (1|video), data=e1ld)
-summary(modCT) 
-get_stan_glmer_reporting_values(modCT, "conditionexp") # pd = .96 mean=2.52 [-.20,5.28]
-p_direction(modCT, effects="all")
-# E1 CT: exp early significant (+ effect)
-# E2 CT: age nearly significant (+ effect)
 ```
@@
 There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`).
-<!-- A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no predicted influence of age.
--->
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 [^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018].
-Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.
+Our ESS ranges from 2,000-5,000, and thus we go with the tighter, more stable interval.
 
@@
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using more tokens in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the rate of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using tokens at a higher rate in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)` tokens/min, bootstrapped 95% confidence interval (conf.
 int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
@@
             "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
+names(e1) = c("Condition","TTR/min (M)", "(sd)", "MTLD/min (M)", "(sd)", "Types/min (M)", "(sd)", "Tokens/min (M)", "(sd)")
 kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
@@
 
-ttr2 <- e2data %>% group_by(Condition) %>%
+ttr2 <- e2ld %>% group_by(Condition) %>%
   tidyboot_mean(TTR)
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
@@
 
-mtld2 <- e2data %>% group_by(Condition) %>%
+mtld2 <- e2ld %>% group_by(Condition) %>%
   tidyboot_mean(MTLD)
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("MTLD") +
@@
 
-e2tok <- e2data %>% group_by(Condition) %>%
+e2tok <- e2ld %>% group_by(Condition) %>%
   tidyboot_mean(tokens)
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Mean Word Tokens per Minute") +
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 89% CI=[`r e1bids['89pLB']`, `r e1bids['89pUB']`]).
+Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, `r print_CI(e1bids)`).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 These models included random intercepts per video. 
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, 89% CI=[`r e1pjaRR['89pLB']`, `r e1pjaRR['89pUB']`]).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 89% CI=[`r e1pjaE['89pLB']`, `r e1pjaE['89pUB']`]).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaRR)`).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).
 
@@
 ### Participants. 
-`r nrow(e2data)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
+`r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
 (`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
-The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 89% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 89% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 89% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 89% CI = [0.75, 0.94] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for total duration of coordinated JA episodes.
 
@@
 
-Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report preregistered regressions[^5] predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
+Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e2ld$play_duration), 2)` min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
+We first report preregistered regressions[^6] predicting TTR and number of tokens per minute of play, as well as an exploratory regression predicting MTLD per minute.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
 
-[^5]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
+[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
 Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).
@@
 # Predicting lexical diversity based on experimental condition. 
-e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
+e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2ld) 
 summary(e2TTR_m) # conditionexp beta=-.1 89% CI=[-.2,0.0]
@@
 # predict word tokens
-e2tokens_m <- stan_lmer(log(tokens) ~ age * condition + (1 | video), data=e2data)
+e2tokens_m <- stan_lmer(log(tokens) ~ age * condition + (1 | video), data=e2ld)
 summary(e2tokens_m) # NA 
@@
 
-e2MTLD_m <- stan_lmer(MTLD ~ age * condition + (1 | video), data=e2data)
+e2MTLD_m <- stan_lmer(MTLD ~ age * condition + (1 | video), data=e2ld)
 summary(e2MTLD_m) # NA
@@
 
-e2_lexdiv <- e2data %>% group_by(condition) %>%
+e2_lexdiv <- e2ld %>% group_by(condition) %>%
   summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 89% CI=[`r e2TTR['89pLB']`, `r e2TTR['89pUB']`]).
+This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , `r print_CI(e2TTR)`).
 The preregistered regression predicting the number of tokens used by parents revealed no effects. 
@@
 ```{r e2tab, echo=F}
-e2 <- e2data %>% group_by(Condition) %>%
+e2 <- e2ld %>% group_by(Condition) %>%
   summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
@@
 # NOT INCLUDED
-e2typ <- e2data %>% group_by(Condition) %>%
+e2typ <- e2ld %>% group_by(Condition) %>%
   tidyboot_mean(types)
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2ld, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Word Types per Minute") +
@@
 ```{r, e2-effect-size, echo=F, include=F}
-ttr_means <- e2data %>% group_by(Condition) %>%
+ttr_means <- e2ld %>% group_by(Condition) %>%
   summarise(mean = mean(TTR), sd = sd(TTR))
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 89% CI = [`r e2bids["89pLB"]`, `r e2bids["89pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, `r print_CI(e2bids)`)) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 89% CI = [`r e2tjaCond["89pLB"]`, `r e2tjaCond["89pUB"]`]), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
+The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, 89% CI = [`r e2tjaAge["89pLB"]`, `r e2tjaAge["89pUB"]`]). 
-However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 89% CI = [`r e2tjaAgeCond["89pLB"]`, `r e2tjaAgeCond["89pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, `r print_CI(e2tjaAge)`). 
+However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2tjaAgeCond)`): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 89% CI = [`r e2cjaCond["89pLB"]`, `r e2cjaCond["89pUB"]`]), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 89% CI = [`r e2cjaAgeCond["89pLB"]`, `r e2cjaAgeCond["89pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, `r print_CI(e2cjaCond)`), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2cjaAgeCond)`), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, 89% CI = [`r e2pja["89pLB"]`, `r e2pja["89pUB"]`]), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 89% CI = [`r e2pjat["89pLB"]`, `r e2pjat["89pUB"]`]).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, `r print_CI(e2pja)`), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, `r print_CI(e2pjat)`).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

### 2020-03-30 paper/manuscript.tex
cleaning up and adding appendix

@@
 
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008).
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008; see Schwab \& Lew-Williams, 2016 for a review).
 Thus, because of the potential for large downstream effects (Heckman, 2006), there is tremendous interest in interventions that change children's language environment.
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 89\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 89\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 89\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 89\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.
 
@@
 
-Parents' child-directed speech during the play sessions was transcribed; child utterances were not considered.
+Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
 Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
@@
 
-For each transcript of child-directed speech, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
+For each transcript of child-directed speech, the caregivers' unique word \emph{types} and \emph{tokens} (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
 Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
@@
 Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range.
-There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 89\% CI={[}-0.26, -0.01{]}) TEST 89\% CI={[}-0.263, -0.014{]}, \emph{pd}= 0.965.
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 89\% CI={[}-22.46, 8.45{]}), with no predicted influence of age.
+There was lower TTR in the Activity Video condition (mean: 0.10) than in the No Video condition (mean: 0.14, \(\beta=\)-0.04, 89\% CI={[}-0.052, -0.027{]}, \emph{pd}= 1).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 5.46) than in the No Video condition (mean: 8.49, \(\beta=\)-3.04, 89\% CI={[}-4.505, -1.448{]}, \emph{pd}= 0.998{]}), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 32.41, 89\% CI={[}-2.06, 65.94{]}), with parents using more tokens in the Activity Video condition (mean: 69, bootstrapped 95\% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the rate of word tokens (\(\beta=\) 16.50, 89\% CI={[}5.778, 27.201{]}, \emph{pd}= 0.994), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf.
 int.): {[}193, 259{]}) than in the No Video condition (mean: 52, 95\% conf.
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 89\% CI={[}0.27, 1.16{]}).
+Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 89\% CI={[}0.27, 1.16{]}, \emph{pd}= 0.99).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
@@
 These models included random intercepts per video.
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 89\% CI={[}-0.60, -0.08{]}).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 89\% CI={[}0.22, 0.96{]}).
+Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 89\% CI={[}-0.599, -0.078{]}, \emph{pd}= 0.98).
+However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 89\% CI={[}0.221, 0.955{]}, \emph{pd}= 0.992).
 
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
-Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).}
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}
 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
-The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 89\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 89\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 89\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 89\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.
 
@@
 
-Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
+Parents' child-directed speech during the play sessions (mean duration: 3.08 min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
 We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
-Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
+Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and number of tokens per minute of play, as well as an exploratory regression predicting MTLD per minute.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI={[}-0.14, -0.05{]}).
+This revealed lower TTR after the Activity Video (mean: 0.12) than after the Science Video (mean: 0.15, \(\beta=-0.03\), , 89\% CI={[}-0.046, -0.014{]}, \emph{pd}= 0.997).
 The preregistered regression predicting the number of tokens used by parents revealed no effects.
@@
 \hline
-Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 25.14 & 9.2 & 55.30 & 23.69\\
+Science Video & 0.15 & 0.03 & 7.28 & 3.41 & 28.05 & 8.54 & 61.85 & 23.58\\
 \hline
-Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 20.31 & 8.7 & 59.42 & 30.51\\
+Activity Video & 0.12 & 0.04 & 6.74 & 2.80 & 26.57 & 8.39 & 77.22 & 32.09\\
 \hline
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf.
-int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 89\% CI = {[}0.51, 1.53{]}) than after the Science Video (mean: 3.18, 95\% conf.
+int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 89\% CI={[}0.51, 1.53{]}, \emph{pd}= 1)) than after the Science Video (mean: 3.18, 95\% conf.
 int.: {[}2.81, 3.54{]}).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 89\% CI = {[}0.16, 0.84{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
+The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
 int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf.
 int.: {[}2.13, 2.61{]}).
-Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 89\% CI = {[}-2.46, -0.63{]}).
-However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 89\% CI = {[}0.33, 2.99{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 89\% CI={[}-2.46, -0.63{]}, \emph{pd}= 0.99).
+However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 89\% CI={[}0.33, 2.99{]}, \emph{pd}= 0.97): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.14, 0.77{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
-There was an interaction of age and condition (\(\beta=1.60\), 89\% CI = {[}0.40, 2.87{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI={[}0.143, 0.769{]}, \emph{pd}= 0.989), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
+There was an interaction of age and condition (\(\beta=1.60\), 89\% CI={[}0.405, 2.874{]}, \emph{pd}= 0.984), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 89\% CI = {[}-1.51, -0.17{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 89\% CI = {[}-0.01, 0.00{]}).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 89\% CI={[}-1.514, -0.166{]}, \emph{pd}= 0.972), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 89\% CI={[}-0.01, -0.002{]}, \emph{pd}= 0.99).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 
-\leavevmode\hypertarget{ref-spacy2}{}%
-Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language understanding with bloom embeddings, convolutional neural networks and incremental parsing. \emph{To Appear}.
-
 \leavevmode\hypertarget{ref-Kruschke2014}{}%
@@
 McElreath, R. (2018). \emph{Statistical rethinking: A bayesian course with examples in r and stan}. Chapman; Hall/CRC.
+
+\leavevmode\hypertarget{ref-Schwab2016}{}%
+Schwab, J. F., \& Lew-Williams, C. (2016). Language learning, socioeconomic status, and child-directed speech. \emph{WIREs Cognitive Science}, \emph{7}, 264--275. \url{http://doi.org/10.1002/wcs.1393}
 

### 2020-04-01 paper/manuscript.Rmd
final stats check

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4938"
+wordcount         : "5052"
 
@@
 library(knitr)
+library(rstanarm)
+library(bayestestR)
 source("multiplot.R")
@@
          tokens = (tokens / play_duration),
-         TTR = (TTR / play_duration),
-         MTLD = (MTLD / play_duration))
+         TTRnorm = (TTR / play_duration), # # not really interpretable if we normalize LD measures
+         MTLDnorm = (MTLD / play_duration)
+         )
 
@@
          gender = as.factor(gender),
-         Video = as.factor(Video),
-         pja_length = pja_length/1000,
-         cja_length = cja_length/1000,
-         total_lja = total_lja/1000) # convert duration ms -> seconds
+         Video = as.factor(Video)
+         #pja_length = pja_length/1000,
+         #cja_length = cja_length/1000,
+         #total_lja = total_lja/1000
+         ) # convert duration ms -> seconds
 ```
@@
          tokens = (tokens / play_duration),
-         TTR = (TTR / play_duration),
-         MTLD = (MTLD / play_duration))
+         TTRnorm = (TTR / play_duration), # not really interpretable if we normalize LD measures
+         MTLDnorm = (MTLD / play_duration)
+         )
 ```
@@
 e2ja <- d %>% mutate(bids = bids,
-                     age = as.numeric(langcog::scale(age, scale=FALSE)),
-                     pja_length = pja_length/1000,
-                     cja_length = cja_length/1000,
-                     total_lja = total_lja/1000) # convert duration ms -> seconds
+                     age = as.numeric(langcog::scale(age, scale=FALSE))
+                     #pja_length = pja_length/1000,
+                     #cja_length = cja_length/1000,
+                     #total_lja = total_lja/1000
+                     ) # convert duration ms -> seconds
 
@@
 ```{r, e1-lexdiv-regressions, echo=F, include=F}
-require("rstanarm")
-require("bayestestR")
 # get estimated coefficient and 89% CI from Bayesian regression
-get_stan_glmer_reporting_values <- function(model, cond, digits=3) {
+get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
   ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
@@
 print_CI <- function(mod) {
-  string = paste0("89% CI=[",mod['89pLB'],", ",mod['89pUB'],"]", ", *pd*= ",mod['pd'])
+  string = paste0("89% CI = [",mod['89pLB'],", ",mod['89pUB'],"]", ", *pd* = ",mod['pd'])
   return(string)
@@
 
-modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
-summary(modTTR) # n_eff ~2100 (is n_eff / n = Effective Sample Size (ESS)?)
-diagnostic_posterior(modTTR) # 2500-4100
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.14  !!!
-p_direction(modTTR, effects="all") # orchestra 78.7%
-#print_CI(e1TTR)
-
-#ci_hdi <- ci(modTTR, method = "HDI") # [-0.25, -0.01]
-#ci_eti <- ci(modTTR, method = "ETI") # [-0.26, -0.01]
+modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld, adapt_delta = .97)
+summary(modTTR) # ESS from ~1800 - 3600
+p_direction(modTTR, effects="all") # condition
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
 
 modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
-summary(modMTLD) 
+summary(modMTLD) # ESS ~ [2200, 4100]
+p_direction(modMTLD, effects="all") # condition
 e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -8.48
-p_direction(modMTLD, effects="all")
 
@@
 summary(tokens_mod)
+p_direction(tokens_mod, effects="all") # condition
 e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 19.45
-p_direction(tokens_mod, effects="all") # orchestra 89.7%
 
@@
                         adapt_delta = .97)
-summary(types_mod) # nothing 
-p_direction(types_mod, effects="all") # condition 80%, age 78, cond*age 84%..
+summary(types_mod) 
+p_direction(types_mod, effects="all") # cage 78, cond*age 83%
 
@@
 # only 54 parents completed the EPAQ
+
 modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
-summary(modTTRE) # conditionexp, RR, genderM, parent_ed 
-get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
-p_direction(modTTRE, effects="all") # RR 91.00%  parent_ed 92.17%
+summary(modTTRE) 
+p_direction(modTTRE, effects="all") # RR 87%  parent_ed 90.9%
 
@@
 summary(modMTLDE) #
-p_direction(modMTLDE, effects="all") # AA 85.60% RR 85.02% age 55.80% genderM 85.12%
+p_direction(modMTLDE, effects="all") # genderM 85%, RR 85%, AA 77%..
 
@@
 get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # 
-p_direction(tokens_modE, effects="all") # RR 71% parent_ed 90%
+p_direction(tokens_modE, effects="all") # RR 73.5% parent_ed 90.5%
 
@@
 summary(types_modE) 
-p_direction(types_modE, effects="all") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
-get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
+p_direction(types_modE, effects="all") # EL 84% AA 79% genderM 79%, parent_ed 89% cond:AA 96.3%
 e1types_condAA = get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA') # ADD THIS TO TEXT
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
-For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range.
+For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range (see Appendix for more an illustrated explanation).
 There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no predicted influence of age.
-Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no notable influence of age.
+Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018].
-Our ESS ranges from 2,000-5,000, and thus we go with the tighter, more stable interval.
+[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018; @bayestestR].
+Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.
 
@@
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the rate of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using tokens at a higher rate in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)` tokens/min, bootstrapped 95% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using tokens at a higher rate in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)` tokens/min, bootstrapped 95% confidence interval (conf.
 int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
@@
 # Total number of bids
-e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
+e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja, adapt_delta = .98) # 
 summary(e1bids_mod) 
+p_direction(e1bids_mod, effects="all") # condition
 e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # .72
-p_direction(e1bids_mod, effects="all")
 
@@
 
-e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
-summary(e1tja_mod) # NA
-p_direction(e1tja_mod, effects="all")
-
-e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
-summary(e1tjadur_mod) # NA
-p_direction(e1tjadur_mod, effects="all") # condition 91%
-
 # Episodes of passive joint attention.
@@
 summary(e1pja_mod) # NA
-p_direction(e1pja_mod, effects="all") # condition 84.5%
+p_direction(e1pja_mod, effects="all") # condition 89%
 
 # Episodes of coordinated joint attention.
-e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
+e1cja_mod <- stan_lmer(paste("cja", model_string), adapt_delta = 0.99, data = e1ja) 
 summary(e1cja_mod) # NA
-p_direction(e1cja_mod, effects="all") # condition 80%
+p_direction(e1cja_mod, effects="all") # condition 81%
 
 # Total duration of passive joint attention.
-e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
+e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja, adapt_delta=.98)
 summary(e1pja_time_mod) # NA
-p_direction(e1pja_time_mod, effects="all") # condition 85.7%
+p_direction(e1pja_time_mod, effects="all") # condition 90.6%
 
@@
 summary(e1cja_time_mod) # NA
-p_direction(e1cja_time_mod, effects="all") # cond*age 85%
+p_direction(e1cja_time_mod, effects="all") # cond*age 86%
 ```
@@
 Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, `r print_CI(e1bids)`).
-Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
+Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
 There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
-Figure \@ref(fig:JA) (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.
+Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.
 
@@
 summary(e1bids_modE) # cond, gender 
+p_direction(e1bids_modE, effects="all")
 e1bidsE = get_stan_glmer_reporting_values(e1bids_modE, "genderM") # .73 [.11,1.36] REPORT
-p_direction(e1bids_modE, effects="all")
+
+e1bidsE_M <- e1ja %>% group_by(gender) %>% 
+  summarise(mean = mean(bids), sd = sd(bids))
 
@@
 e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
+p_direction(e1cja_modE, effects="all") # RR 89% parent_ed 89%
 summary(e1cja_modE) # NA
-p_direction(e1cja_modE, effects="all") # RR 86% parent_ed 89%
 
@@
 summary(e1pja_modE) # condition*RR beta=1.8, RR close
-e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 89% CI = [-.65,-.02]  REPORT
-#e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed") # -.23 [-.47,.02] pd=.97 REPORT?
+p_direction(e1pja_modE, effects="all") # RR 98%, parent_ed 98%
+e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 89% CI = [-.65,-.02]  
 e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR") # .60 [.14,1.05]
-p_direction(e1pja_modE, effects="all")
+e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed")
 
@@
 summary(e1pja_time_modE) # NA
-p_direction(e1pja_time_mod, effects="all") # condition 85.7%
+p_direction(e1pja_time_mod, effects="all") # condition 91%
 
@@
 summary(e1cja_time_modE) # NA
-p_direction(e1cja_time_mod, effects="all") # condition 85.1%
+p_direction(e1cja_time_mod, effects="all") # condition:age 86%
 ```
 
-We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
 These models included random intercepts per video. 
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaRR)`).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).
+Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
+First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: $\beta=`r e1types_condAA["conditionexp:AA"]`$, `r print_CI(e1types_condAA)`).
+Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["RR"]`$, `r print_CI(e1pjaRR)`).
+However, higher RR parents who saw an Activity Video did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).
+This regression also found that more educated parents showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
+Finally, parents made bids for JA at a higher rate with male children than with female children (male mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min, female mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$ `r print_CI(e1bidsE)`).
 
-To better understand the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
 Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
@@
 However, parents who watched an activity video also made more bids for JA with their child.
-While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
+This did not result in a greater number of successful episodes of JA---passive or coordinated---than dyads in the No Video condition, although low reliability in passive JA coding (which led us to refine our JA coding guidelines for Experiment 2) may limit our ability to detect an effect there.
 In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, expand the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
+<!-- discuss exploratory regression results? -->
 
@@
 
-Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
+Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words tokens per minute to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
@@
 Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e2ld$play_duration), 2)` min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report preregistered regressions[^6] predicting TTR and number of tokens per minute of play, as well as an exploratory regression predicting MTLD per minute.
+We first report preregistered regressions[^6] predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
@@
 # Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
-# “secondary analyses"
+# "secondary analyses"
 # We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.
@@
 e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2ld) 
-summary(e2TTR_m) # conditionexp beta=-.1 89% CI=[-.2,0.0]
+summary(e2TTR_m) 
+p_direction(e2TTR_m, effects="all") # condition, age 85%
 e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
-p_direction(e2TTR_m, effects="all") # age 85.6% age:cond 78%
 
@@
 summary(e2tokens_m) # NA 
-print(e2tokens_m, digits=2)
-p_direction(e2tokens_m, effects="all") 
+p_direction(e2tokens_m, effects="all") # condition 90%
 #launch_shinystan(e2tokens_m, ppd = FALSE)
@@
 summary(e2MTLD_m) # NA
-p_direction(e2MTLD_m, effects="all") # cond 77.9% age:cond 84.2%
+p_direction(e2MTLD_m, effects="all") # cond 76% age:cond 83%
 
@@
   summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
-# predict word types (NOT A PREREGISTERED REGRESSION)
-#types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
-#summary(types_mod) # NA
 ```
@@
 summary(e2bids_m) # condition mean=3.1, 95%CI = [1.1, 5.0]
+p_direction(e2bids_m, effects="all") # age 84%
 e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")
-p_direction(e2bids_m, effects="all") # age 82%
 
@@
 summary(e2tja_m) # total episodes of joint attention -- age, age*condition, condition
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             7.3    0.4    6.4    7.0    7.3    7.6    8.2 
-# age                                    -5.0    1.7   -8.2   -6.1   -5.0   -3.9   -1.6 
-# ConditionVideo                          1.5    0.6    0.3    1.1    1.5    1.9    2.8 
-# age:ConditionVideo                      5.6    2.5    0.7    3.9    5.7    7.4   10.5 
+p_direction(e2tja_m, effects="all") # age, cond, age:cond
 e2tjaAge = get_stan_glmer_reporting_values(e2tja_m, "age")
@@
 e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionActivity Video")
-p_direction(e2tja_m, effects="all") # age, cond, age:cond
 ```
@@
 summary(e2cja_m) #
+p_direction(e2cja_m, effects="all") # cond, age:cond, age 90%
 e2cjaCond <- get_stan_glmer_reporting_values(e2cja_m, "ConditionActivity Video")
 e2cjaAgeCond <- get_stan_glmer_reporting_values(e2cja_m, "age:ConditionActivity Video")
-p_direction(e2cja_m, effects="all") # cond, age:cond
 
@@
 summary(e2pja_m) # age beta=-2.7 89% CI=[-5.1,0.0]
+p_direction(e2pja_m, effects="all") # age 
 e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")
-p_direction(e2pja_m, effects="all") # age
 
@@
 summary(e2pjat_m) # age: est: -17.97 89% CI = [-33.37,-2.41] 
+p_direction(e2pjat_m, effects="all") # age
 e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")
-p_direction(e2pjat_m, effects="all") # age
 
@@
 e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(e2cjat_m) # age: est: 35.3 89% CI = [1.57,67.4] 
+summary(e2cjat_m) 
+p_direction(e2cjat_m, effects="all") # age, cond 85%, age:cond 86%
 e2cjat <- get_stan_glmer_reporting_values(e2cjat_m, "age")
-p_direction(e2cjat_m, effects="all") # age, cond 84.4%, age:cond 86.2%
-
-e2tjat_m <- stan_glmer(total_lja ~ age * Condition + (1|video), data=e2ja)
-summary(e2tjat_m) # anything here? close!
-p_direction(e2tjat_m, effects="all") # age 85.3%, cond 89%, age:cond 90.4%
 ```

### 2020-04-01 paper/manuscript.tex
final stats check

@@
 \textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
-\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4629}
+\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 5056}
 \usepackage{csquotes}
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
-For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski, Ben-Shachar, Chen, \& Lüdecke (2019)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; McElreath, 2018).
-Our ESS is approximately 2,100, and thus we go with the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range.
-There was lower TTR in the Activity Video condition (mean: 0.10) than in the No Video condition (mean: 0.14, \(\beta=\)-0.04, 89\% CI={[}-0.052, -0.027{]}, \emph{pd}= 1).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 5.46) than in the No Video condition (mean: 8.49, \(\beta=\)-3.04, 89\% CI={[}-4.505, -1.448{]}, \emph{pd}= 0.998{]}), with no predicted influence of age.
-Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski et al.
+(2019a)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; Makowski et al., 2019b; McElreath, 2018).
+Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range (see Appendix for more an illustrated explanation).
+There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1{]}), with no notable influence of age.
+Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the rate of word tokens (\(\beta=\) 16.50, 89\% CI={[}5.778, 27.201{]}, \emph{pd}= 0.994), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf.
-int.): {[}193, 259{]}) than in the No Video condition (mean: 52, 95\% conf.
-int.: {[}139, 194{]}).
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens (\(\beta=\) 16.50, 89\% CI = {[}5.78, 27.2{]}, \emph{pd} = 0.99), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf.
+int.): {[}60, 79{]}) than in the No Video condition (mean: 52, 95\% conf.
+int.: {[}44, 61{]}).
 
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 89\% CI={[}0.27, 1.16{]}, \emph{pd}= 0.99).
-Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
+Parents' bid rate was greater in the Activity Video condition (mean: 3, sd: 1.11) than in the No Video condition (mean: 2.15, sd: 1.02, \(\beta=0.72\), 89\% CI = {[}0.12, 1.32{]}, \emph{pd} = 0.97).
+Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
 There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
@@
 
-We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
 These models included random intercepts per video.
-Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 89\% CI={[}-0.599, -0.078{]}, \emph{pd}= 0.98).
-However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 89\% CI={[}0.221, 0.955{]}, \emph{pd}= 0.992).
+Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
+First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
+Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
+However, higher RR parents who saw an Activity Video did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
+This regression also found that more educated parents showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
+Finally, parents made bids for JA at a higher rate with male children than with female children (male mean: 2.76 bids/min, female mean: 2.49, \(\beta=0.82\) 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).
 
-To better understand the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
 Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.
@@
 However, parents who watched an activity video also made more bids for JA with their child.
-While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
+This did not result in a greater number of successful episodes of JA---passive or coordinated---than dyads in the No Video condition, although low reliability in passive JA coding (which led us to refine our JA coding guidelines for Experiment 2) may limit our ability to detect an effect there.
 In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, expand the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
@@
 We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
-Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and number of tokens per minute of play, as well as an exploratory regression predicting MTLD per minute.
+Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: 0.12) than after the Science Video (mean: 0.15, \(\beta=-0.03\), , 89\% CI={[}-0.046, -0.014{]}, \emph{pd}= 0.997).
+This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.05{]}, \emph{pd} = 1).
 The preregistered regression predicting the number of tokens used by parents revealed no effects.
@@
 \hline
-Science Video & 0.15 & 0.03 & 7.28 & 3.41 & 28.05 & 8.54 & 61.85 & 23.58\\
+Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 28.05 & 8.54 & 61.85 & 23.58\\
 \hline
-Activity Video & 0.12 & 0.04 & 6.74 & 2.80 & 26.57 & 8.39 & 77.22 & 32.09\\
+Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 26.57 & 8.39 & 77.22 & 32.09\\
 \hline
@@
 We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf.
-int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 89\% CI={[}0.51, 1.53{]}, \emph{pd}= 1)) than after the Science Video (mean: 3.18, 95\% conf.
-int.: {[}2.81, 3.54{]}).
+Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf.
+int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1)) than after the Science Video (mean: 3.19, 95\% conf.
+int.: {[}2.83, 3.57{]}).
 There were no other effects on parental bids for JA.
 
-The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf.
-int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf.
-int.: {[}2.13, 2.61{]}).
-Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 89\% CI={[}-2.46, -0.63{]}, \emph{pd}= 0.99).
-However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 89\% CI={[}0.33, 2.99{]}, \emph{pd}= 0.97): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf.
+int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf.
+int.: {[}2.12, 2.60{]}).
+Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.57\), 89\% CI = {[}-2.42, -0.65{]}, \emph{pd} = 1).
+However, this age effect was moderated in the Activity Video condition (\(\beta=1.69\), 89\% CI = {[}0.34, 2.98{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI={[}0.143, 0.769{]}, \emph{pd}= 0.989), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
-There was an interaction of age and condition (\(\beta=1.60\), 89\% CI={[}0.405, 2.874{]}, \emph{pd}= 0.984), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.13, 0.77{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
+There was an interaction of age and condition (\(\beta=1.59\), 89\% CI = {[}0.35, 2.94{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
 
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 89\% CI={[}-1.514, -0.166{]}, \emph{pd}= 0.972), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 89\% CI={[}-0.01, -0.002{]}, \emph{pd}= 0.99).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.54, -0.2{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.92\), 89\% CI = {[}-9.85, -1.83{]}, \emph{pd} = 0.99).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 A., \& Lüdecke, D.
-(2019).
+(2019a).
 Indices of effect existence and significance in the bayesian framework.
@@
 \url{http://doi.org/10.3389/fpsyg.2019.02767}
+
+\leavevmode\hypertarget{ref-bayestestR}{}%
+Makowski, D., Ben-Shachar, M.
+S., \& Lüdecke, D.
+(2019b).
+BayestestR: Describing effects and their uncertainty, existence and significance within the bayesian framework.
+\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
+\url{http://doi.org/10.21105/joss.01541}
 

### 2020-04-08 paper/appendix-Bayesian-analyses.Rmd
fixed a couple NAs and line 328 issue, and improved appendix

@@
   return(c(beta,ci))
+}
+
+# pars are specific to E1
+plot_posterior <- function(mod, title="") {
+  posterior <- as.matrix(mod)
+  plot_title <- ggtitle(title)
+  mcmc_areas(posterior,
+           pars = c("conditionexp", 
+                    "EL", "AA", "RR", 
+                    "age", "genderM", "parent_ed", 
+                    "conditionexp:EL",
+                    "conditionexp:AA",
+                    "conditionexp:RR"),
+           prob = 0.89, prob_outer = 0.95, point_est = "mean") + 
+           theme(plot.margin=unit(c(-25,2,2,2),"mm")) +
+           annotate("text", x = -0, y = 10.63, label = title)
 }
@@
 pd = p_direction(types_modE, effects="fixed") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
+
+tok_modE1 <- stan_glmer(paste("tokens", e1model_string), data=e1ld) 
+mtld_modE1 <- stan_glmer(paste("MTLD", e1model_string), data=e1ld) 
+ttr_modE1 <- stan_glmer(paste("TTR", e1model_string), data=e1ld) 
 ```
@@
 
-```{r, parent-ed-effect, echo=F, fig.cap="Figure 1.
-Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
+```{r, parent-ed-effect, echo=F, fig.cap="Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
 dat = types_modE %>% posterior_samples("parent_ed") %>%
@@
 The outermost 5% of each posterior distribution is clipped and not shown."}
-posterior <- as.matrix(types_modE)
+plot_posterior(types_modE, title="Exp. 1: Word Types")
+```
 
-#plot_title <- ggtitle("Posterior distributions", "with means and 89% credible intervals")
-mcmc_areas(posterior,
-           pars = c("conditionexp", 
-                    "EL", "AA", "RR", 
-                    "age", "genderM", "parent_ed", 
-                    "conditionexp:EL",
-                    "conditionexp:AA",
-                    "conditionexp:RR"),
-           prob = 0.89,
-           prob_outer = 0.95,
-           point_est = "mean") + #+ plot_title
-  theme(plot.margin=unit(c(-30,2,2,2),"mm"))
+```{r, plot-token-posterior, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals.
+The outermost 5% of each posterior distribution is clipped and not shown."}
+
+#e1ed = get_stan_glmer_reporting_values(tok_modE1, 'parent_ed') 
+#pd = p_direction(tok_modE1, effects="fixed") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
+
+plot_posterior(tok_modE1, "Exp. 1: Word Tokens")
+
 ```
+
+```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting TTR, with means and 89% credible intervals.
+The outermost 5% of each posterior distribution is clipped and not shown.", warning=F}
+plot_posterior(ttr_modE1, "Exp. 1: TTR")
+```
+
+```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting MTLD, with means and 89% credible intervals.
+The outermost 5% of each posterior distribution is clipped and not shown."}
+plot_posterior(mtld_modE1, "Exp. 1: MTLD")
+```

### 2020-04-08 paper/manuscript.Rmd
fixed a couple NAs and line 328 issue, and improved appendix

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "5052"
+wordcount         : "4995"
 
@@
 Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
-Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
+Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
 Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
-Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
+Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for time spent in coordinated JA episodes.
 
@@
 Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
-Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).
+Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (we use 0.72, as proposed by McCarthy & Jarvis).
 
@@
 There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no notable influence of age.
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`), with no notable influence of age.
 Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["RR"]`$, `r print_CI(e1pjaRR)`).
-However, higher RR parents who saw an Activity Video did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).
-This regression also found that more educated parents showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
-Finally, parents made bids for JA at a higher rate with male children than with female children (male mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min, female mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$ `r print_CI(e1bidsE)`).
+However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).
+Parents with higher education also showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
+Finally, parents with male children made bids for JA at a higher rate (mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min) than those with female children (mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$, `r print_CI(e1bidsE)`).
 
@@
 Sixteen parents reported their child was of Hispanic origin. 
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed["3"]`), four-year college (n = `r e2_parent_ed["4"]`), some graduate school (n = `r e2_parent_ed["5"]`), to completed graduate school (n = `r e2_parent_ed["6"]`) or declined to state (n = 13).
 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
-The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for time spent (secs/min) in passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for time spent in coordinated JA episodes.
 
@@
 
-[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
-Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).
+[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some regressions led us to switch to Bayesian regression.
+Using a Bayesian analysis has the added benefit of not requiring arbitrary changes to alpha levels to correct for multiple comparisons (Gelman, 2008).
 
@@
 Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
-The means of the lexical measures are shown in Table \ref{e2tab}.
+The means of the lexical measures are shown in Table 1.
 
@@
             "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
+names(e2) = c("Condition","TTR", "(sd)", "MTLD", "(sd)", "Types", "(sd)", "Tokens", "(sd)")
+#kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
+apa_table(e2, caption = "Mean lexical diversity measures in Experiment 2.")
 ```
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, `r print_CI(e2bids)`)) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, `r print_CI(e2bids)`) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
+The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, `r print_CI(e2tjaCond)`), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
@@
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
-
 Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, `r print_CI(e2pja)`), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, `r print_CI(e2pjat)`).
@@
 As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
-The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".
+The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".
 
@@
 
-The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions.
+The short, activity-oriented parenting messages we used encouraged parents to make more attempts---both verbal and non-verbal---to engage their child, supporting their use as a component of interventions.
 Why were they successful? 
@@
 This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
-Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.
+Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
 

### 2020-04-08 paper/manuscript.tex
fixed a couple NAs and line 328 issue, and improved appendix

@@
 \textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
-\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 5056}
+\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4995}
 \usepackage{csquotes}
@@
 Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
-Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
+Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
 Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
-Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
+Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for time spent in coordinated JA episodes.
 
@@
 Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
-Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy \& Jarvis (2010): 0.720).
+Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (we use 0.72, as proposed by McCarthy \& Jarvis).
 
@@
 There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1{]}), with no notable influence of age.
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1), with no notable influence of age.
 Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
-However, higher RR parents who saw an Activity Video did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
-This regression also found that more educated parents showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
-Finally, parents made bids for JA at a higher rate with male children than with female children (male mean: 2.76 bids/min, female mean: 2.49, \(\beta=0.82\) 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).
+However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
+Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
+Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.82\), 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).
 
@@
 Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).
 
@@
 To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
-The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for time spent (secs/min) in passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for time spent in coordinated JA episodes.
 
@@
 Parents' child-directed speech during the play sessions (mean duration: 3.08 min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
-Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
+We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some regressions led us to switch to Bayesian regression.
+Using a Bayesian analysis has the added benefit of not requiring arbitrary changes to alpha levels to correct for multiple comparisons (Gelman, 2008).} predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
@@
 Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
-The means of the lexical measures are shown in Table \ref{e2tab}.
+The means of the lexical measures are shown in Table 1.
 
-\begin{table}
-
-\caption{\label{tab:e2tab}\label{e2tab} Lexical diversity measures in Experiment 2.}
-\centering
-\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
-\hline
-Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
-\hline
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:e2tab}Mean lexical diversity measures in Experiment 2.}
+\begin{tabular}{lllllllll}
+\toprule
+Condition & \multicolumn{1}{c}{TTR} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{MTLD} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Types} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Tokens} & \multicolumn{1}{c}{(sd)}\\
+\midrule
 Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 28.05 & 8.54 & 61.85 & 23.58\\
-\hline
 Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 26.57 & 8.39 & 77.22 & 32.09\\
-\hline
+\bottomrule
 \end{tabular}
+\end{threeparttable}
+\end{center}
 \end{table}
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf.
-int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1)) than after the Science Video (mean: 3.19, 95\% conf.
+int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf.
 int.: {[}2.83, 3.57{]}).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf.
+The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), 89\% CI = {[}0.18, 0.84{]}, \emph{pd} = 0.99), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf.
 int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf.
@@
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
-
 Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.54, -0.2{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.92\), 89\% CI = {[}-9.85, -1.83{]}, \emph{pd} = 0.99).
@@
 As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
-The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
+The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uh-oh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
 
@@
 
-The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions.
+The short, activity-oriented parenting messages we used encouraged parents to make more attempts---both verbal and non-verbal---to engage their child, supporting their use as a component of interventions.
 Why were they successful?
@@
 This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
-Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.
+Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
 

### 2020-04-28 paper/manuscript.Rmd
anonymous view-only links for blind peer review

@@
   In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
-  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
+  The rise of phone-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
   Of special interest are the parents of very young children, who are often difficult to reach in other ways.
 Yet little is known about the effects of communicating to parents through app-based interventions.
-  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention.
+  We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
   Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
@@
 output            : papaja::apa6_pdf
-appendix: "appendix.Rmd"
 ---
@@
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).
 
@@
 
-## Results and Discussion
+## Results
 
@@
 
-[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf)
+[^3]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982)
 
@@
 
-To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) for the interactive corpus characteristic plot).
 Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
@@
 
-[^5]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf).
+[^5]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982).
 
@@
 
-```{r e2token-type, include=F}
-# NOT INCLUDED
-e2typ <- e2ld %>% group_by(Condition) %>%
-  tidyboot_mean(types)
-
-e2types <- ggplot(e2typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ld, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Word Types per Minute") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-#multiplot(e2tokens, e2types, cols=2)
-```
-
 ```{r, e2-effect-size, echo=F, include=F}
@@
 
-As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
+As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp2_characteristic_chart.html)).
 The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".
@@
 
-e2cja_age = ggplot(e2ja, aes(x = age, y = cja, group=Condition, colour = Condition)) +
+e2cja_age = ggplot(e2ja, aes(x = Age, y = cja, group=Condition, colour = Condition)) +
   geom_point(alpha=.7) + geom_smooth(method='lm') + 
@@
 \endgroup
-
-```{r echo = FALSE, results = 'asis'}
-render_appendix('appendix.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis'}
-render_appendix('appendix.Rmd')
-```

### 2020-04-28 paper/manuscript.tex
anonymous view-only links for blind peer review

@@
 In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
-The rise of phone- and tablet-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
+The rise of phone-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
 Of special interest are the parents of very young children, who are often difficult to reach in other ways.
 Yet little is known about the effects of communicating to parents through app-based interventions.
-We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention.
+We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
 Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
@@
 
-\hypertarget{results-and-discussion}{%
-\subsection{Results and Discussion}\label{results-and-discussion}}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
@@
 
-\hypertarget{results-and-discussion-1}{%
-\subsection{Results and Discussion}\label{results-and-discussion-1}}
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf.
-int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf.
+int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.56{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf.
 int.: {[}2.83, 3.57{]}).
@@
 
-The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), 89\% CI = {[}0.18, 0.84{]}, \emph{pd} = 0.99), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf.
+The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), 89\% CI = {[}0.18, 0.85{]}, \emph{pd} = 0.99), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf.
 int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf.
 int.: {[}2.12, 2.60{]}).
-Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.57\), 89\% CI = {[}-2.42, -0.65{]}, \emph{pd} = 1).
-However, this age effect was moderated in the Activity Video condition (\(\beta=1.69\), 89\% CI = {[}0.34, 2.98{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.60\), 89\% CI = {[}-2.46, -0.7{]}, \emph{pd} = 0.99).
+However, this age effect was moderated in the Activity Video condition (\(\beta=1.73\), 89\% CI = {[}0.36, 3.06{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.13, 0.77{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
-There was an interaction of age and condition (\(\beta=1.59\), 89\% CI = {[}0.35, 2.94{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.47\), 89\% CI = {[}0.14, 0.78{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
+There was an interaction of age and condition (\(\beta=1.64\), 89\% CI = {[}0.42, 2.95{]}, \emph{pd} = 0.99), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.54, -0.2{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.92\), 89\% CI = {[}-9.85, -1.83{]}, \emph{pd} = 0.99).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.52, -0.19{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.96\), 89\% CI = {[}-9.82, -1.98{]}, \emph{pd} = 0.99).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 
-\leavevmode\hypertarget{ref-Baldwin1991}{}%
-Baldwin, D. (1991). Infants' contribution to the achievement of joint reference. \emph{Child Development}, \emph{62}, 875--890.
-
-\leavevmode\hypertarget{ref-Bigelow2004}{}%
-Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint attention in the development of infants' play with objects. \emph{Developmental Science}, \emph{7}, 518--526.
-
-\leavevmode\hypertarget{ref-Breitenstein2016}{}%
-Breitenstein, S.
-M., Fogg, L., Ocampo, E.
-V., Acosta, D.
-I., \& Gross, D.
-(2016).
-Parent use and efficacy of a self-administered, tablet-based parent training intervention: A randomized controlled trial.
-\emph{JMIR mHealth and uHealth}, \emph{4}(2), e36.
-\url{http://doi.org/10.2196/mhealth.5202}
-
-\leavevmode\hypertarget{ref-Breitenstein2014}{}%
-Breitenstein, S.
-M., Gross, D., \& Christophersen, R.
-(2014).
-Digital delivery methods of parenting training interventions: A systematic review.
-\emph{Worldviews on Evidence-Based Nursing}, \emph{11}, 168--176.
-
-\leavevmode\hypertarget{ref-Cartmill2013}{}%
-Cartmill, E.
-A., Armstrong, B.
-F., Gleitman, L.
-R., Goldin-Meadow, S., Medina, T.
-N., \& Trueswell, J.
-C.
-(2013).
-Quality of early parent input predicts child vocabulary 3 years later.
-\emph{Proceedings of the National Academy of Sciences}, \emph{110}(28), 11278--11283.
-\url{http://doi.org/10.1073/pnas.1309518110}
-
-\leavevmode\hypertarget{ref-Jamaica2014}{}%
-Gertler, P., Heckman, J., Pinto, R., Zanolini, A., Vermeersch, C., Walker, S., \ldots{} Grantham-McGregor, S.
-(2014).
-Labor market returns to an early childhood stimulation intervention in jamaica.
-\emph{Science}, \emph{344}(6187), 998--1001.
-\url{http://doi.org/10.1126/science.1251178}
-
-\leavevmode\hypertarget{ref-rstanarm}{}%
-Goodrich, B., Gabry, J., Ali, I., \& Brilleman, S. (2018). Rstanarm: Bayesian applied regression modeling via Stan. Retrieved from \url{http://mc-stan.org/}
-
-\leavevmode\hypertarget{ref-Hart1995}{}%
-Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the everyday experience of young american children}. Baltimore, MD: Brookes.
-
-\leavevmode\hypertarget{ref-Heckman2006}{}%
-Heckman, J. J. (2006). Skill formation and the economics of investing in disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902. \url{http://doi.org/10.1126/science.1128898}
-
-\leavevmode\hypertarget{ref-Hembacher2020}{}%
-Hembacher, E., \& Frank, M.
-C.
-(2020).
-The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development.
-\emph{Collabra: Psychology}, \emph{6}(1).
-\url{http://doi.org/10.31234/osf.io/hxk3d}
-
-\leavevmode\hypertarget{ref-HirshPasek2015}{}%
-Hirsh-Pasek, K., Adamson, L.
-B., Bakeman, R., Owen, M.
-T., Golinkoff, R.
-M., Pace, A., \ldots{} Suma, K.
-(2015).
-The contribution of early communication quality to low-income children's language success.
-\emph{Psychological Science}, \emph{26}(7), 1071--1083.
-\url{http://doi.org/10.1177/0956797615581493}
-
-\leavevmode\hypertarget{ref-Kruschke2014}{}%
-Kruschke, J. (2014). \emph{Doing bayesian data analysis: A tutorial with r, jags, and stan}. Academic Press.
-
-\leavevmode\hypertarget{ref-Leung2018}{}%
-Leung, C.
-Y., Hernandez, M.
-W., \& Suskind, D.
-L.
-(2018).
-Enriching home language environment among families from low-ses backgrounds: A randomized controlled trial of a home visiting curriculum.
-\emph{Early Childhood Research Quarterly}.
-\url{http://doi.org/https://doi.org/10.1016/j.ecresq.2018.12.005}
-
-\leavevmode\hypertarget{ref-Makowski2019}{}%
-Makowski, D., Ben-Shachar, M.
-S., Chen, S.
-H.
-A., \& Lüdecke, D.
-(2019a).
-Indices of effect existence and significance in the bayesian framework.
-\emph{Frontiers in Psychology}, \emph{10}, 2767.
-\url{http://doi.org/10.3389/fpsyg.2019.02767}
-
-\leavevmode\hypertarget{ref-bayestestR}{}%
-Makowski, D., Ben-Shachar, M.
-S., \& Lüdecke, D.
-(2019b).
-BayestestR: Describing effects and their uncertainty, existence and significance within the bayesian framework.
-\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
-\url{http://doi.org/10.21105/joss.01541}
-
-\leavevmode\hypertarget{ref-Malvern2004}{}%
-Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). \emph{Lexical diversity and language development}. Palgrave Macmillan.
-
-\leavevmode\hypertarget{ref-Marchman2008}{}%
-Marchman, V.
-A., \& Fernald, A.
-(2008).
-Speed of word recognition and vocabulary knowledge in infancy predict cognitive and language outcomes in later childhood.
-\emph{Developmental Science}, \emph{11}, F9--F16.
-
-\leavevmode\hypertarget{ref-McCarthy2010}{}%
-McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A validation study of sophisticated approaches to lexical diversity assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.
-
-\leavevmode\hypertarget{ref-McElreath2018}{}%
-McElreath, R. (2018). \emph{Statistical rethinking: A bayesian course with examples in r and stan}. Chapman; Hall/CRC.
-
-\leavevmode\hypertarget{ref-Schwab2016}{}%
-Schwab, J. F., \& Lew-Williams, C. (2016). Language learning, socioeconomic status, and child-directed speech. \emph{WIREs Cognitive Science}, \emph{7}, 264--275. \url{http://doi.org/10.1002/wcs.1393}
-
-\leavevmode\hypertarget{ref-PerryPreschool2004}{}%
-Schweinhart, L.
-J., Montie, J., Xiang, Z., Barnett, W.
-S., Belfield, C.
-R., \& Nores, M.
-(2004).
-\emph{Lifetime effects: The highscope perry preschool study through age 40}.
-Ypsilanti, MI: HighScope Press.
-
-\leavevmode\hypertarget{ref-datavyu}{}%
-Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}. Retrieved from \url{http://datavyu.org}
-
-\leavevmode\hypertarget{ref-Weisberg2013}{}%
-Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain, and Education}, \emph{7}, 104--112.
-
-\leavevmode\hypertarget{ref-Wood1976}{}%
-Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in problem solving. \emph{Journal of Child Psychology and Psychiatry}, \emph{17}, 89--100.
-
 \endgroup
 
-\clearpage
-\makeatletter
-\efloat@restorefloats
-\makeatother
-
-\begin{appendix}
-\section{}
-\hypertarget{experiment-1-activities}{%
-\subsection{Experiment 1 Activities}\label{experiment-1-activities}}
-
-\hypertarget{video-a-6-11.9-months-pick-it-up}{%
-\subsubsection{Video A (6-11.9 months) ``Pick it
-up''}\label{video-a-6-11.9-months-pick-it-up}}
-
-Parents are told to encourage their child to pick up and drop individual
-objects. They are also encouraged to place toys on a small cloth and
-show the child that they can drag the cloth towards them to reach the
-toys.
-
-Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car
-
-\hypertarget{video-b-6-11.9-months-animal-sounds}{%
-\subsubsection{Video B (6-11.9 months) ``Animal
-sounds''}\label{video-b-6-11.9-months-animal-sounds}}
-
-Parents are told to call different animals and imitate different sounds
-the animals make. They are also encouraged to observe which animal the
-child prefers.
-
-Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls
-
-\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
-\subsubsection{Video C (12-17.9 months) ``Give me the
-toy''}\label{video-c-12-17.9-months-give-me-the-toy}}
-
-Parents are told to ask their child to hand over individual toys. They
-are also encouraged to praise the child after they give them the toys,
-and repeat the process until the child follows the verbal instructions.
-
-Props: toy boat, plastic frog, plastic elephant, toy bus
-
-\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
-\subsubsection{Video D (12-17.9 months) ``Classifying my
-toys''}\label{video-d-12-17.9-months-classifying-my-toys}}
-
-Parents are told to place toys of different sizes (big or small) in two
-hoops. They are also encouraged to ask their child to distinguish
-between two objects and identify which one is larger.
-
-Props: two yellow and green rings, big car, small car, big horse, small
-horse
-
-\hypertarget{video-e-18-23.9-months-my-toys}{%
-\subsubsection{Video E (18-23.9 months) ``My
-toys''}\label{video-e-18-23.9-months-my-toys}}
-
-Parents are told to show the child toys of the same shape but different
-sizes, to place one of the objects in a basket and to ask the child to
-take out the object. They are also encouraged to ask their child if the
-object is bigger or smaller compared to its pair.
-
-Props: two buckets, big car, small car, big horse, small horse
-
-\hypertarget{video-f-18-23.9-months-the-orchestra}{%
-\subsubsection{Video F (18-23.9 months) ``The
-orchestra''}\label{video-f-18-23.9-months-the-orchestra}}
-
-Parents are told to give their child a musical instrument to play. They
-are also encouraged to play a song and see if the child follows the
-rhythm.
-
-Props: maracas, drum, tambourine, clapper
-
-\hypertarget{experiment-2-activities}{%
-\subsection{Experiment 2 Activities}\label{experiment-2-activities}}
-
-\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
-\subsubsection{Video A (12-17.9 months) ``Give me the
-toy''}\label{video-a-12-17.9-months-give-me-the-toy}}
-
-Parents are told to ask their child to hand over individual toys. They
-are also encouraged to praise the child after they give them the toys,
-and repeat the process until the child follows the verbal instructions.
-
-Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow
-
-\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
-\subsubsection{Video B (12-17.9 months) ``Classifying my
-toys''}\label{video-b-12-17.9-months-classifying-my-toys}}
-
-Parents are told to place toys of different sizes (big or small) in two
-hoops. They are also encouraged to ask their child to distinguish
-between two objects and identify which one is larger.
-
-Props: two yellow and green rings, big car, small car, big horse, small
-horse
-
-\hypertarget{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}{%
-\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigsaw
-puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}}
-
-Parents are told to encourage their child to name different shapes on a
-jigsaw puzzle. Then they are told to undo the puzzle and invite the
-child to complete the puzzle.
-
-Props: A jigsaw puzzle of geometric shapes
-
-\hypertarget{video-d-18-23.9-months-my-toys}{%
-\subsubsection{Video D (18-23.9 months) ``My
-toys''}\label{video-d-18-23.9-months-my-toys}}
-
-Parents are told to show the child toys of the same shape but different
-sizes, to place one of the objects in a basket and to ask the child to
-take out the object. They are also encouraged to ask their child if the
-object is bigger or smaller compared to its pair.
-
-Props: two buckets, big car, small car, big horse, small horse
-
-\hypertarget{video-e-18-23.9-months-the-orchestra}{%
-\subsubsection{Video E (18-23.9 months) ``The
-orchestra''}\label{video-e-18-23.9-months-the-orchestra}}
-
-Parents are told to give their child a musical instrument to play. They
-are also encouraged to play a song and see if the child follows the
-rhythm.
-
-Props: maracas, drum, tambourine, clapper
-
-\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
-\subsubsection{Video F (18-23.9 months) ``My yellow
-toys''}\label{video-f-18-23.9-months-my-yellow-toys}}
-
-Parents are told to show their child yellow toys and to ask, ``What
-color are they?'' They are also told to give the child toys of different
-colors, to ask them to only play with the yellow ones, and to praise the
-child after they do so.
-
-Props: blue car, yellow car, yellow block, red block, blue block, green
-block
-\end{appendix}
-
 \end{document}

### 2020-04-28 paper/supp-Bayesian-analyses.Rmd
anonymous view-only links for blind peer review

--- 2020-04-08 paper/appendix-Bayesian-analyses.Rmd
@@
 ---
-title: 'Appendix: Bayesian Analysis Overview'
+title: 'Supplemental Materials: Bayesian Analysis Overview'
 output: pdf_document
 ---
+<!-- 424 words -->
 
@@
 
-```{r, parent-ed-effect, echo=F, fig.cap="Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
+```{r, parent-ed-effect, echo=F, fig.cap="Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0, warning=F}
 dat = types_modE %>% posterior_samples("parent_ed") %>%
@@
 ```{r, plot-posteriors, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals.
-The outermost 5% of each posterior distribution is clipped and not shown."}
+The outermost 5% of each posterior distribution is clipped and not shown.", warning=F}
 plot_posterior(types_modE, title="Exp. 1: Word Types")
@@
 ```{r, plot-token-posterior, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals.
-The outermost 5% of each posterior distribution is clipped and not shown."}
+The outermost 5% of each posterior distribution is clipped and not shown.", include=F}
 
@@
 ```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting TTR, with means and 89% credible intervals.
-The outermost 5% of each posterior distribution is clipped and not shown.", warning=F}
+The outermost 5% of each posterior distribution is clipped and not shown.", warning=F, include=F}
 plot_posterior(ttr_modE1, "Exp. 1: TTR")
@@
 ```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting MTLD, with means and 89% credible intervals.
-The outermost 5% of each posterior distribution is clipped and not shown."}
+The outermost 5% of each posterior distribution is clipped and not shown.", include=F}
 plot_posterior(mtld_modE1, "Exp. 1: MTLD")

### 2020-05-01 paper/manuscript.Rmd
final changes to abstract and keywords, trying to compile...

@@
 abstract: |
-  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
-  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
-  The rise of phone-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
-  Of special interest are the parents of very young children, who are often difficult to reach in other ways.
+  Early parenting practices play an important role in shaping children’s future outcomes. 
+  In particular, high-quality early interactions can facilitate language learning and school performance. 
+  The rise of phone-based parenting applications ("apps") could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
   Yet little is known about the effects of communicating to parents through app-based interventions. 
-  We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
-  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
-keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4995"
+  In two studies (one preregistered), we showed parents short videos depicting age-appropriate parent-child activities from a parenting app. 
+  We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2). 
+  These results suggest that activity videos can lead to positive changes in parent engagement, providing support for the use of such videos in parenting interventions.
+keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
+wordcount         : "4954"
 
@@
 documentclass     : "apa6"
-csl: apa6.csl
 classoption       : "man"
@@
 suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
-library("papaja")
+library(papaja)
 library(png)
@@
 
-<div id = "refs"></div>
+<div id="refs" custom-style="Bibliography"></div>
 \endgroup

### 2020-05-05 paper/manuscript.Rmd
fixed annoying YAML bug

@@
 
-authornote: |
-
 abstract: |
@@
 wordcount         : "4954"
-
 bibliography      : ["library.bib"]
-
 floatsintext      : yes

### 2020-08-26 paper/manuscript_anonymized.Rmd
added research highlights, video transcripts

--- 2020-05-05 paper/manuscript.Rmd
@@
 ---
-title             : "Understanding the impacts of video-guided activities on parent-child interaction"
-shorttitle        : "Impacts of videos on parent-child interaction"
-
+title: "Understanding the impacts of video-guided activities on parent-child interaction"
 author:
-  - name          : "George Kachergis"
-    affiliation   : "1"
-    address       : "Stanford, CA 94305 USA"
-    email         : "kachergis@stanford.edu"
-  - name          : "Emily Hembacher"
-    affiliation   : "1"
-  - name          : "Veronica Cristiano"
-    affiliation   : "2"
-  - name          : "Hanwen Vivian Zhang"
-    affiliation   : "3"
-  - name          : "Michael C. Frank"
-    corresponding : yes
-    address       : "Stanford, CA 94305 USA"
-    email         : "mcfrank@stanford.edu"
-    affiliation   : "1"
-
+- name: XXXX
+  corresponding: yes
+  affiliation: '1'
+  address: XXXX
+  email: XXXX
+- name: XXXX
+  affiliation: '1'
+- name: XXXX
+  affiliation: '2'
+- name: XXXX
+  affiliation: '3'
+- name: XXXX
+  address: XXXX
+  email: XXXX
+  affiliation: '1'
+shorttitle: Impacts of videos on parent-child interaction
+output:
+  papaja::apa6_pdf: default
+  papaja::apa6_docx: default
+abstract: "Early parenting practices play an important role in shaping children’s
+  future outcomes. \nIn particular, high-quality early interactions can facilitate
+  language learning and school performance. \nThe rise of phone-based parenting applications
+  (\"apps\") could deliver low-cost interventions on parenting style to a wide variety
+  of populations, especially the parents of very young children, who are often difficult
+  to reach in other ways. \nYet little is known about the effects of communicating
+  to parents through app-based interventions. \nIn two studies (one preregistered),
+  we showed parents short videos depicting age-appropriate parent-child activities
+  from a parenting app. \nWe found that after watching the video, parents spoke more
+  and made more bids for joint attention, as compared with controls who watched no
+  video (experiment 1) or a science video (experiment 2). \nThese results suggest
+  that activity videos can lead to positive changes in parent engagement, providing
+  support for the use of such videos in parenting interventions.\n"
+keywords: language development; parent intervention; childhood development; joint
+  attention; lexical diversity
+wordcount: '5066'
+bibliography: library.bib
+floatsintext: no
+figurelist: no
+tablelist: no
+footnotelist: no
+linenumbers: yes
+mask: no
+draft: no
+header-includes: \usepackage{float}
+documentclass: apa6
+classoption: man
 affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution    : "Gallaudet University"
-  - id            : "3"
-    institution    : "Cornell University"
-
-abstract: |
-  Early parenting practices play an important role in shaping children’s future outcomes. 
-  In particular, high-quality early interactions can facilitate language learning and school performance. 
-  The rise of phone-based parenting applications ("apps") could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
-  Yet little is known about the effects of communicating to parents through app-based interventions. 
-  In two studies (one preregistered), we showed parents short videos depicting age-appropriate parent-child activities from a parenting app. 
-  We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2). 
-  These results suggest that activity videos can lead to positive changes in parent engagement, providing support for the use of such videos in parenting interventions.
-keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
-wordcount         : "4954"
-bibliography      : ["library.bib"]
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-header-includes:
-  - \usepackage{float}
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
+- id: '1'
+  institution: XXXX
+- id: '2'
+  institution: XXXX
+- id: '3'
+  institution: XXXX
+authornote: |
+  The data that support the findings of this study are openly available in OSF at [XXXX]
 ---
@@
 
+# Research Highlights
+
+* After watching short activity videos in a parenting app, parents made more attempts to engage with their children and spoke more to them.
+* Older toddlers showed greater engagement after parents watched the activity videos, relative to younger toddlers.
+* These activity videos led parents to set more goals for their child during play. 
+* Our findings suggest that parent-led activities guided by apps may be helpful in scaffolding the play of older toddlers.
+
 # Introduction
@@
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting a children's museum in XXXX to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
 Parents were randomly assigned to one of two conditions: parents in the _Activity Video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
@@
 
-### Participants. 
-`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
+### Participants 
+`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in XXXX.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
@@
 
-### Materials.
+### Materials
 Stimuli included activity videos from a commercial parenting application. 
@@
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](XXX)).
+<!-- https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79 -->
 
-### Procedure.
+### Procedure
 After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
@@
 
-### Joint Attention Coding Procedure.
+### Joint Attention Coding Procedure
 The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
@@
 
-[^3]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982)
+[^3]: Preregistration: [XXX]
+<!-- https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982) -->
 
@@
 
-To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) for the interactive corpus characteristic plot).
+To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://cogsciguy.github.io/parenting_obs_language/Exp1_characteristic_chart.html)
+<!-- https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) --> for the interactive corpus characteristic plot). 
 Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
@@
 
-[^5]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982).
+[^5]: Preregistration: [XXX]
+<!-- [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982). -->
 
@@
 
-### Participants. 
+### Participants 
 `r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
@@
 
-### Materials.
-
+### Materials 
 The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
@@
 
-### Procedure. 
+### Procedure
 The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
@@
 
-As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp2_characteristic_chart.html)).
+As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions ([see SI](https://cogsciguy.github.io/parenting_obs_language/Exp2_characteristic_chart.html)).
+<!-- (https://osf.io/2bpdf/files/github/language_analyses/Exp2_characteristic_chart.html)). -->
 The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".
@@
 
+XXXX
+<!-- 
 This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
 Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion. 
+-->
 

### 2020-08-26 paper/manuscript_anonymized.tex
added research highlights, video transcripts

--- 2020-04-28 paper/manuscript.tex
@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
 \PassOptionsToPackage{hyphens}{url}
 %
-\documentclass[man,floatsintext]{apa6}
+\documentclass[
+  english,
+  man]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
   \IfFileExists{parskip.sty}{%
@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
   pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
-            pdfauthor={George Kachergis, Emily Hembacher, Veronica Cristiano, Hanwen Vivian Zhang, \& Michael C. Frank},
-            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided play},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  pdfauthor={XXXX1, XXXX1, XXXX2, XXXX3, \& XXXX1},
+  pdflang={en-EN},
+  pdfkeywords={language development; parent intervention; childhood development; joint attention; lexical diversity},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
 \ifx\paragraph\undefined\else
@@
 \fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\shorttitle{Impacts of videos on parent-child interaction}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
-\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4995}
-\usepackage{csquotes}
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{Impacts of videos on parent-child interaction}
+\keywords{language development; parent intervention; childhood development; joint attention; lexical diversity\newline\indent Word count: 5066}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 \linenumbers
+\usepackage{csquotes}
 \usepackage{float}
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[shorthands=off,main=english]{babel}
+\fi
 
 \title{Understanding the impacts of video-guided activities on parent-child interaction}
-\author{George Kachergis\textsuperscript{1}, Emily Hembacher\textsuperscript{1}, Veronica Cristiano\textsuperscript{2}, Hanwen Vivian Zhang\textsuperscript{3}, \& Michael C. Frank\textsuperscript{1}}
+\author{XXXX\textsuperscript{1}, XXXX\textsuperscript{1}, XXXX\textsuperscript{2}, XXXX\textsuperscript{3}, \& XXXX\textsuperscript{1}}
 \date{}
@@
 
-Correspondence concerning this article should be addressed to Michael C. Frank, Stanford, CA 94305 USA. E-mail: \href{mailto:mcfrank@stanford.edu}{\nolinkurl{mcfrank@stanford.edu}}}
+The data that support the findings of this study are openly available in OSF at {[}XXXX{]}
+
+Correspondence concerning this article should be addressed to XXXX, XXXX. E-mail: XXXX
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} XXXX\\\textsuperscript{2} XXXX\\\textsuperscript{3} XXXX}
 
 \abstract{
-Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
-In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
-The rise of phone-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
-Of special interest are the parents of very young children, who are often difficult to reach in other ways.
+Early parenting practices play an important role in shaping children's future outcomes.
+In particular, high-quality early interactions can facilitate language learning and school performance.
+The rise of phone-based parenting applications (``apps'') could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
 Yet little is known about the effects of communicating to parents through app-based interventions.
-We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
-Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
-
+In two studies (one preregistered), we showed parents short videos depicting age-appropriate parent-child activities from a parenting app.
+We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2).
+These results suggest that activity videos can lead to positive changes in parent engagement, providing support for the use of such videos in parenting interventions.
 }
@@
 \maketitle
+
+\hypertarget{research-highlights}{%
+\section{Research Highlights}\label{research-highlights}}
+
+\begin{itemize}
+\tightlist
+\item
+  After watching short activity videos in a parenting app, parents made more attempts to engage with their children and spoke more to them.
+\item
+  Older toddlers showed greater engagement after parents watched the activity videos, relative to younger toddlers.
+\item
+  These activity videos led parents to set more goals for their child during play.
+\item
+  Our findings suggest that parent-led activities guided by apps may be helpful in scaffolding the play of older toddlers.
+\end{itemize}
 
@@
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting a children's museum in XXXX to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
 Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
@@
 
-\hypertarget{participants.}{%
-\subsubsection{Participants.}\label{participants.}}
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
 
-60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
+60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in XXXX.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
@@
 
-\hypertarget{materials.}{%
-\subsubsection{Materials.}\label{materials.}}
+\hypertarget{materials}{%
+\subsubsection{Materials}\label{materials}}
 
@@
 Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (\href{XXX}{see SI}).
 
-\hypertarget{procedure.}{%
-\subsubsection{Procedure.}\label{procedure.}}
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
 
@@
 
-\hypertarget{joint-attention-coding-procedure.}{%
-\subsubsection{Joint Attention Coding Procedure.}\label{joint-attention-coding-procedure.}}
+\hypertarget{joint-attention-coding-procedure}{%
+\subsubsection{Joint Attention Coding Procedure}\label{joint-attention-coding-procedure}}
 
@@
 Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
-Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
+Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: {[}XXX{]}}, with any deviations or exploratory analyses noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
@@
 There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1), with no notable influence of age.
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.25, 89\% CI = {[}-14.25, -4.16{]}, \emph{pd} = 1), with no notable influence of age.
 Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens (\(\beta=\) 16.50, 89\% CI = {[}5.78, 27.2{]}, \emph{pd} = 0.99), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf.
+We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens (\(\beta=\) 16.56, 89\% CI = {[}6.38, 27.27{]}, \emph{pd} = 0.99), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf.
 int.): {[}60, 79{]}) than in the No Video condition (mean: 52, 95\% conf.
@@
 We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: 3, sd: 1.11) than in the No Video condition (mean: 2.15, sd: 1.02, \(\beta=0.72\), 89\% CI = {[}0.12, 1.32{]}, \emph{pd} = 0.97).
+Parents' bid rate was greater in the Activity Video condition (mean: 3, sd: 1.11) than in the No Video condition (mean: 2.15, sd: 1.02, \(\beta=0.72\), 89\% CI = {[}0.14, 1.32{]}, \emph{pd} = 0.98).
 Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
@@
 Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
-First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
-Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
-However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
-Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
-Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.82\), 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).
+First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.85\), 89\% CI = {[}0.74, 12.91{]}, \emph{pd} = 0.96).
+Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.35\), 89\% CI = {[}-0.63, -0.06{]}, \emph{pd} = 0.97).
+However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.22, 1.03{]}, \emph{pd} = 0.99).
+Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.46, -0.05{]}, \emph{pd} = 0.97).
+Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.81\), 89\% CI = {[}0.07, 1.57{]}, \emph{pd} = 0.96).
 
-To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (\href{https://cogsciguy.github.io/parenting_obs_language/Exp1_characteristic_chart.html}{see SI}
+for the interactive corpus characteristic plot).
 Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: {[}XXX{]}}
 
@@
 
-\hypertarget{participants.-1}{%
-\subsubsection{Participants.}\label{participants.-1}}
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
 
@@
 
-\hypertarget{materials.-1}{%
-\subsubsection{Materials.}\label{materials.-1}}
+\hypertarget{materials-1}{%
+\subsubsection{Materials}\label{materials-1}}
 
@@
 
-\hypertarget{procedure.-1}{%
-\subsubsection{Procedure.}\label{procedure.-1}}
+\hypertarget{procedure-1}{%
+\subsubsection{Procedure}\label{procedure-1}}
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.05{]}, \emph{pd} = 1).
+This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.04{]}, \emph{pd} = 1).
 The preregistered regression predicting the number of tokens used by parents revealed no effects.
@@
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:e2tab}Mean lexical diversity measures in Experiment 2.}
+
 \begin{tabular}{lllllllll}
@@
 \end{tabular}
+
 \end{threeparttable}
 \end{center}
+
 \end{table}
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf.
-int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.56{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf.
+int.: {[}3.85, 4.65{]}; \(\beta=1.04\), 89\% CI = {[}0.54, 1.56{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf.
 int.: {[}2.83, 3.57{]}).
@@
 int.: {[}2.12, 2.60{]}).
-Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.60\), 89\% CI = {[}-2.46, -0.7{]}, \emph{pd} = 0.99).
-However, this age effect was moderated in the Activity Video condition (\(\beta=1.73\), 89\% CI = {[}0.36, 3.06{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
+Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.56\), 89\% CI = {[}-2.42, -0.69{]}, \emph{pd} = 1).
+However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 89\% CI = {[}0.28, 3.04{]}, \emph{pd} = 0.97): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.47\), 89\% CI = {[}0.14, 0.78{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
-There was an interaction of age and condition (\(\beta=1.64\), 89\% CI = {[}0.42, 2.95{]}, \emph{pd} = 0.99), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.14, 0.79{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
+There was an interaction of age and condition (\(\beta=1.60\), 89\% CI = {[}0.41, 2.92{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.52, -0.19{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.96\), 89\% CI = {[}-9.82, -1.98{]}, \emph{pd} = 0.99).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 89\% CI = {[}-1.49, -0.22{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.95\), 89\% CI = {[}-9.86, -1.79{]}, \emph{pd} = 0.99).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
 
-As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
+As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions (\href{https://cogsciguy.github.io/parenting_obs_language/Exp2_characteristic_chart.html}{see SI}).
 The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uh-oh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
@@
 
-This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
-Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
+XXXX
 
@@
 \emph{JMIR mHealth and uHealth}, \emph{4}(2), e36.
-\url{http://doi.org/10.2196/mhealth.5202}
+\url{https://doi.org/10.2196/mhealth.5202}
 
@@
 \emph{Proceedings of the National Academy of Sciences}, \emph{110}(28), 11278--11283.
-\url{http://doi.org/10.1073/pnas.1309518110}
+\url{https://doi.org/10.1073/pnas.1309518110}
 
@@
 \emph{Science}, \emph{344}(6187), 998--1001.
-\url{http://doi.org/10.1126/science.1251178}
+\url{https://doi.org/10.1126/science.1251178}
 
@@
 \leavevmode\hypertarget{ref-Heckman2006}{}%
-Heckman, J. J. (2006). Skill formation and the economics of investing in disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902. \url{http://doi.org/10.1126/science.1128898}
+Heckman, J. J. (2006). Skill formation and the economics of investing in disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902. \url{https://doi.org/10.1126/science.1128898}
 
@@
 \emph{Collabra: Psychology}, \emph{6}(1).
-\url{http://doi.org/10.31234/osf.io/hxk3d}
+\url{https://doi.org/10.31234/osf.io/hxk3d}
 
@@
 \emph{Psychological Science}, \emph{26}(7), 1071--1083.
-\url{http://doi.org/10.1177/0956797615581493}
+\url{https://doi.org/10.1177/0956797615581493}
 
@@
 Leung, C.
+Y.
 Y., Hernandez, M.
@@
 \emph{Early Childhood Research Quarterly}.
-\url{http://doi.org/https://doi.org/10.1016/j.ecresq.2018.12.005}
+\url{https://doi.org/10.1016/j.ecresq.2018.12.005}
 
@@
 H.
-A., \& Lüdecke, D.
+A., \& Ludecke, D.
 (2019a).
@@
 \emph{Frontiers in Psychology}, \emph{10}, 2767.
-\url{http://doi.org/10.3389/fpsyg.2019.02767}
+\url{https://doi.org/10.3389/fpsyg.2019.02767}
 
@@
 Makowski, D., Ben-Shachar, M.
-S., \& Lüdecke, D.
+S., \& Ludecke, D.
 (2019b).
@@
 \emph{Journal of Open Source Software}, \emph{4}(40), 1541.
-\url{http://doi.org/10.21105/joss.01541}
+\url{https://doi.org/10.21105/joss.01541}
 
@@
 \leavevmode\hypertarget{ref-Schwab2016}{}%
-Schwab, J. F., \& Lew-Williams, C. (2016). Language learning, socioeconomic status, and child-directed speech. \emph{WIREs Cognitive Science}, \emph{7}, 264--275. \url{http://doi.org/10.1002/wcs.1393}
+Schwab, J.
+F., \& Lew-Williams, C.
+(2016).
+Language learning, socioeconomic status, and child-directed speech.
+\emph{WIREs Cognitive Science}, \emph{7}, 264--275.
+\url{https://doi.org/10.1002/wcs.1393}
 

### 2020-08-26 psychsci_wordcount.Rmd
added research highlights, video transcripts

--- 2020-04-28 paper/manuscript.Rmd
@@
 ---
-title             : "Understanding the impacts of video-guided activities on parent-child interaction"
-shorttitle        : "Impacts of videos on parent-child interaction"
-
-author: 
-  - name          : "George Kachergis"
-    affiliation   : "1"
-    address       : "Stanford, CA 94305 USA"
-    email         : "kachergis@stanford.edu"
-  - name          : "Emily Hembacher"
-    affiliation   : "1"
-  - name          : "Veronica Cristiano"
-    affiliation   : "2"
-  - name          : "Hanwen Vivian Zhang"
-    affiliation   : "3"
-  - name          : "Michael C. Frank"
-    corresponding : yes
-    address       : "Stanford, CA 94305 USA"
-    email         : "mcfrank@stanford.edu"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution    : "Gallaudet University"
-  - id            : "3"
-    institution    : "Cornell University"
-
-authornote: |
-
-abstract: |
-  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
-  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
-  The rise of phone-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
-  Of special interest are the parents of very young children, who are often difficult to reach in other ways.
-Yet little is known about the effects of communicating to parents through app-based interventions.
-  We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
-  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
-keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4995"
-
-bibliography      : ["library.bib"]
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-header-includes:
-  - \usepackage{float}
-documentclass     : "apa6"
-csl: apa6.csl
-classoption       : "man"
-output            : papaja::apa6_pdf
+title: "Untitled"
+author: "George Kachergis"
+date: "4/20/2020"
+output: html_document
 ---
 
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.crop = F, 
-                      fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=T, 
-                      message=F, sanitize = T)
-```
-
-```{r setup, include = FALSE}
-suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
-library("papaja")
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
-library(psych)
-library(langcog)
-library(tidyverse)
-library(ggthemes)
-library(lme4)
-library(lmerTest)
-library(tidyboot)
-library(knitr)
-library(rstanarm)
-library(bayestestR)
-source("multiplot.R")
-
-select <- dplyr::select # masked by MASS
-theme_set(theme_few())
-
-# labels=addline_format(c("Activity Video", "Science Video"))
-addline_format <- function(x,...){
-    gsub('\\s','\n',x)
-}
-```
-
-```{r load-exp1-lexical-data, include=F}
-e1path = "../parenting_obs_e1/"
-
-d = read.csv("../language_analyses/exp1_lexical_diversity.csv")
-
-e1_parent_ed = table(d$parent_ed)
-
-e1ld <- d %>%
-  mutate(condition = factor(condition), 
-         gender = as.factor(gender),
-         video = as.factor(video))
-
-e1_gender = table(e1ld$gender)
-
-# rate calculations (tokens / min, words / min)
-e1_play_duration <- read.csv(paste0(e1path,"joint_attention/parenting_obs_play_duration_E1.csv"), header=T)
-e1_play_duration$start_sec = with(e1_play_duration, ifelse(is.na(verbalcue_start_sec), 
-                                                           play_start_sec, verbalcue_start_sec))
-e1_play_duration <- e1_play_duration %>% 
-  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to mins
-  select(SID, play_duration)
-e1ld <- e1ld %>% left_join(e1_play_duration, by=c("sid"="SID"))
-
-# convert types and tokens to rate: types/min and tokens/min
-e1ld <- e1ld %>% 
-  mutate(types = (types / play_duration), 
-         tokens = (tokens / play_duration),
-         TTRnorm = (TTR / play_duration), # # not really interpretable if we normalize LD measures
-         MTLDnorm = (MTLD / play_duration)
-         )
-
-e1_6to12 = table(subset(e1ld, age<1)$condition) # con 9, exp 10
-e1_12to18 = table(subset(e1ld, age<1.5 & age>=1)$condition) # con 11 exp 9
-e1_18to24 = table(subset(e1ld, age>=1.5)$condition) # con 10, exp 11
-```
-
-```{r load-exp1-joint-attention-data, echo=F}
-load(paste0(e1path,"joint_attention/Exp1_joint_attention_data.RData"))
-d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))
-
-e1ja <- d %>%
-  #filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>% # 6 parents NA -- don't want to remove from main analysis!
-  mutate(Condition = factor(Condition), 
-         bids_tot = as.numeric(bids_tot),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         parent_ed = langcog::scale(parent_ed, scale=TRUE),
-         gender = as.factor(gender),
-         Video = as.factor(Video)
-         #pja_length = pja_length/1000,
-         #cja_length = cja_length/1000,
-         #total_lja = total_lja/1000
-         ) # convert duration ms -> seconds
-```
-
-```{r load-exp2-lexical-data, echo=F}
-e2path = "../parenting_obs_e2/"
-load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
-e2Age <- d %>% mutate(Age = age) %>%
-  select(sid, Age)
-e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
-d = read.csv("../language_analyses/exp2_lexical_diversity.csv")
-d <- d %>% left_join(e2Age, by="sid")
-
-e2ld <- d %>%
-  mutate(condition = as.factor(condition), 
-         gender = as.factor(gender),
-         video = as.factor(video)) %>%
-  select(-X.1, -X)
-
-e2ld$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
-
-e2_gender = table(d$gender)
-e2_12to18 = table(subset(d, Age<1.5)$Condition) # Activity Vid 20, Science Vid 21
-e2_18to24 = table(subset(d, Age>=1.5)$Condition) # Activity Vid 22, Science Vid 21
-
-#e2_dur = read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"))
-#e2_dur <- e2_dur %>% mutate(vid_dur=video_duration_sec / 60) %>% # sec / min
-#  select(sid, vid_dur)
-#e2ld <- e2ld %>% left_join(e2_dur, by="sid")
-
-e2_play_duration <- read.csv(paste0(e2path,"joint_attention/parenting_obs_play_duration_E2.csv"), header=T)
-e2_play_duration$start_sec = with(e2_play_duration, ifelse(is.na(verbalcue_start_sec), 
-                                                           play_start_sec, verbalcue_start_sec))
-e2_play_duration <- e2_play_duration %>% 
-  mutate(play_duration = (play_stop_sec - start_sec) / 60) %>% # sec to min
-  select(sid, play_duration)
-e2ld <- e2ld %>% left_join(e2_play_duration, by="sid")
-
-# convert types and tokens to rate: types/min and tokens/min
-e2ld <- e2ld %>% 
-  mutate(types = (types / play_duration), 
-         tokens = (tokens / play_duration),
-         TTRnorm = (TTR / play_duration), # not really interpretable if we normalize LD measures
-         MTLDnorm = (MTLD / play_duration)
-         )
-```
-
-```{r load-exp2-joint-attention-data, echo=F}
-load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
-d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
-d$Age = d$age 
-e2ja <- d %>% mutate(bids = bids,
-                     age = as.numeric(langcog::scale(age, scale=FALSE))
-                     #pja_length = pja_length/1000,
-                     #cja_length = cja_length/1000,
-                     #total_lja = total_lja/1000
-                     ) # convert duration ms -> seconds
-
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
@@
 
-## Method
-
-### Participants. 
-`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
-We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
-Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
-Fifteen parents reported that their child was of Hispanic origin. 
-Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).
-
-### Materials.
-Stimuli included activity videos from a commercial parenting application. 
-The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
-In each video, an adult and child perform the activity (e.g., sorting toys according to size) while a narrator explains the activity and its purpose. 
-We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months).
-Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.[^1]
-
-[^1]: Details of the specific videos used and the toys associated with each video are in the Appendix.
-
-Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
-Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
-The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
-Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).
-
-### Procedure.
-After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
-To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
-Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
-The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
-In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
-They were not given any additional instructions about how to use the props.
-
-[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.
-
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech.
-After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
-Parents were then asked to complete the EPAQ before being debriefed.
-
-### Joint Attention Coding Procedure.
-The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
-The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera. 
-Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA. 
-Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA. 
-If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
-An episode of joint attention was considered _passive_ if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent. 
-If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention. 
-A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
-Full details of our guidelines for coding joint attention are available in SI.
-
-A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for time spent in coordinated JA episodes.
-
-## Results
-
-Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e1ld$play_duration), 2)` min) was transcribed; child utterances were not considered.
-Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
-Below we first report the lexical diversity results, followed by the joint attention results.
-
-[^3]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982)
-
-### Lexical Diversity
-
-For each transcript of child-directed speech, the caregivers' unique word *types* and *tokens* (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
-Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
-Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (we use 0.72, as proposed by McCarthy & Jarvis).
-
-```{r, e1-lexdiv-regressions, echo=F, include=F}
-# get estimated coefficient and 89% CI from Bayesian regression
-get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
-  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
-  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
-  pd = p_direction(model)
-  pd = pd[which(pd$Parameter==cond),]$pd
-  ci = round(c(ci95,ci89,pd), digits)
-  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
-  beta = round(model$coefficients[cond], digits)
-  return(c(beta,ci))
-}
-
-print_CI <- function(mod) {
-  string = paste0("89% CI = [",mod['89pLB'],", ",mod['89pUB'],"]", ", *pd* = ",mod['pd'])
-  return(string)
-}
-
-modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld, adapt_delta = .97)
-summary(modTTR) # ESS from ~1800 - 3600
-p_direction(modTTR, effects="all") # condition
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
-
-modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
-summary(modMTLD) # ESS ~ [2200, 4100]
-p_direction(modMTLD, effects="all") # condition
-e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -8.48
-
-# predict word tokens
-tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
-summary(tokens_mod)
-p_direction(tokens_mod, effects="all") # condition
-e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 19.45
-
-# predict word types
-types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld,
-                        adapt_delta = .97)
-summary(types_mod) 
-p_direction(types_mod, effects="all") # cage 78, cond*age 83%
-
-e1_lexdiv <- e1ld %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) # types=mean(types) # con=16.7, exp=18.1
-```
-
-```{r, e1ld-exploratory, echo=F, include=F}
-# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
-e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
-# only 54 parents completed the EPAQ
-
-modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
-summary(modTTRE) 
-p_direction(modTTRE, effects="all") # RR 87%  parent_ed 90.9%
-
-modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
-summary(modMTLDE) #
-p_direction(modMTLDE, effects="all") # genderM 85%, RR 85%, AA 77%..
-
-tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
-summary(tokens_modE) # condition 54.4 
-get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # 
-p_direction(tokens_modE, effects="all") # RR 73.5% parent_ed 90.5%
-
-# predict word types
-types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
-summary(types_modE) 
-p_direction(types_modE, effects="all") # EL 84% AA 79% genderM 79%, parent_ed 89% cond:AA 96.3%
-e1types_condAA = get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA') # ADD THIS TO TEXT
-
-```
-
-We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
-For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range (see Appendix for more an illustrated explanation).
-There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`).
-A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`), with no notable influence of age.
-Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-
-[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018; @bayestestR].
-Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.
-
-```{r e1tokens, echo=F, include=F}
-e1ld$Condition = factor(e1ld$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))
-
-e1_mtld <- e1ld %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD) 
-e1_lex <- e1ld %>% group_by(Condition) %>%
-  tidyboot_mean(TTR) # Type/Token Ratio
-e1_tok <- e1ld %>% group_by(Condition) %>%
-  tidyboot_mean(tokens) 
-e1_type <- e1ld %>% group_by(Condition) %>%
-  tidyboot_mean(types)
-```
-
-We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, `r print_CI(e1tokens)`), with parents using tokens at a higher rate in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)` tokens/min, bootstrapped 95% confidence interval (conf.
-int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
-int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`, `r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
-
-```{r e1tab, echo=F, include=F}
-e1 <- e1ld %>% group_by(Condition) %>%
-  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
-            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
-            "Mean types"=mean(types), types.sd=sd(types),
-            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e1) = c("Condition","TTR/min (M)", "(sd)", "MTLD/min (M)", "(sd)", "Types/min (M)", "(sd)", "Tokens/min (M)", "(sd)")
-kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
-```
-
-```{r e1ld-figs, include=F}
-small_text = theme(
-  plot.title = element_text(size = 12, face="bold"),
-  axis.title.x = element_text(size = 10),
-  axis.text.x = element_text(size = 8),
-  axis.title.y = element_text(size = 10),
-  axis.text.y = element_text(size = 8))
-
-e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
-  geom_point(data=e1ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
-# want carriage return in Condition labels..
-
-e1mtld <- ggplot(e1_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e1ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle(" ") + small_text
-
-e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle(" ") + small_text
-
-```
-
-```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom).
-Error bars show bootstrapped 95\\% confidence intervals, and gray dots indicate values for each participant."}
-
-ttr2 <- e2ld %>% group_by(Condition) %>%
-  tidyboot_mean(TTR)
-
-e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle("Experiment 2") + small_text
-
-mtld2 <- e2ld %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD)
-
-e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle(" ") + small_text
-
-e2tok <- e2ld %>% group_by(Condition) %>%
-  tidyboot_mean(tokens)
-
-e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Word Tokens per Minute") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle(" ") + small_text
-
-#multiplot(e1ttr, e1mtld, e1tokens, cols=3) # Exp1 LD graph
-#multiplot(e2ttr, e2mtld, e2tokens, cols=3) # Exp2 LD graph
-
-multiplot(e1ttr, e1mtld, e1tokens, 
-          e2ttr, e2mtld, e2tokens, cols=3, layout=matrix(c(1,2,3, 4,5,6), nrow=2, byrow=T)) 
-```
-
-```{r, e1-effect-size, echo=F, include=F}
-cohens_d <- function(dat) {
-  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
-}
-
-ttr_means <- e1ld %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means) # -1.68 - should we report this?
-```
-
-### Joint Attention
-
-```{r, e1ja-regressions, echo=F, include=F}
-
-model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
-# Total number of bids
-e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja, adapt_delta = .98) # 
-summary(e1bids_mod) 
-p_direction(e1bids_mod, effects="all") # condition
-e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # .72
-
-e1bids_M <- e1ja %>% group_by(Condition) %>% 
-  summarise(mean = mean(bids), sd = sd(bids))
-
-# Episodes of passive joint attention.
-e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
-summary(e1pja_mod) # NA
-p_direction(e1pja_mod, effects="all") # condition 89%
-
-# Episodes of coordinated joint attention.
-e1cja_mod <- stan_lmer(paste("cja", model_string), adapt_delta = 0.99, data = e1ja) 
-summary(e1cja_mod) # NA
-p_direction(e1cja_mod, effects="all") # condition 81%
-
-# Total duration of passive joint attention.
-e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja, adapt_delta=.98)
-summary(e1pja_time_mod) # NA
-p_direction(e1pja_time_mod, effects="all") # condition 90.6%
-
-# Total duration of coordinated joint attention.
-e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
-summary(e1cja_time_mod) # NA
-p_direction(e1cja_time_mod, effects="all") # cond*age 86%
-```
-
-We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Parents' bid rate was greater in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, `r print_CI(e1bids)`).
-Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
-There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
-Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.
-
-### Exploratory Analyses
-
-```{r e1ja-epaq-regressions, include=F, echo=F}
-# follow-up regression (if we find a sig effect?)
-model_stringE =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
-
-# Rate of parental bids
-e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
-summary(e1bids_modE) # cond, gender 
-p_direction(e1bids_modE, effects="all")
-e1bidsE = get_stan_glmer_reporting_values(e1bids_modE, "genderM") # .73 [.11,1.36] REPORT
-
-e1bidsE_M <- e1ja %>% group_by(gender) %>% 
-  summarise(mean = mean(bids), sd = sd(bids))
-
-# Episodes of coordinated joint attention.
-e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
-p_direction(e1cja_modE, effects="all") # RR 89% parent_ed 89%
-summary(e1cja_modE) # NA
-
-# Episodes of passive joint attention.
-e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
-summary(e1pja_modE) # condition*RR beta=1.8, RR close
-p_direction(e1pja_modE, effects="all") # RR 98%, parent_ed 98%
-e1pjaRR = get_stan_glmer_reporting_values(e1pja_modE, "RR") # -.34, 89% CI = [-.65,-.02]  
-e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR") # .60 [.14,1.05]
-e1pja_parent_ed = get_stan_glmer_reporting_values(e1pja_modE, "parent_ed")
-
-# Total duration of passive joint attention.
-e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
-summary(e1pja_time_modE) # NA
-p_direction(e1pja_time_mod, effects="all") # condition 91%
-
-# Total duration of coordinated joint attention.
-e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
-summary(e1cja_time_modE) # NA
-p_direction(e1cja_time_mod, effects="all") # condition:age 86%
-```
-
-We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-These models included random intercepts per video. 
-Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
-First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: $\beta=`r e1types_condAA["conditionexp:AA"]`$, `r print_CI(e1types_condAA)`).
-Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["RR"]`$, `r print_CI(e1pjaRR)`).
-However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`).
-Parents with higher education also showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
-Finally, parents with male children made bids for JA at a higher rate (mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min) than those with female children (mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$, `r print_CI(e1bidsE)`).
-
-To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) for the interactive corpus characteristic plot).
-Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
-
-```{r fig-JA, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:JA} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1 (top).
-For Experiment 2 (bottom), mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right)."}
-# Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA.
-
-ms_bids1 <- e1ja %>% group_by(Condition) %>%
-  tidyboot_mean(bids_tot)
-
-e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Parental Bids for JA per Minute") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
-
-# total joint attention episodes
-ms_tja1 <- e1ja %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
-e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of JA per Minute") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle(" ") + small_text
-
-e2_cja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-
-library("scales")
-#show_col(solarized_pal()(2)) # blue, red
-sol_colors = solarized_pal()(2)
-
-e2_bids <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(bids)
-e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  labs(fill="Condition") + 
-  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Parental Bids for JA per Minute") + 
-  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
-  theme(legend.position="none")
-  #theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))
-
-# total JA episodes (not currently graphed)
-e2_tja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja) 
-e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of JA per Minute") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  ggtitle(" ") + small_text + theme(legend.position="none")
-
-e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
-  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
-  xlab("Age (years)") + ylab("Episodes of JA per Minute") +
-  ggthemes::theme_few() + ggtitle(" ") + small_text + 
-  theme(legend.position="bottom", legend.text=element_text(size=9), 
-        legend.margin=margin(0,0,5,0),
-        legend.box.margin=margin(-10,-10,-5,-10))
-  #theme(legend.position="none")
-
-# multiplot(e1bids, e1tja, cols=2) # old Exp1
-# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
-multiplot(e1bids, e1tja, e2bids, e2tja_age, 
-          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
-```
-
 ### Discussion
@@
 In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, expand the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
-<!-- discuss exploratory regression results? -->
 
@@
 
-[^5]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982).
-
-## Method
-
-### Participants. 
-`r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
-(`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
-`r e2_12to18["Science Video"]` 12-17.9 month-olds in the Science Video condition; 
-`r e2_18to24["Activity Video"]` 18-24 month-olds in the Activity Video condition;
-`r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
-We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
-Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
-Sixteen parents reported their child was of Hispanic origin. 
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed["3"]`), four-year college (n = `r e2_parent_ed["4"]`), some graduate school (n = `r e2_parent_ed["5"]`), to completed graduate school (n = `r e2_parent_ed["6"]`) or declined to state (n = 13).
-
-### Materials.
-
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
-This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
-The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies.
-Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
-The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
-Details of the videos used in the Activity Video conditions are in the Appendix.
-
-### Procedure. 
-The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
-Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
-The coding procedure also matched that of Experiment 1. 
-To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
-The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for time spent (secs/min) in passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for time spent in coordinated JA episodes.
-
-## Results
-
-Parents' child-directed speech during the play sessions (mean duration: `r round(mean(e2ld$play_duration), 2)` min) was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report preregistered regressions[^6] predicting TTR and rate of word tokens, as well as an exploratory regression predicting MTLD.
-We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
-
-[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some regressions led us to switch to Bayesian regression.
+Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some regressions led us to switch to Bayesian regression.
 Using a Bayesian analysis has the added benefit of not requiring arbitrary changes to alpha levels to correct for multiple comparisons (Gelman, 2008).
-
-### Lexical Diversity
-```{r, e2-lexdiv-regressions, echo=F, include=F}
-# preregistered analyses:
-# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens).
-# 1) bids, 2) total JA eps, 3) # tokens 4) TTR 
-# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs.
-control) and age in months as fixed effects and participant and specific video as random effects.
-# DV ~ age * condition + (1 | participant) + (1 | video)
-# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
-# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
-# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
-# "secondary analyses"
-# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.
-
-# Notes: 
-# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
-# Predicting lexical diversity based on experimental condition. 
-e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2ld) 
-summary(e2TTR_m) 
-p_direction(e2TTR_m, effects="all") # condition, age 85%
-e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp") # -.09 [-.15,-.04]
-
-# predict word tokens
-e2tokens_m <- stan_lmer(log(tokens) ~ age * condition + (1 | video), data=e2ld)
-summary(e2tokens_m) # NA 
-p_direction(e2tokens_m, effects="all") # condition 90%
-#launch_shinystan(e2tokens_m, ppd = FALSE)
-#summary(e2tokens_m, 
-#        pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"),
-#        probs = c(0.025, 0.975),
-#        digits = 2)
-#plot(e2tokens_m)
-#prior_summary(object = e2tokens_m)
-get_stan_glmer_reporting_values(e2tokens_m,"conditionexp")
-
-# require(bayesplot)
-# bayesplot_grid(
-#   plot(e2tokens_m, plotfun = "intervals", pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"), prob = 0.5, prob_outer = 0.89, point_est = "median") + ggtitle("Marginal Posterior Parameter Estimates"),
-#   plot(e2tokens_m, plotfun = "areas", pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"), prob = 0.5, prob_outer = 0.89, point_est = "median") + ggtitle("Marginal Posterior Parameter Estimates"),
-#   grid_args = list(ncol = 2)
-# )
-
-e2MTLD_m <- stan_lmer(MTLD ~ age * condition + (1 | video), data=e2ld)
-summary(e2MTLD_m) # NA
-p_direction(e2MTLD_m, effects="all") # cond 76% age:cond 83%
-
-e2_lexdiv <- e2ld %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
-```
-
-We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , `r print_CI(e2TTR)`).
-The preregistered regression predicting the number of tokens used by parents revealed no effects. 
-An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
-Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
-The means of the lexical measures are shown in Table 1.
-
-```{r e2tab, echo=F}
-e2 <- e2ld %>% group_by(Condition) %>%
-  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
-            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
-            "Mean types"=mean(types), types.sd=sd(types),
-            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e2) = c("Condition","TTR", "(sd)", "MTLD", "(sd)", "Types", "(sd)", "Tokens", "(sd)")
-#kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
-apa_table(e2, caption = "Mean lexical diversity measures in Experiment 2.")
-```
-
-```{r, e2-effect-size, echo=F, include=F}
-ttr_means <- e2ld %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means)
-```
-
-### Joint Attention
-```{r, e2ja-regressions, echo=F, include=F}
-
-# Total number of bids
-e2bids_m <- stan_lmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(e2bids_m) # condition mean=3.1, 95%CI = [1.1, 5.0]
-p_direction(e2bids_m, effects="all") # age 84%
-e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")
-
-e2tja_m <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
-summary(e2tja_m) # total episodes of joint attention -- age, age*condition, condition
-p_direction(e2tja_m, effects="all") # age, cond, age:cond
-e2tjaAge = get_stan_glmer_reporting_values(e2tja_m, "age")
-e2tjaCond = get_stan_glmer_reporting_values(e2tja_m, "ConditionActivity Video")
-e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionActivity Video")
-```
-
-We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, `r print_CI(e2bids)`) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
-There were no other effects on parental bids for JA.
-
-The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, `r print_CI(e2tjaCond)`), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
-int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, `r print_CI(e2tjaAge)`). 
-However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2tjaAgeCond)`): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.
-
-```{r e2ja-exploratory, echo=F, include=F}
-# EXPLORATORY ANALYSES (NOT PREREGISTERED)
-
-# Episodes of coordinated joint attention
-e2cja_m <- stan_lmer(cja ~ age * Condition + (1 | video), data = e2ja)
-summary(e2cja_m) #
-p_direction(e2cja_m, effects="all") # cond, age:cond, age 90%
-e2cjaCond <- get_stan_glmer_reporting_values(e2cja_m, "ConditionActivity Video")
-e2cjaAgeCond <- get_stan_glmer_reporting_values(e2cja_m, "age:ConditionActivity Video")
-
-# Episodes of passive joint attention.
-e2pja_m <- stan_lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(e2pja_m) # age beta=-2.7 89% CI=[-5.1,0.0]
-p_direction(e2pja_m, effects="all") # age 
-e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")
-
-# Total duration of passive joint attention.
-e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(e2pjat_m) # age: est: -17.97 89% CI = [-33.37,-2.41] 
-p_direction(e2pjat_m, effects="all") # age
-e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")
-
-# Total duration of coordinated joint attention.
-e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(e2cjat_m) 
-p_direction(e2cjat_m, effects="all") # age, cond 85%, age:cond 86%
-e2cjat <- get_stan_glmer_reporting_values(e2cjat_m, "age")
-```
-
-### Exploratory Analyses
-
-Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, `r print_CI(e2cjaCond)`), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2cjaAgeCond)`), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
-The regression predicting the time spent in coordinated JA episodes found no notable effects.
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, `r print_CI(e2pja)`), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, `r print_CI(e2pjat)`).
-Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
-
-As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp2_characteristic_chart.html)).
-The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".
-
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2."}
-# Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition. (no interpretation in PsychSci captions)
-
-#Episodes of coordinated joint attention
-e2cjad <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-
-e2cja <- ggplot(e2cjad, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Coordinated JA") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
-
-e2cja_age = ggplot(e2ja, aes(x = Age, y = cja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
-  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few()
-
-print(e2cja_age)
-#multiplot(e2cja, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
-```
 
@@
 
-<!-- Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
--->
+In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
 
-<!-- Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp.
-1).
-However, activity videos resulted in parents using more word tokens, while the number of word types did not differ significantly across conditions.
--->
-<!-- Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens. -->
+[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.
 
-In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
+[^4]: 89% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95% credible interval is unstable [@Kruschke2014; @McElreath2018; @bayestestR].
+Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.
 
@@
 Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
-
-\newpage
-
-# References
-```{r create_r-references}
-r_refs(file = "library.bib")
-```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup

### 2021-01-08 paper/manuscript.Rmd
minor revisions

@@
   - name          : "George Kachergis"
+    corresponding: yes
     affiliation   : "1"
@@
   - name          : "Michael C. Frank"
-    corresponding : yes
     address       : "Stanford, CA 94305 USA"
@@
     affiliation   : "1"
+
+authornote: |
+  The data that support the findings of this study are openly available in OSF at http://doi.org/10.17605/OSF.IO/2BPDF
 
@@
 keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
-wordcount         : "4954"
+wordcount         : "5066"
 bibliography      : ["library.bib"]
-floatsintext      : yes
+floatsintext      : no
 figurelist        : no
@@
 ```{r global_options, include=FALSE}
+# The data that support the findings of this study are openly available in OSF at https://osf.io/2bpdf/?view_only=d4b230deba2a4f91bdb2aba29088d982
+#  The data that support the findings of this study are openly available in OSF at http://doi.org/10.17605/OSF.IO/2BPDF
+
 knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.crop = F, 
@@
 
-The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities. 
+The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice, coaching, and suggested activities.
 A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages [for a review, see @Breitenstein2014].
@@
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commercial parenting app that delivers digital parenting advice in the form of short videos.
 Parents were randomly assigned to one of two conditions: parents in the _Activity Video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
@@
 
-### Participants. 
+### Participants
 `r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
-We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
+We included infants who were exposed to English more than 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
 62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
@@
 
-### Procedure.
+### Procedure
 After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
@@
 
-### Joint Attention Coding Procedure.
-The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
+### Joint Attention Coding Procedure
+The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu], and coders were blind to condition. 
 The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera. 
@@
 
-### Participants. 
+### Participants
 `r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
@@
 `r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
-We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
+We included infants who were exposed to English more than 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
 Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
@@
 
-### Materials.
-
+### Materials
 The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.

### 2021-01-08 paper/manuscript.Rmd
minor clarifications

@@
 
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015; see @Schwab2016 for a review].
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Rowe2012; @Cartmill2013; @HirshPasek2015; see @Schwab2016 for a review].
 Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment. 
@@
 Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages? 
-In two experiments, we collected data from parent-child dyads in a local children's museum. 
+In two experiments, we collected a convenience sample of parent-child dyads at a local children's museum. 
 We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification. 
@@
 ### Materials
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
+The design of Experiment 2 was the same as that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
 This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
@@
 ### Procedure
-The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
+The procedure for Experiment 2 matched that of Experiment 1, except that parents randomly-assigned to the Control Video condition watched a control video before the play session. 
 Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.

### 2021-01-08 paper/manuscript.Rmd
abstract, limitations

--- 2021-01-08 paper/manuscript.Rmd
@@
   The rise of phone-based parenting applications ("apps") could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
-  Yet little is known about the effects of communicating to parents through app-based interventions. 
-  In two studies (one preregistered), we showed parents short videos depicting age-appropriate parent-child activities from a parenting app. 
+  Yet relatively little is known about the local effects of communicating to parents about how they should interact via videos. 
+  In two studies (one preregistered), we investigated effects of short videos on parent behavior.
+  We showed parents videos depicting age-appropriate parent-child activities from a parenting app. 
   We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2). 
-  These results suggest that activity videos can lead to positive changes in parent engagement, providing support for the use of such videos in parenting interventions.
+  These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
 keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
@@
 
-# Research Highlights
-
-* After watching short activity videos in a parenting app, parents made more attempts to engage with their children and spoke more to them.
-* Older toddlers showed greater engagement after parents watched the activity videos, relative to younger toddlers.
-* These activity videos led parents to set more goals for their child during play. 
-* Our findings suggest that parent-led activities guided by apps may be helpful in scaffolding the play of older toddlers.
-
 # Introduction
@@
 But what do parents take away from these short messages about what to do with or how to talk with their children? 
+In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.
 
@@
 Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
-Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.
+Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which in turn is assumed to be more stimulating than what parents would have done otherwise.
 
@@
 
-But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
-Alternatively, by focusing parents on a specific activity, this approach could be flawed, causing parents to over-focus on achieving the superficial goals of the activity. 
+But is this theory of change correct in the case of digital parenting interventions? 
+That is, does the provision of knowledge and activities via short videos or messages actually lead to higher-quality play? 
+Alternatively, this approach could be flawed. 
+For example, focusing parents on a specific activity could cause them parents to over-focus on achieving the superficial goals of the activity while neglecting the broader goals of fostering more -- and more responsive -- interaction.
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
-Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
-Another possibility is that these messages might produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
+Attempting to reproduce the surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
+(Speaking as a parent, one author of the current paper has found himself occasionally so engrossed in attempting to execute an activity with his children that he has lost track of whether the children are continuing to enjoy it!).
 
-Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages? 
-In two experiments, we collected data from parent-child dyads in a local children's museum. 
+Thus, our goal was to gather information about whether the use of short video parenting messages as a component of broader interventions is supported by their local effects on parent-child interaction and language use.
+Our current studies were designed to assess how parents change their interactions with young children on the basis of these videos.  
+We made a first step towards assessing this question by performing two studies within the context of a convenience sample of parent-child dyads in a local children's museum. 
 We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification. 
@@
 
-We were interested in how digital parenting advice alters parents' interactions with their children. 
-We specifically set out to test whether activity suggestions led to higher-quality play, a presupposition of many early parenting interventions. 
-Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
+Activity suggestions, often in the form of videos, are a component of many larger digital interventions for parents. 
+We were interested in how these short activity videos alter parents' interactions with their children -- in particular, whether they actually lead to higher quality language or interaction, a presupposition of their inclusion in broader interventions.
+Towards this goal, we performed two short randomized experiments with a convenience sample of parent-child dyads. 
+We observed their behavior in short free-play sessions after viewing either activity videos or control videos, with quality of play assessed through measures of parent language and joint attention. 
 In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
@@
 
-Our study has a number of limitations related to design and sample, each of which suggests possible future directions. 
+Our study is a first step towards testing one component of a broader theory of change, namely that provisioning activities to parents can lead to more and more positive parenting interactions. 
+But even given our results, there are of course myriad reasons why digital parenting interventions might not be successful.
+Even with the best of intentions, parents viewing activities may not actually carry those activities out with greater frequency; other constraints of time and resources might be more determinative of parent behavior.
+Our results begin to address only one baseline concern about such interventions -- one that the authors held prior to performing these studies -- namely that watching these videos might simply not result in any measurable changes to parent behavior.
+That particular worry appears unfounded, though whether the changes we observed in parent behavior can be harnessed in a broader intervention remains a question for future work.
+
+Our study has a number of further limitations related to design and sample, each of which suggests possible future directions. 
 First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
@@
 Providing materials may be critical for the success of activity suggestions. 
+Third, our study evaluated only one source of videos and did not systematically identify those characteristics of the videos that might lead to success.
 Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research.
@@
 
-In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
+In sum, our findings suggest that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
+We hope that future work on this topic attempts to realize this promise in the context of broader intervention research.
 
@@
 
-This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
+This work was supported by both an unrestricted gift and a research contract from Kinedu, Inc. to the Language and Cognition Lab. 
 Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.

### 2021-01-08 paper/manuscript.Rmd
observer bias

@@
 In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
-They were not given any additional instructions about how to use the props.
-
-[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.
+They were not given any additional instructions about how to use the props.^[Based on piloting, we estimated these activities would would only require three minutes to complete.]
 
@@
 Parents were then asked to complete the EPAQ before being debriefed.
+
+Experimenters were aware of the condition structure of the experiment and condition assignment of parents but made no comments or other intervention once the parent-child interaction began.
 
@@
 The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for time spent in coordinated JA episodes.
+
+We assume that, because parents knew that they were being videotaped, they might alter their behaviors in response to the presence of the camera. 
+However, we assume that these alterations should be evenly distributed between conditions; thus inferences regarding condition differences in interaction should be unaffected by this factor.
 

### 2021-01-11 paper/manuscript.Rmd
ready to submit

@@
   We showed parents videos depicting age-appropriate parent-child activities from a parenting app. 
-  We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2). 
+  We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1; N=60) or a science video (experiment 2; N=84).
   These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
 keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
-wordcount         : "5066"
+wordcount         : "6279"
 bibliography      : ["library.bib"]
@@
 Often, however, the theory of change presupposed by such interventions is relatively vague.
-Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
+Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language; @earlylangint), often in tandem with a suggestion regarding activities (e.g., book reading; for a review see @Reese2010review).
 Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which in turn is assumed to be more stimulating than what parents would have done otherwise.
@@
 Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
-Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
+Episodes of joint attention are frequent during guided play, when parents set goals (e.g., building a tower) and scaffold their child's activities [@Wood1976; @Weisberg2013].
 Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
@@
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
-Attempting to reproduce the surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
+Attempting to reproduce the surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play, a target of parent responsiveness interventions [e.g., @Landry2008].
 (Speaking as a parent, one author of the current paper has found himself occasionally so engrossed in attempting to execute an activity with his children that he has lost track of whether the children are continuing to enjoy it!).
@@
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commercial parenting app that delivers digital parenting advice in the form of short videos.
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting [a children's museum in XXXX] to complete video-guided activities from a commercial parenting app that delivers digital parenting advice in the form of short videos.
+<!-- the Children's Discovery Museum in San Jose -->
 Parents were randomly assigned to one of two conditions: parents in the _Activity Video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
@@
 ### Participants
-`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
+`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in [XXXX].
+<!-- San Jose, CA -->
 We included infants who were exposed to English more than 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
@@
 
-Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
+Without their knowledge, participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
 Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
@@
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](XXXX)).
+<!-- https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79 -->
 
@@
 Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
-The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.[^2]
+The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of approximately three minutes.^[Based on piloting, we estimated these activities would would only require three minutes to complete.]
 In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
-They were not given any additional instructions about how to use the props.^[Based on piloting, we estimated these activities would would only require three minutes to complete.]
+They were not given any additional instructions about how to use the props.
 
@@
 Parents were then asked to complete the EPAQ before being debriefed. 
+No compensation was provided to the parents; children were given a sticker of their choice.
 
@@
 
-[^3]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982)
+[^3]: [XXXX]
+<!-- https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982) -->
 
@@
 
-[^5]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982).
+[^5]: Preregistration: [XXXX] <!-- [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982). -->
 
@@
 We included infants who were exposed to English more than 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
+Data from an additional 40 parent-child dyads were excluded from analysis (25 due to language, 10 due to experimenter error, 5 for fussiness or sibling interference).
+Forty-nine percent of included participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
 Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
@@
 
-This work was supported by both an unrestricted gift and a research contract from Kinedu, Inc. to the Language and Cognition Lab. 
-Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
+XXXX
+<!-- This work was supported by both an unrestricted gift and a research contract from Kinedu, Inc. to the Language and Cognition Lab.  -->
+<!-- Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion. -->
 

### 2021-01-11 paper/manuscript.tex
ready to submit

@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
   pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
-            pdfauthor={George Kachergis, Emily Hembacher, Veronica Cristiano, Hanwen Vivian Zhang, \& Michael C. Frank},
-            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided play},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  pdfauthor={George Kachergis1, Emily Hembacher1, Veronica Cristiano2, Hanwen Vivian Zhang3, \& Michael C. Frank1},
+  pdflang={en-EN},
+  pdfkeywords={language development; parent intervention; childhood development; joint attention; lexical diversity},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{Impacts of videos on parent-child interaction}
+\keywords{language development; parent intervention; childhood development; joint attention; lexical diversity\newline\indent Word count: 6279}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 \linenumbers
+\usepackage{csquotes}
 \usepackage{float}
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[shorthands=off,main=english]{babel}
+\fi
 
@@
 
-Correspondence concerning this article should be addressed to Michael C. Frank, Stanford, CA 94305 USA. E-mail: \href{mailto:mcfrank@stanford.edu}{\nolinkurl{mcfrank@stanford.edu}}}
+The data that support the findings of this study are openly available in OSF at \url{http://doi.org/10.17605/OSF.IO/2BPDF}
+
+Correspondence concerning this article should be addressed to George Kachergis, Stanford, CA 94305 USA. E-mail: \href{mailto:kachergis@stanford.edu}{\nolinkurl{kachergis@stanford.edu}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
 
 \abstract{
-Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
-In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
-The rise of phone-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
-Of special interest are the parents of very young children, who are often difficult to reach in other ways.
-Yet little is known about the effects of communicating to parents through app-based interventions.
-We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
-Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
-
+Early parenting practices play an important role in shaping children's future outcomes.
+In particular, high-quality early interactions can facilitate language learning and school performance.
+The rise of phone-based parenting applications (``apps'') could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
+Yet relatively little is known about the local effects of communicating to parents about how they should interact via videos.
+In two studies (one preregistered), we investigated effects of short videos on parent behavior.
+We showed parents videos depicting age-appropriate parent-child activities from a parenting app.
+We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1; N=60) or a science video (experiment 2; N=84).
+These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
 }
@@
 
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008; see Schwab \& Lew-Williams, 2016 for a review).
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008; Rowe, 2012; see Schwab \& Lew-Williams, 2016 for a review).
 Thus, because of the potential for large downstream effects (Heckman, 2006), there is tremendous interest in interventions that change children's language environment.
@@
 But what do parents take away from these short messages about what to do with or how to talk with their children?
+In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.
 
-The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities.
+The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice, coaching, and suggested activities.
 A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see Breitenstein, Gross, \& Christophersen, 2014).
@@
 Often, however, the theory of change presupposed by such interventions is relatively vague.
-Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
-Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.
+Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language; Kruythoff-Broekman, Wiefferink, Rieffe, and Uilenburg (2019)), often in tandem with a suggestion regarding activities (e.g., book reading; for a review see Reese, Sparks, and Leyva (2010)).
+Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which in turn is assumed to be more stimulating than what parents would have done otherwise.
 
@@
 Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
-Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
+Episodes of joint attention are frequent during guided play, when parents set goals (e.g., building a tower) and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
 Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
 
-But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play?
-Alternatively, by focusing parents on a specific activity, this approach could be flawed, causing parents to over-focus on achieving the superficial goals of the activity.
+But is this theory of change correct in the case of digital parenting interventions?
+That is, does the provision of knowledge and activities via short videos or messages actually lead to higher-quality play?
+Alternatively, this approach could be flawed.
+For example, focusing parents on a specific activity could cause them parents to over-focus on achieving the superficial goals of the activity while neglecting the broader goals of fostering more -- and more responsive -- interaction.
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
-Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
-Another possibility is that these messages might produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
+Attempting to reproduce the surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play, a target of parent responsiveness interventions (e.g., Landry, Smith, Swank, \& Guttentag, 2008).
+(Speaking as a parent, one author of the current paper has found himself occasionally so engrossed in attempting to execute an activity with his children that he has lost track of whether the children are continuing to enjoy it!).
 
-Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages?
-In two experiments, we collected data from parent-child dyads in a local children's museum.
+Thus, our goal was to gather information about whether the use of short video parenting messages as a component of broader interventions is supported by their local effects on parent-child interaction and language use.
+Our current studies were designed to assess how parents change their interactions with young children on the basis of these videos.\\
+We made a first step towards assessing this question by performing two studies within the context of a convenience sample of parent-child dyads in a local children's museum.
 We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification.
@@
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting {[}a children's museum in XXXX{]} to complete video-guided activities from a commercial parenting app that delivers digital parenting advice in the form of short videos.
 Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
@@
 
-\hypertarget{participants.}{%
-\subsubsection{Participants.}\label{participants.}}
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
 
-60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
-We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
+60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in {[}XXXX{]}.
+We included infants who were exposed to English more than 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
 62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
@@
 
-Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
+Without their knowledge, participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
 Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
@@
 Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (\href{XXXX}{see SI}).
 
-\hypertarget{procedure.}{%
-\subsubsection{Procedure.}\label{procedure.}}
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
 
@@
 Parents were then asked to complete the EPAQ before being debriefed.
+No compensation was provided to the parents; children were given a sticker of their choice.
 
-\hypertarget{joint-attention-coding-procedure.}{%
-\subsubsection{Joint Attention Coding Procedure.}\label{joint-attention-coding-procedure.}}
+Experimenters were aware of the condition structure of the experiment and condition assignment of parents but made no comments or other intervention once the parent-child interaction began.
 
-The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014).
+\hypertarget{joint-attention-coding-procedure}{%
+\subsubsection{Joint Attention Coding Procedure}\label{joint-attention-coding-procedure}}
+
+The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014), and coders were blind to condition.
 The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
@@
 
+We assume that, because parents knew that they were being videotaped, they might alter their behaviors in response to the presence of the camera.
+However, we assume that these alterations should be evenly distributed between conditions; thus inferences regarding condition differences in interaction should be unaffected by this factor.
+
 \hypertarget{results}{%
@@
 Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
-Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
+Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{{[}XXXX{]}}, with any deviations or exploratory analyses noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
@@
 Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
-First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
-Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
-However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
-Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
-Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.82\), 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).
+First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.85\), 89\% CI = {[}0.74, 12.91{]}, \emph{pd} = 0.96).
+Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.35\), 89\% CI = {[}-0.63, -0.06{]}, \emph{pd} = 0.97).
+However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.22, 1.03{]}, \emph{pd} = 0.99).
+Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.46, -0.05{]}, \emph{pd} = 0.97).
+Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.81\), 89\% CI = {[}0.07, 1.57{]}, \emph{pd} = 0.96).
 
-To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (\href{https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html}{see SI} for the interactive corpus characteristic plot).
 Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.
@@
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}
+Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: {[}XXXX{]} }
 
@@
 21 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1.
-We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
+We included infants who were exposed to English more than 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
+Data from an additional 40 parent-child dyads were excluded from analysis (25 due to language, 10 due to experimenter error, 5 for fussiness or sibling interference).
+Forty-nine percent of included participants (n = 41) had been exposed to two or more languages as indicated by their parent.
 Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
@@
 
-\hypertarget{materials.-1}{%
-\subsubsection{Materials.}\label{materials.-1}}
+\hypertarget{materials-1}{%
+\subsubsection{Materials}\label{materials-1}}
 
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
+The design of Experiment 2 was the same as that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
 This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
@@
 
-\hypertarget{procedure.-1}{%
-\subsubsection{Procedure.}\label{procedure.-1}}
+\hypertarget{procedure-1}{%
+\subsubsection{Procedure}\label{procedure-1}}
 
-The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
+The procedure for Experiment 2 matched that of Experiment 1, except that parents randomly-assigned to the Control Video condition watched a control video before the play session.
 Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.47\), 89\% CI = {[}0.14, 0.78{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
-There was an interaction of age and condition (\(\beta=1.64\), 89\% CI = {[}0.42, 2.95{]}, \emph{pd} = 0.99), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
+The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.14, 0.79{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
+There was an interaction of age and condition (\(\beta=1.60\), 89\% CI = {[}0.41, 2.92{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
 The regression predicting the time spent in coordinated JA episodes found no notable effects.
-Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.52, -0.19{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.96\), 89\% CI = {[}-9.82, -1.98{]}, \emph{pd} = 0.99).
+Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 89\% CI = {[}-1.49, -0.22{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.95\), 89\% CI = {[}-9.86, -1.79{]}, \emph{pd} = 0.99).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
 
-As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
+As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions (\href{https://osf.io/2bpdf/files/github/language_analyses/Exp2_characteristic_chart.html}{see SI}).
 The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uh-oh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
@@
 
-We were interested in how digital parenting advice alters parents' interactions with their children.
-We specifically set out to test whether activity suggestions led to higher-quality play, a presupposition of many early parenting interventions.
-Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
+Activity suggestions, often in the form of videos, are a component of many larger digital interventions for parents.
+We were interested in how these short activity videos alter parents' interactions with their children -- in particular, whether they actually lead to higher quality language or interaction, a presupposition of their inclusion in broader interventions.
+Towards this goal, we performed two short randomized experiments with a convenience sample of parent-child dyads.
+We observed their behavior in short free-play sessions after viewing either activity videos or control videos, with quality of play assessed through measures of parent language and joint attention.
 In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
@@
 
-Our study has a number of limitations related to design and sample, each of which suggests possible future directions.
+Our study is a first step towards testing one component of a broader theory of change, namely that provisioning activities to parents can lead to more and more positive parenting interactions.
+But even given our results, there are of course myriad reasons why digital parenting interventions might not be successful.
+Even with the best of intentions, parents viewing activities may not actually carry those activities out with greater frequency; other constraints of time and resources might be more determinative of parent behavior.
+Our results begin to address only one baseline concern about such interventions -- one that the authors held prior to performing these studies -- namely that watching these videos might simply not result in any measurable changes to parent behavior.
+That particular worry appears unfounded, though whether the changes we observed in parent behavior can be harnessed in a broader intervention remains a question for future work.
+
+Our study has a number of further limitations related to design and sample, each of which suggests possible future directions.
 First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
@@
 Providing materials may be critical for the success of activity suggestions.
+Third, our study evaluated only one source of videos and did not systematically identify those characteristics of the videos that might lead to success.
 Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research.
@@
 
+\leavevmode\hypertarget{ref-earlylangint}{}%
+Kruythoff-Broekman, A., Wiefferink, C., Rieffe, C., \& Uilenburg, N.
+(2019).
+Parent-implemented early language intervention programme for late talkers: Parental communicative behaviour change and child language outcomes at 3 and 4 years of age.
+\emph{International Journal of Language \& Communication Disorders}, \emph{54}(3), 451--464.
+
+\leavevmode\hypertarget{ref-Landry2008}{}%
+Landry, S.
+H., Smith, K.
+E., Swank, P.
+R., \& Guttentag, C.
+(2008).
+A responsive parenting intervention: The optimal timing across early childhood for impacting maternal behaviors and child outcomes.
+\emph{Developmental Psychology}, \emph{44}(5), 1335--1353.
+
 \leavevmode\hypertarget{ref-Leung2018}{}%
 Leung, C.
+Y.
 Y., Hernandez, M.
@@
 
+\leavevmode\hypertarget{ref-Reese2010review}{}%
+Reese, E., Sparks, A., \& Leyva, D. (2010). A review of parent interventions for preschool children's language and emergent literacy. \emph{Journal of Early Childhood Literacy}, \emph{10}(1), 97--117.
+
+\leavevmode\hypertarget{ref-Rowe2012}{}%
+Rowe, M. L. (2012). A longitudinal investigation of the role of quantity and quality of child-directed speech in vocabulary development. \emph{Child Development}, \emph{83}, 1762--1774.
+
 \leavevmode\hypertarget{ref-Schwab2016}{}%
-Schwab, J. F., \& Lew-Williams, C. (2016). Language learning, socioeconomic status, and child-directed speech. \emph{WIREs Cognitive Science}, \emph{7}, 264--275. \url{http://doi.org/10.1002/wcs.1393}
+Schwab, J.
+F., \& Lew-Williams, C.
+(2016).
+Language learning, socioeconomic status, and child-directed speech.
+\emph{WIREs Cognitive Science}, \emph{7}, 264--275.
+\url{https://doi.org/10.1002/wcs.1393}
 

### 2021-03-16 paper/manuscript.Rmd
shortened abstract for ChilDev

@@
 abstract: |
-  Early parenting practices play an important role in shaping children’s future outcomes. 
+  Early parenting practices help shape children’s future outcomes.
 In particular, high-quality early interactions can facilitate language learning and school performance.
-  The rise of phone-based parenting applications ("apps") could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
-  Yet relatively little is known about the local effects of communicating to parents about how they should interact via videos. 
-  In two studies (one preregistered), we investigated effects of short videos on parent behavior.
-  We showed parents videos depicting age-appropriate parent-child activities from a parenting app. 
-  We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1; N=60) or a science video (experiment 2; N=84).
+Phone-based parenting applications can deliver low-cost interventions on parenting style, yet relatively little is known about the efficacy of this approach.
+In two studies (N=142; 79 female; ages 6-24 months), we investigated effects of short videos on parent behavior.
+Parents watched videos depicting age-appropriate parent-child activities from a parenting app.
+After watching the videos, parents spoke more and made more bids for joint attention.
 These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
 keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
-wordcount         : "6279"
+wordcount         : "5509"
 bibliography      : ["library.bib"]
@@
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](XXXX)).
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).
 <!-- https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79 -->

### 2021-09-21 paper/manuscript.Rmd
condensed abstract

@@
 In particular, high-quality early interactions can facilitate language learning and school performance.
-Phone-based parenting applications can deliver low-cost interventions on parenting style, yet relatively little is known about the efficacy of this approach.
-In two studies (N=142; 79 female; ages 6-24 months), we investigated effects of short videos on parent behavior.
-Parents watched videos depicting age-appropriate parent-child activities from a parenting app.
-After watching the videos, parents spoke more and made more bids for joint attention.
+Phone-based parenting applications can deliver low-cost interventions on parenting style, yet little is known about the efficacy of this approach.
+In two studies (N=142; 79 female; ages 6-24 months; 74 white, 31 Asian, 31 biracial, 3 black, 12 other; 31 Hispanic), we investigated effects of short videos on parent behavior.
+After parents watched videos depicting age-appropriate parent-child activities, parents spoke more (d=0.83) and made more bids for joint attention (d=1.03).
 These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
@@
 
-ttr_means <- e1ld %>% group_by(Condition) %>%
+ttr_means <- e1ld %>% group_by(condition) %>%
   summarise(mean = mean(TTR), sd = sd(TTR))
@@
 ```{r, e2-effect-size, echo=F, include=F}
-ttr_means <- e2ld %>% group_by(Condition) %>%
+ttr_means <- e2ld %>% group_by(condition) %>%
   summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means)
+cohens_d(ttr_means) # -1.28
+
+# overall effect sizes for abstract:
+e1e2_tok <- e1ld %>% select(sid, condition, types, tokens, TTR, MTLD) %>%
+  bind_rows(e2ld %>% select(sid, condition, types, tokens, TTR, MTLD)) %>% 
+  group_by(condition) %>%
+  summarise(mean = mean(tokens), sd = sd(tokens))
+cohens_d(e1e2_tok) # d=0.83 (E1: 0.94, E2: .77)
+
+e1e2_ja <- e1ja %>% mutate(condition = factor(ifelse(Condition=="No Video", "con", "exp"))) %>%
+  select(SID, condition, bids, pja, cja) %>%
+  bind_rows(e2ja %>% select(SID, condition, bids, pja, cja)) %>% 
+  group_by(condition) %>%
+  summarise(mean = mean(bids), sd = sd(bids))
+cohens_d(e1e2_ja) # d=1.03
+# After watching the videos, parents spoke more (d=0.83) and made more bids for joint attention (d=1.03).
 ```

### 2021-09-21 paper/supp-ActivityVideos.Rmd
anonymous view-only links for blind peer review
condensed abstract

--- 2020-03-26 paper/appendix.Rmd
@@
 ---
-title: "Appendix: Activity Videos"
-output: pdf_document
+title: 'Supplemental Materials: Activity Videos'
+output:
+  word_document: default
+  pdf_document: default
 ---
+<!-- 522 words -->
 
@@
 
-Parents are told to ask their child to hand over individual toys.
-They are also encouraged to praise the child after they give them the toys, and repeat the process until the child follows the verbal instructions.
+(The same as Video C in Exp. 1, but with different props.)
 
@@
 
-Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
-
-Props: two yellow and green rings, big car, small car, big horse, small horse
+(The same as Video D in Exp. 1.)
 
@@
 
-Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
-They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
-
-Props: two buckets, big car, small car, big horse, small horse
+(The same as Video E in Exp. 1.)
 
@@
 
-Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
-
-Props: maracas, drum, tambourine, clapper
+(The same as Video F in Exp. 1.)
 

### 2023-10-23 paper/manuscript.Rmd
update abstract
minor edits

@@
 In particular, high-quality early interactions can facilitate language learning and school performance.
-Phone-based parenting applications can deliver low-cost interventions on parenting style, yet little is known about the efficacy of this approach.
+Phone-based parenting applications can deliver low-cost interventions on parenting style.
 In two studies (N=142; 79 female; ages 6-24 months; 74 white, 31 Asian, 31 biracial, 3 black, 12 other; 31 Hispanic), we investigated effects of short videos on parent behavior.
-After parents watched videos depicting age-appropriate parent-child activities, parents spoke more (d=0.83) and made more bids for joint attention (d=1.03).
-These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
+Immediately after parents watched videos depicting age-appropriate parent-child activities, parents spoke more (d=0.83) and made more bids for joint attention (d=1.03).
+These results suggest that activity videos can lead to near-term changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
 keywords          : "language development; parent intervention; childhood development; joint attention; lexical diversity"
@@
 But what do parents take away from these short messages about what to do with or how to talk with their children? 
-In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.
+In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local (i.e.
+near-term) behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.
 
@@
 Alternatively, this approach could be flawed. 
-For example, focusing parents on a specific activity could cause them parents to over-focus on achieving the superficial goals of the activity while neglecting the broader goals of fostering more -- and more responsive -- interaction.
+For example, focusing parents on a specific activity could cause parents to over-focus on achieving the superficial goals of the activity while neglecting the broader goals of fostering more -- and more responsive -- interaction.
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
@@
 Thus, our goal was to gather information about whether the use of short video parenting messages as a component of broader interventions is supported by their local effects on parent-child interaction and language use.
-Our current studies were designed to assess how parents change their interactions with young children on the basis of these videos.  
+Our current studies were designed to assess how parents change their near-term interactions with young children on the basis of these videos. 
 We made a first step towards assessing this question by performing two studies within the context of a convenience sample of parent-child dyads in a local children's museum. 
@@
 To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) for the interactive corpus characteristic plot).
-Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
+Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "see", "let", and the child's name.
 
